---
title: "211020_Griess_pipet_confirm"
author: "KiseokUchicago"
date: "2021-10-21"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=11, fig.height=9,
                      error=TRUE, echo=TRUE, eval=TRUE, warning=FALSE, message=FALSE)
```

## Slurry extraction pipet confirmation (Griess assay)
Researcher: **Kiseok Lee** \
Experiment Date: 10/20/21 \
Analysis Date: 10/21/21
Lab: **Seppe Kuehn**

```{r}
# libraries
library(dplyr)
library(ggplot2)
library(RColorBrewer)
library(vegan)
library(tidyverse)
library(magrittr)
library(readxl)
library(reshape2)
library(gtools)
library(devtools)
library(openxlsx)
library(ape)
library(stringr)
library(tidyr)
library(ggrepel)
library(ggpubr)

## theme for ggplot
mytheme <- theme_bw() + 
  theme(text = element_text(family="serif")) +
  theme(plot.title = element_text(size = 19,hjust = 0.5, family="serif")) + 
  theme(axis.title.x = element_text(size = 17,hjust = 0.5, family="serif")) + 
  theme(axis.title.y = element_text(size = 17,hjust = 0.5, family="serif")) + 
  theme(axis.text.x = element_text(hjust = 0.5, vjust=0.3,size=13, family="serif"))+
  theme(axis.text.y = element_text(size=10, family="serif"))+
  theme(panel.grid.major = element_blank()) +
  theme(panel.grid.minor = element_blank(),panel.background=element_blank(),panel.border=element_blank(),plot.background=element_blank()) +
  theme(axis.ticks = element_line(size = 1.1))

mytheme_2d <- theme_bw() + 
  theme(text = element_text(family="serif")) +
  theme(plot.title = element_text(size = 19,hjust = 0.5, family="serif")) + 
  theme(axis.title.x = element_text(size = 17,hjust = 0.5, family="serif")) + 
  theme(axis.title.y = element_text(size = 17,hjust = 0.5, family="serif")) + 
  theme(axis.text.x = element_text(hjust = 0.5, vjust=0.3,size=13, family="serif"))+
  theme(axis.text.y = element_text(size=13, family="serif"))+
  # theme(panel.grid.major = element_blank()) +
  # theme(panel.grid.minor = element_blank(),panel.background=element_blank(),plot.background=element_blank()) +
  theme(axis.ticks = element_line(size = 1.1))


# color collection
my_color_collection <- c(
  "#CBD588", "#5F7FC7", "orange", "#AD6F3B", "#673770", 
  "#D14285", "#652926", "#C84248", "#8569D5", "#5E738F",
  "#D1A33D", "#8A7C64", "#599861","#616163", "#FFCDB2",
  "#6D9F71", "#242F40",
  "#CCA43B", "#F92A82", "#ED7B84", "#7EB77F", 
  "#DEC4A1", "#E5D1D0", '#0E8482', '#C9DAEA', '#337357', 
  '#95C623', '#E55812', '#04471C', '#F2D7EE', '#D3BCC0', 
  '#A5668B', '#69306D', '#0E103D', '#1A535C', '#4ECDC4', 
  '#F7FFF7', '#FF6B6B', '#FFE66D', '#6699CC', '#FFF275', 
  '#FF8C42', '#FF3C38', '#A23E48', '#000000', '#CF5C36', 
  '#EEE5E9', '#7C7C7C', '#EFC88B', '#2E5266', '#6E8898', 
  '#9FB1BC', '#D3D0CB', '#E2C044', '#5BC0EB', '#FDE74C', 
  '#9BC53D', '#E55934', '#FA7921', "#CD9BCD", "#508578", "#DA5724")

# for git push, use this instead of using wflow_git_push()
# git push -u origin master (in the Git app / in the working directory)

```


## 1. Import data table from python code
```{r}
# import file
df_p0 <- openxlsx::read.xlsx("data/211020_Griess_plate0.xlsx")
df_p1 <- openxlsx::read.xlsx("data/211020_Griess_plate1.xlsx")

head(df_p0)
colnames(df_p0)
dim(df_p0)

head(df_p1)
colnames(df_p1)
dim(df_p1)

# remove wells 
# df_p1 %<>% filter(!(Well %in% c("B02","H04")))
# dim(df_p1)

# bind two dataframe
df_p <- rbind(df_p0, df_p1)
dim(df_p)

# remove NA
dim(df_p)
df_p <- na.omit(df_p)
dim(df_p)

df_p

# remove 4mM spike ins because it is out of standard curve range
df_p %<>% filter(!(Nitrate_input == 4))
dim(df_p)

# Check
# df_p1 %>% filter(Well =="B02")
# df_p1 %>% filter(Well =="H04")

```

## 2. Get average and standard deviation
```{r}
# average and standard deviation

# plot to see
ggplot(df_p, aes(x=Nitrate_input, y=NO3_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  scale_fill_brewer(palette='Set2') +
  ylab("NO3- (mM) \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  # scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  ggtitle("Without averaging \n") +
  mytheme_2d

# plot to see
ggplot(df_p0, aes(x=Nitrate_input, y=NO3_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  scale_fill_brewer(palette='Set2') +
  ylab("NO3- (mM) \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  # scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  ggtitle("Without averaging \n") +
  mytheme_2d

# plot to see
ggplot(df_p1, aes(x=Nitrate_input, y=NO3_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  scale_fill_brewer(palette='Set2') +
  ylab("NO3- (mM) \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  # scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  ggtitle("Without averaging \n") +
  mytheme_2d

# average technical replicate
df_NO2NO3 <- df_p %>% group_by(Sample, Extraction_method, Extraction_ul, Nitrate_input, Sample_type, Pipet) %>% summarise(Ave_NO2_mM = mean(NO2_mM), Std_NO2_mM = sd(NO2_mM), Ave_NO3_mM = mean(NO3_mM), Std_NO3_mM = sd(NO3_mM)) %>% ungroup()

dim(df_NO2NO3)

# Factor in orders
df_NO2NO3$Sample_type <-  factor(df_NO2NO3$Sample_type, levels = c("Soil","Blank"))
df_NO2NO3$Pipet <-  factor(df_NO2NO3$Pipet, levels = c("300pipet","1200pipet"))

# Testing negative samples
df_neg <- df_NO2NO3 %>% filter(Sample_type == "Blank", Nitrate_input == 0)
df_neg
# close to zero

# plot to see
ggplot(df_NO2NO3, aes(x=Nitrate_input, y=Ave_NO3_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  geom_errorbar(aes(ymin=Ave_NO3_mM - Std_NO3_mM, ymax=Ave_NO3_mM + Std_NO3_mM), width=.05)+
  scale_fill_brewer(palette='Set2') +
  ylab("NO3- (mM) \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  # scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  ggtitle("After averaging with technical replicates \n") +
  mytheme_2d

# average biological replicates
# standard deviation is the standard deviation of the technical replicate average
dim(df_NO2NO3)
head(df_NO2NO3)


```

## 3. Plot per method

## 3.1. Scatter plots for blanks and spike ins

```{r}
# try out 100ul 300pipet case
df_100ul_300pipet <- df_NO2NO3 %>% filter(Extraction_ul  == 100, Pipet == "300pipet")
colnames(df_100ul_300pipet)
dim(df_100ul_300pipet)

ggplot(df_100ul_300pipet, aes(x=Nitrate_input, y=Ave_NO3_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  geom_errorbar(aes(ymin=Ave_NO3_mM - Std_NO3_mM, ymax=Ave_NO3_mM + Std_NO3_mM), width=.05)+
  # scale_color_brewer(palette='Set2') +
  # scale_color_manual(values = c("deepskyblue4","maroon2"))+
  ylab("Measured NO3- (mM) \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  scale_y_continuous(breaks = seq(0,2.1,0.25), limits=c(0, 2.1))+
  scale_x_continuous(breaks = seq(0,2.1,0.25), limits=c(0, 2.1))+
  ggtitle("0.5:1:1.5 (soil:water:KCl) method-100ul extraction-300ulPipet \n") +
  geom_abline(slope = 1, intercept=0, show.legend = "y=x")+
  mytheme_2d

# look at 100ul 1200 pipet case
df_100ul_1200pipet <- df_NO2NO3 %>% filter(Extraction_ul  == 100, Pipet == "1200pipet")
colnames(df_100ul_1200pipet)
dim(df_100ul_1200pipet)

ggplot(df_100ul_1200pipet, aes(x=Nitrate_input, y=Ave_NO3_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  geom_errorbar(aes(ymin=Ave_NO3_mM - Std_NO3_mM, ymax=Ave_NO3_mM + Std_NO3_mM), width=.05)+
  # scale_color_brewer(palette='Set2') +
  # scale_color_manual(values = c("deepskyblue4","maroon2"))+
  ylab("Measured NO3- (mM) \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  scale_y_continuous(breaks = seq(0,2.1,0.25), limits=c(0, 2.1))+
  scale_x_continuous(breaks = seq(0,2.1,0.25), limits=c(0, 2.1))+
  ggtitle("0.5:1:1.5 (soil:water:KCl) method-100ul extraction-1200ulPipet \n") +
  geom_abline(slope = 1, intercept=0, show.legend = "y=x")+
  mytheme_2d

# look at 100ul 1200 pipet case
df_100ul_1200pipet <- df_NO2NO3 %>% filter(Extraction_ul  == 100, Pipet == "1200pipet")
colnames(df_100ul_1200pipet)
dim(df_100ul_1200pipet)

ggplot(df_100ul_1200pipet, aes(x=Nitrate_input, y=Ave_NO3_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  geom_errorbar(aes(ymin=Ave_NO3_mM - Std_NO3_mM, ymax=Ave_NO3_mM + Std_NO3_mM), width=.05)+
  # scale_color_brewer(palette='Set2') +
  # scale_color_manual(values = c("deepskyblue4","maroon2"))+
  ylab("Measured NO3- (mM) \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  scale_y_continuous(breaks = seq(0,2.1,0.25), limits=c(0, 2.1))+
  scale_x_continuous(breaks = seq(0,2.1,0.25), limits=c(0, 2.1))+
  ggtitle("0.5:1:1.5 (soil:water:KCl) method-100ul extraction-1200ulPipet \n") +
  geom_abline(slope = 1, intercept=0, show.legend = "y=x")+
  mytheme_2d

# look at 100ul 1200 pipet case
df_100ul_1200pipet <- df_NO2NO3 %>% filter(Extraction_ul  == 100, Pipet == "1200pipet")
colnames(df_100ul_1200pipet)
dim(df_100ul_1200pipet)

ggplot(df_100ul_1200pipet, aes(x=Nitrate_input, y=Ave_NO3_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  geom_errorbar(aes(ymin=Ave_NO3_mM - Std_NO3_mM, ymax=Ave_NO3_mM + Std_NO3_mM), width=.05)+
  # scale_color_brewer(palette='Set2') +
  # scale_color_manual(values = c("deepskyblue4","maroon2"))+
  ylab("Measured NO3- (mM) \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  scale_y_continuous(breaks = seq(0,2.1,0.25), limits=c(0, 2.1))+
  scale_x_continuous(breaks = seq(0,2.1,0.25), limits=c(0, 2.1))+
  ggtitle("0.5:1:1.5 (soil:water:KCl) method-100ul extraction-1200ulPipet \n") +
  geom_abline(slope = 1, intercept=0, show.legend = "y=x")+
  mytheme_2d

# look at 50ul 300 pipet case
df_50ul_300pipet <- df_NO2NO3 %>% filter(Extraction_ul  == 50, Pipet == "300pipet")
colnames(df_50ul_300pipet)
dim(df_50ul_300pipet)

ggplot(df_50ul_300pipet, aes(x=Nitrate_input, y=Ave_NO3_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  geom_errorbar(aes(ymin=Ave_NO3_mM - Std_NO3_mM, ymax=Ave_NO3_mM + Std_NO3_mM), width=.05)+
  # scale_color_brewer(palette='Set2') +
  # scale_color_manual(values = c("deepskyblue4","maroon2"))+
  ylab("Measured NO3- (mM) \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  scale_y_continuous(breaks = seq(0,2.1,0.25), limits=c(0, 2.1))+
  scale_x_continuous(breaks = seq(0,2.1,0.25), limits=c(0, 2.1))+
  ggtitle("0.5:1:1.5 (soil:water:KCl) method-50ul extraction-300ulPipet \n") +
  geom_abline(slope = 1, intercept=0, show.legend = "y=x")+
  mytheme_2d

# get extraction ratio
# innate nitrate
add_innate <- df_NO2NO3 %>% filter(Sample_type== "Soil", Nitrate_input == 0) %>% rename(Innate_NO3_mM = Ave_NO3_mM) %>% select(Extraction_ul, Pipet, Innate_NO3_mM)

df_NO2NO3_innate <- df_NO2NO3 %>% filter(Sample_type== "Soil", Nitrate_input != 0) %>% arrange(Sample) %>%
  left_join(add_innate, by=c("Extraction_ul"="Extraction_ul", "Pipet"="Pipet")) %>% 
  mutate(Retrieved_NO3_mM = Ave_NO3_mM - Innate_NO3_mM)

# Retrieved ratio of spike ins
df_NO2NO3_innate$Ratio_retrieved <- df_NO2NO3_innate$Retrieved_NO3_mM / df_NO2NO3_innate$Nitrate_input 
df_NO2NO3_innate$Std_Ratio_retrieved <- df_NO2NO3_innate$Std_NO3_mM / df_NO2NO3_innate$Nitrate_input 

```

## 3.2. Pipet effect
300ul multichannel vs 1200ul Rainin 1.2ml tip 
```{r}
# filter

df_100 <- df_NO2NO3_innate %>% filter(Extraction_ul == 100)
df_100$Nitrate_input <- factor(df_100$Nitrate_input)

ggplot(df_100, aes(x=Nitrate_input, y=Ratio_retrieved, fill=Pipet, group=Pipet)) +
  geom_bar(stat="identity",position="dodge")+
  geom_errorbar(aes(ymin=Ratio_retrieved - Std_Ratio_retrieved, ymax=Ratio_retrieved + Std_Ratio_retrieved), width=.05, position = position_dodge(0.8))+
  # geom_line(size=0.2, color="brown")+
  scale_fill_brewer(palette='Set2') +
  ylab("Ratio of retrieved nitrate concentraion \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  # scale_y_continuous(breaks = seq(0,1,0.1), limits=c(0, 1))+
  # scale_x_continuous(breaks = seq(0,2.1,0.25), limits=c(0, 2.1))+
  ggtitle("Effect of different pipet (100ul extraction) \n") +
  geom_text(aes(label = round(Ratio_retrieved,3)), size = 3, vjust = -1.5, family="serif", show.legend = FALSE, position = position_dodge(0.8))+
  mytheme_2d

```

## 3.3. Sampled volume (Vs) effect
50ul vs 100ul sampling (same 300ul multichannel pipet) 
```{r}
# filter
df_volume <- df_NO2NO3_innate %>% filter(Pipet == "300pipet")
df_volume$Nitrate_input <- factor(df_volume$Nitrate_input)
df_volume$Extraction_ul <- factor(df_volume$Extraction_ul)


ggplot(df_volume, aes(x=Nitrate_input, y=Ratio_retrieved, fill=Extraction_ul, group=Extraction_ul)) +
  geom_bar(stat="identity",position="dodge")+
  geom_errorbar(aes(ymin=Ratio_retrieved - Std_Ratio_retrieved, ymax=Ratio_retrieved + Std_Ratio_retrieved), width=.05, position = position_dodge(0.8))+
  # geom_line(size=0.2, color="brown")+
  # scale_fill_brewer(palette='Set4') +
  ylab("Ratio of retrieved nitrate concentraion \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  # scale_y_continuous(breaks = seq(0,1,0.1), limits=c(0, 1))+
  # scale_x_continuous(breaks = seq(0,2.1,0.25), limits=c(0, 2.1))+
  ggtitle("Effect of sampling volume (same 300ul multichannel pipet) \n") +
  geom_text(aes(label = round(Ratio_retrieved,3)), size = 3, vjust = -1.5, family="serif", show.legend = FALSE, position = position_dodge(0.8))+
  mytheme_2d

```

## 3.4. Moisture correction factor 

```{r}
# without any correction
df_100ul_300pipet_innate <- df_NO2NO3_innate %>% filter(Extraction_ul == 100, Pipet == "300pipet")
dim(df_100ul_300pipet_innate)

ggplot(df_100ul_300pipet_innate, aes(x=Nitrate_input, y=Ratio_retrieved)) +  ## I put fill=value which was wrong
  geom_bar(stat="identity",position="dodge", fill = "brown")+
  geom_line(size=0.2, color="brown")+
  ylab("Ratio of retrieved nitrate concentraion \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  # scale_y_continuous(breaks = seq(0,1,0.1), limits=c(0, 1))+
  # scale_x_continuous(breaks = seq(0,2.1,0.25), limits=c(0, 2.1))+
  ggtitle("0.5:1:1.5 (soil:water:KCl) method-100ul extraction-300ulPipet \n") +
  geom_text(aes(label = round(Ratio_retrieved,3)), size = 3, vjust = -1.5, family="serif", show.legend = FALSE)+
  mytheme_2d

# moisture correction factor
soil_g = 0.5
moisture_percent = 2.14
mcf = (soil_g*(moisture_percent/100) + 1)

df_NO2NO3_mcf <- df_NO2NO3 %>% mutate(Ave_NO3_mM = Ave_NO3_mM * mcf, Ave_NO2_mM = Ave_NO2_mM * mcf, Std_NO2_mM = Std_NO2_mM * mcf, Std_NO3_mM = Std_NO3_mM * mcf)

# (correction) get extraction ratio
# innate nitrate
add_innate_mcf <- df_NO2NO3_mcf %>% filter(Sample_type== "Soil", Nitrate_input == 0) %>% rename(Innate_NO3_mM = Ave_NO3_mM) %>% select(Extraction_ul, Pipet, Innate_NO3_mM)

df_NO2NO3_innate_mcf <- df_NO2NO3_mcf %>% filter(Sample_type== "Soil", Nitrate_input != 0) %>% arrange(Sample) %>%
  left_join(add_innate_mcf, by=c("Extraction_ul"="Extraction_ul", "Pipet"="Pipet")) %>% 
  mutate(Retrieved_NO3_mM_mcf = Ave_NO3_mM - Innate_NO3_mM)

# Retrieved ratio of spike ins
df_NO2NO3_innate_mcf$Ratio_retrieved_mcf <- df_NO2NO3_innate_mcf$Retrieved_NO3_mM_mcf / df_NO2NO3_innate_mcf$Nitrate_input 
df_NO2NO3_innate_mcf$Std_Ratio_retrieved_mcf <- df_NO2NO3_innate_mcf$Std_NO3_mM / df_NO2NO3_innate_mcf$Nitrate_input 

df_NO2NO3_innate_mcf

# plot
df_100_300_innate_mcf <- df_NO2NO3_innate_mcf %>% filter(Extraction_ul == 100, Pipet == "300pipet")
dim(df_100_300_innate_mcf)

ggplot(df_100_300_innate_mcf, aes(x=Nitrate_input, y=Ratio_retrieved_mcf)) +  ## I put fill=value which was wrong
  geom_bar(stat="identity",position="dodge", fill = "brown")+
  geom_line(size=0.2, color="brown")+
  ylab("Ratio of retrieved nitrate concentraion \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  # scale_y_continuous(breaks = seq(0,1,0.1), limits=c(0, 1))+
  # scale_x_continuous(breaks = seq(0,2.1,0.25), limits=c(0, 2.1))+
  ggtitle("(Moisture correction) 0.5:1:1.5 (soil:water:KCl) method-100ul extraction-300ulPipet \n") +
  geom_text(aes(label = round(Ratio_retrieved_mcf,3)), size = 3, vjust = -1.5, family="serif", show.legend = FALSE)+
  mytheme_2d
```


3.5. Blank - nitrate spike correlation correction

```{r}
# fitting to blank of 100ul extraction
df_100ul_300pipet

# multiply mcf first to raw data.
colnames(df_p)
df_p_mcf <- df_p %>% mutate(NO3_mM = NO3_mM * mcf, NO2_mM = NO2_mM * mcf)

df_b100 <- df_p_mcf %>% filter(Extraction_ul ==100, Pipet == "300pipet", Sample_type == "Blank")
dim(df_b100)

fit.b100 <- lm(NO3_mM ~ Nitrate_input, df_b100)

# Plot fitted linear regression line
ggplot(df_b100, aes(x=Nitrate_input, y=NO3_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  # geom_errorbar(aes(ymin=NO3_mM - sd_NO3_mM, ymax=NO3_mM + sd_NO3_mM), width=.05)+
  # scale_color_brewer(palette='Set2') +
  scale_color_manual(values = c("maroon2","deepskyblue4"))+
  ylab("Measured NO3- (mM) \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  scale_y_continuous(breaks = seq(0,2.5,0.25), limits=c(0, 2.5))+
  scale_x_continuous(breaks = seq(0,2.1,0.1), limits=c(0, 2.1))+
  # geom_text_repel(aes(label = round(NO3_mM,3)), size = 3,family="serif", show.legend = FALSE)+
  ggtitle("Blank spike in \n") +
  geom_abline(slope = 1, intercept=0, show.legend = "y=x")+
  # regression line
  geom_abline(slope = coef(fit.b100)[[2]], intercept = coef(fit.b100)[[1]],
              color = "maroon2") +
  # show equation
  # stat_cor(aes(label = paste(..rr.label.., ..p.label.., sep = "~`,`~"))) +
  annotate("text",x=1,y=2, label= paste0("y = ", round(coef(fit.b100)[[1]],3),"+",round(coef(fit.b100)[[2]],3),"x"), color = "maroon2") +
  mytheme_2d

# correction factor... is it reasonable to include correction factor with blanks?
# use the regression equation for correction
# starting from df_NO2NO3_mcf (moisture corrected)
# select 100ul sampling w/ 300 pipet
df_100_300_mcf <- df_NO2NO3_mcf %>% filter(Extraction_ul == 100, Pipet == "300pipet")
# multiplying blank correction factor
df_100_300_mcf_bcf <- df_100_300_mcf %>% mutate(Ave_NO3_mM = (Ave_NO3_mM - coef(fit.b100)[[1]]) / coef(fit.b100)[[2]], Std_NO3_mM = Std_NO3_mM / coef(fit.b100)[[2]])
# if negative make it 0
df_100_300_mcf_bcf$Ave_NO3_mM <- ifelse(df_100_300_mcf_bcf$Ave_NO3_mM < 0, 0, df_100_300_mcf_bcf$Ave_NO3_mM)
# innate nitrate
add_innate_mcf_bcf <- df_100_300_mcf_bcf %>% filter(Sample_type== "Soil", Nitrate_input == 0) %>% rename(Innate_NO3_mM = Ave_NO3_mM) %>% select(Extraction_ul, Pipet, Innate_NO3_mM)

df_100_300_innate_mcf_bcf <- df_100_300_mcf_bcf %>% filter(Sample_type== "Soil", Nitrate_input != 0) %>% arrange(Sample) %>%
  left_join(add_innate_mcf_bcf, by=c("Extraction_ul"="Extraction_ul", "Pipet"="Pipet")) %>% 
  mutate(Retrieved_NO3_mM_mcf_bcf = Ave_NO3_mM - Innate_NO3_mM)

# Retrieved ratio of spike ins
df_100_300_innate_mcf_bcf$Ratio_retrieved_mcf_bcf <- df_100_300_innate_mcf_bcf$Retrieved_NO3_mM_mcf_bcf / df_100_300_innate_mcf_bcf$Nitrate_input 
df_100_300_innate_mcf_bcf$Std_Ratio_retrieved_mcf_bcf <- df_100_300_innate_mcf_bcf$Std_NO3_mM / df_100_300_innate_mcf_bcf$Nitrate_input 

df_100_300_innate_mcf_bcf

# plot
ggplot(df_100_300_innate_mcf_bcf, aes(x=Nitrate_input, y=Ratio_retrieved_mcf_bcf)) +  ## I put fill=value which was wrong
  geom_bar(stat="identity",position="dodge", fill = "brown")+
  geom_line(size=0.2, color="brown")+
  ylab("Ratio of retrieved nitrate concentraion \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  # scale_y_continuous(breaks = seq(0,1,0.1), limits=c(0, 1))+
  # scale_x_continuous(breaks = seq(0,2.1,0.25), limits=c(0, 2.1))+
  ggtitle("(After blank correction) 0.5:1:1.5 (soil:water:KCl) method-100ul extraction-300ulPipet \n") +
  geom_text(aes(label = round(Ratio_retrieved_mcf_bcf,3)), size = 3, vjust = -1.5, family="serif", show.legend = FALSE)+
  mytheme_2d


# plot all corrected ratios in one plate
df_none <- df_100ul_300pipet_innate %>% mutate(Correction = "None") %>% select(Nitrate_input, Ratio_retrieved, Std_Ratio_retrieved, Correction)
df_mcf <- df_100_300_innate_mcf %>% mutate(Correction = "Moisture") %>% select(Nitrate_input, Ratio_retrieved_mcf, Std_Ratio_retrieved_mcf, Correction) %>% rename(Ratio_retrieved= Ratio_retrieved_mcf, Std_Ratio_retrieved=Std_Ratio_retrieved_mcf)
df_mcf_bcf <- df_100_300_innate_mcf_bcf %>% mutate(Correction = "Moisture + Blank") %>% select(Nitrate_input, Ratio_retrieved_mcf_bcf, Std_Ratio_retrieved_mcf_bcf, Correction) %>% rename(Ratio_retrieved=Ratio_retrieved_mcf_bcf, Std_Ratio_retrieved=Std_Ratio_retrieved_mcf_bcf)

df_ratio_correction <- rbind(df_none, df_mcf, df_mcf_bcf)

# factorize
df_ratio_correction$Nitrate_input <- factor(df_ratio_correction$Nitrate_input)
df_ratio_correction$Correction <- factor(df_ratio_correction$Correction, levels = c("None","Moisture","Moisture + Blank" ))

ggplot(df_ratio_correction, aes(x=Nitrate_input, y=Ratio_retrieved, fill=Correction, group=Correction)) +
  geom_bar(stat="identity",position="dodge")+
  geom_errorbar(aes(ymin=Ratio_retrieved - Std_Ratio_retrieved, ymax=Ratio_retrieved + Std_Ratio_retrieved), width=.05, position = position_dodge(0.8))+
  # geom_line(size=0.2, color="brown")+
  scale_fill_brewer(palette='Set2') +
  ylab("Ratio of retrieved nitrate concentraion \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  # scale_y_continuous(breaks = seq(0,1,0.1), limits=c(0, 1))+
  # scale_x_continuous(breaks = seq(0,2.1,0.25), limits=c(0, 2.1))+
  ggtitle("Effect of concentration correction (all 100ul extraction w/ 300pipet) \n") +
  geom_text(aes(label = round(Ratio_retrieved,3)), size = 3, vjust = -1.5, family="serif", show.legend = FALSE, position = position_dodge(0.8))+
  mytheme_2d

```

