---
title: "211017_Griess_slurry_extraction"
author: "KiseokUchicago"
date: "2021-10-18"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=11, fig.height=9,
                      error=TRUE, echo=TRUE, eval=TRUE, warning=FALSE, message=FALSE)
```

## Slurry extraction condition test (Griess assay)
Researcher: **Kiseok Lee** \
Experiment Date: 10/17/21 \
Analysis Date: 10/18/21
Lab: **Seppe Kuehn**

```{r}
# libraries
library(dplyr)
library(ggplot2)
library(RColorBrewer)
library(vegan)
library(tidyverse)
library(magrittr)
library(readxl)
library(reshape2)
library(gtools)
library(devtools)
library(openxlsx)
library(ape)
library(stringr)
library(tidyr)
library(ggrepel)
library(ggpubr)

## theme for ggplot
mytheme <- theme_bw() + 
  theme(text = element_text(family="serif")) +
  theme(plot.title = element_text(size = 19,hjust = 0.5, family="serif")) + 
  theme(axis.title.x = element_text(size = 17,hjust = 0.5, family="serif")) + 
  theme(axis.title.y = element_text(size = 17,hjust = 0.5, family="serif")) + 
  theme(axis.text.x = element_text(hjust = 0.5, vjust=0.3,size=13, family="serif"))+
  theme(axis.text.y = element_text(size=10, family="serif"))+
  theme(panel.grid.major = element_blank()) +
  theme(panel.grid.minor = element_blank(),panel.background=element_blank(),panel.border=element_blank(),plot.background=element_blank()) +
  theme(axis.ticks = element_line(size = 1.1))

mytheme_2d <- theme_bw() + 
  theme(text = element_text(family="serif")) +
  theme(plot.title = element_text(size = 19,hjust = 0.5, family="serif")) + 
  theme(axis.title.x = element_text(size = 17,hjust = 0.5, family="serif")) + 
  theme(axis.title.y = element_text(size = 17,hjust = 0.5, family="serif")) + 
  theme(axis.text.x = element_text(hjust = 0.5, vjust=0.3,size=13, family="serif"))+
  theme(axis.text.y = element_text(size=13, family="serif"))+
  # theme(panel.grid.major = element_blank()) +
  # theme(panel.grid.minor = element_blank(),panel.background=element_blank(),plot.background=element_blank()) +
  theme(axis.ticks = element_line(size = 1.1))


# color collection
my_color_collection <- c(
  "#CBD588", "#5F7FC7", "orange", "#AD6F3B", "#673770", 
  "#D14285", "#652926", "#C84248", "#8569D5", "#5E738F",
  "#D1A33D", "#8A7C64", "#599861","#616163", "#FFCDB2",
  "#6D9F71", "#242F40",
  "#CCA43B", "#F92A82", "#ED7B84", "#7EB77F", 
  "#DEC4A1", "#E5D1D0", '#0E8482', '#C9DAEA', '#337357', 
  '#95C623', '#E55812', '#04471C', '#F2D7EE', '#D3BCC0', 
  '#A5668B', '#69306D', '#0E103D', '#1A535C', '#4ECDC4', 
  '#F7FFF7', '#FF6B6B', '#FFE66D', '#6699CC', '#FFF275', 
  '#FF8C42', '#FF3C38', '#A23E48', '#000000', '#CF5C36', 
  '#EEE5E9', '#7C7C7C', '#EFC88B', '#2E5266', '#6E8898', 
  '#9FB1BC', '#D3D0CB', '#E2C044', '#5BC0EB', '#FDE74C', 
  '#9BC53D', '#E55934', '#FA7921', "#CD9BCD", "#508578", "#DA5724")

# for git push, use this instead of using wflow_git_push()
# git push -u origin master (in the Git app / in the working directory)

```


## 1. Import data table from python code
```{r}
# import file
df_p0 <- openxlsx::read.xlsx("data/211017_Griess_plate0.xlsx")
df_p1 <- openxlsx::read.xlsx("data/211017_Griess_plate1.xlsx")
df_p2 <- openxlsx::read.xlsx("data/211017_Griess_plate2.xlsx")
df_p3 <- openxlsx::read.xlsx("data/211017_Griess_plate3.xlsx")
df_p4 <- openxlsx::read.xlsx("data/211017_Griess_plate4.xlsx")
df_p5 <- openxlsx::read.xlsx("data/211017_Griess_plate5.xlsx")
df_p6 <- openxlsx::read.xlsx("data/211017_Griess_plate6.xlsx")
df_p7 <- openxlsx::read.xlsx("data/211017_Griess_plate7.xlsx")
df_p8 <- openxlsx::read.xlsx("data/211017_Griess_plate8.xlsx")

head(df_p0)
head(df_p1)
colnames(df_p0)
colnames(df_p1)
dim(df_p0)
dim(df_p1)

# remove wells H06, H09
df_p1 %<>% filter(!(Well %in% c("E03")))
dim(df_p1)
df_p2 %<>% filter(!(Well %in% c("E03")))
dim(df_p2)
df_p3 %<>% filter(!(Well %in% c("A03","A04","A09","A10","H03","H09"))) # leaked during vortexing
dim(df_p3)

df_p4 %<>% filter(!(Well %in% c("A03","A04","A09","A10"))) # leaked during vortexing
dim(df_p4)
df_p5 %<>% filter(!(Well %in% c("A03","A04","A09","A10"))) # leaked during vortexing
dim(df_p5)

# bind two dataframe
df_p <- rbind(df_p0, df_p1, df_p2, df_p3, df_p4, df_p5, df_p6, df_p7, df_p8)
dim(df_p)
24+96*8 -16

colnames(df_p)

# remove NA
dim(df_p)
df_p <- na.omit(df_p)
dim(df_p)

# Check
# df_p %>% filter(Well =="H06")
```

## 2. Get average and standard deviation
```{r}
# average and standard deviation
head(df_p)
dim(df_p)

# plot to see


ggplot(df_p1, aes(x=Nitrate_input, y=NO3_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  scale_fill_brewer(palette='Set2') +
  ylab("NO3- (mM) \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  # scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  ggtitle("Without averaging \n") +
  mytheme_2d

ggplot(df_p2, aes(x=Nitrate_input, y=NO3_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  scale_fill_brewer(palette='Set2') +
  ylab("NO3- (mM) \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  # scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  ggtitle("Without averaging \n") +
  mytheme_2d

ggplot(df_p3, aes(x=Nitrate_input, y=NO3_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  scale_fill_brewer(palette='Set2') +
  ylab("NO3- (mM) \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  # scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  ggtitle("Without averaging \n") +
  mytheme_2d

ggplot(df_p4, aes(x=Nitrate_input, y=NO3_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  scale_fill_brewer(palette='Set2') +
  ylab("NO3- (mM) \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  # scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  ggtitle("Without averaging \n") +
  mytheme_2d

df_p4_1 <- df_p4 %>% filter(Sample_type == "Spike", Extraction_ul ==100) 

ggplot(df_p4_1, aes(x=Nitrate_input, y=NO3_mM, color=Replicate, group=Replicate)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  scale_fill_brewer(palette='Set2') +
  ylab("NO3- (mM) \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  # scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  ggtitle("Without averaging \n") +
  mytheme_2d

ggplot(df_p5, aes(x=Nitrate_input, y=NO3_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  scale_fill_brewer(palette='Set2') +
  ylab("NO3- (mM) \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  # scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  ggtitle("Without averaging \n") +
  mytheme_2d

ggplot(df_p6, aes(x=Nitrate_input, y=NO3_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  scale_fill_brewer(palette='Set2') +
  ylab("NO3- (mM) \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  # scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  ggtitle("Without averaging \n") +
  mytheme_2d

ggplot(df_p7, aes(x=Nitrate_input, y=NO3_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  scale_fill_brewer(palette='Set2') +
  ylab("NO3- (mM) \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  # scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  ggtitle("Without averaging \n") +
  mytheme_2d

ggplot(df_p8, aes(x=Nitrate_input, y=NO3_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  scale_fill_brewer(palette='Set2') +
  ylab("NO3- (mM) \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  # scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  ggtitle("Without averaging \n") +
  mytheme_2d

df_p8_1 <- df_p8 %>% filter(Sample_type == "Spike")
  
  
ggplot(df_p8_1, aes(x=Nitrate_input, y=NO3_mM, color=Extraction_ul, group=Extraction_ul)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  scale_fill_brewer(palette='Set2') +
  ylab("NO3- (mM) \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  # scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  ggtitle("Without averaging \n") +
  mytheme_2d

# average technical replicate
df_NO2NO3 <- df_p %>% group_by(Sample, Extraction_method, Extraction_ul, Nitrate_input, Sample_type, Replicate) %>% summarise(Ave_NO2_mM = mean(NO2_mM), Std_NO2_mM = sd(NO2_mM), Ave_NO2NO3_mM = mean(NO2NO3_mM), Std_NO2NO3_mM = sd(NO2NO3_mM), Ave_NO3_mM = mean(NO3_mM), Std_NO3_mM = sd(NO3_mM)) %>% ungroup()

dim(df_NO2NO3)

# plot to see
ggplot(df_NO2NO3, aes(x=Nitrate_input, y=Ave_NO3_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  geom_errorbar(aes(ymin=Ave_NO3_mM - Std_NO3_mM, ymax=Ave_NO3_mM + Std_NO3_mM), width=.05)+
  scale_fill_brewer(palette='Set2') +
  ylab("NO3- (mM) \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  # scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  ggtitle("After averaging with technical replicates \n") +
  mytheme_2d

# average biological replicates
# standard deviation is the standard deviation of the technical replicate average
dim(df_NO2NO3)
head(df_NO2NO3)

df_ave <- df_NO2NO3 %>% group_by(Sample, Extraction_method, Extraction_ul, Nitrate_input, Sample_type) %>% summarise(NO2_mM = mean(Ave_NO2_mM), sd_NO2_mM = sd(Ave_NO2_mM), NO3_mM = mean(Ave_NO3_mM), sd_NO3_mM = sd(Ave_NO3_mM)) %>% ungroup()

dim(df_ave)

# plot to see
ggplot(df_ave, aes(x=Nitrate_input, y=NO3_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  geom_errorbar(aes(ymin=NO3_mM - sd_NO3_mM, ymax=NO3_mM + sd_NO3_mM), width=.05)+
  scale_fill_brewer(palette='Set2') +
  ylab("NO3- (mM) \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  # scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  ggtitle("Ploting nitrate concentration \n") +
  mytheme_2d

# Factor in orders
# df_all$Sample_type <-  factor(df_all$Sample_type, levels = c("Soil","Blank"))

```

## 3. Plot per method

## 3.1. 1_1_1 method (1g soil, 1ml spike in, 1ml 2M KCl)
```{r}
# (1) 1_1_1 method (1g soil, 1ml spike in, 1ml 2M KCl)
df_111 <- df_ave %>% filter(Extraction_method == "1_1_1")
dim(df_111)

# (1-1) 1_1_1 method (1g soil, 1ml spike in, 1ml 2M KCl) 100ul
df_111_100 <- df_111 %>% filter(Extraction_ul == 100)

ggplot(df_111_100, aes(x=Nitrate_input, y=NO3_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  geom_errorbar(aes(ymin=NO3_mM - sd_NO3_mM, ymax=NO3_mM + sd_NO3_mM), width=.05)+
  # scale_color_brewer(palette='Set2') +
  scale_color_manual(values = c("deepskyblue4","maroon2"))+
  ylab("Measured NO3- (mM) \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  # scale_y_continuous(breaks = seq(0,2.1,0.25), limits=c(0, 2))+
  # scale_x_continuous(breaks = seq(0,2.1,0.25), limits=c(0, 2))+
  ggtitle("1_1_1 method (1g soil, 1ml spike in, 1ml 2M KCl) 100ul \n") +
  geom_abline(slope = 1, intercept=0, show.legend = "y=x")+
  mytheme_2d

# subtract innate nitrate in soil
df_111_100_soil <- df_111_100 %>% filter(Sample_type == "Spike")
innate_no3 <- df_111_100 %>% filter(Sample_type== "Spike", Nitrate_input == 0) %>% select(NO3_mM) %>% unlist()
df_111_100_soil$Retrieved_NO3_mM <- df_111_100_soil$NO3_mM - innate_no3

ggplot(df_111_100_soil, aes(x=Nitrate_input, y=Retrieved_NO3_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  geom_errorbar(aes(ymin=Retrieved_NO3_mM - sd_NO3_mM, ymax=Retrieved_NO3_mM + sd_NO3_mM), width=.05)+
  # scale_fill_brewer(palette='Set2') +
  scale_color_manual(values = c("brown3","deepskyblue2"))+
  ylab("Retrieved NO3 concentrations (mM) \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  # scale_y_continuous(breaks = seq(0,2.1,0.25), limits=c(0, 2))+
  # scale_x_continuous(breaks = seq(0,2.1,0.25), limits=c(0, 2))+
  ggtitle("1_1_1 method (1g soil, 1ml spike in, 1ml 2M KCl) 100ul \n") +
  geom_abline(slope = 1, intercept=0, show.legend = "y=x")+
  mytheme_2d

# Retrieved ratio of spike ins
df_111_100_soil$Ratio_retrieved <- df_111_100_soil$Retrieved_NO3_mM / df_111_100_soil$Nitrate_input 

ggplot(df_111_100_soil, aes(x=Nitrate_input, y=Ratio_retrieved)) +  ## I put fill=value which was wrong
  geom_bar(stat="identity",position="dodge", fill="brown3")+
  geom_line(size=0.2, color="brown")+
  ylab("Ratio of retrieved nitrate concentraion \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  # scale_y_continuous(breaks = seq(0,1,0.1), limits=c(0, 1))+
  # scale_x_continuous(breaks = seq(0,2.1,0.25), limits=c(0, 2.1))+
  ggtitle("1_1_1 method (1g soil, 1ml spike in, 1ml 2M KCl) 100ul \n") +
  geom_text(aes(label = round(Ratio_retrieved,3)), size = 3, vjust = -1.5, family="serif", show.legend = FALSE)+
  mytheme_2d

```

```{r}
# (1) 1_1_1 method (1g soil, 1ml spike in, 1ml 2M KCl)
df_111 <- df_ave %>% filter(Extraction_method == "1_1_1")
dim(df_111)

# (1-2) 1_1_1 method (1g soil, 1ml spike in, 1ml 2M KCl) 300ul
df_111_300 <- df_111 %>% filter(Extraction_ul == 300)

ggplot(df_111_300, aes(x=Nitrate_input, y=NO3_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  geom_errorbar(aes(ymin=NO3_mM - sd_NO3_mM, ymax=NO3_mM + sd_NO3_mM), width=.05)+
  # scale_color_brewer(palette='Set2') +
  scale_color_manual(values = c("deepskyblue4","maroon2"))+
  ylab("Measured NO3- (mM) \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  # scale_y_continuous(breaks = seq(0,2.1,0.25), limits=c(0, 2))+
  # scale_x_continuous(breaks = seq(0,2.1,0.25), limits=c(0, 2))+
  ggtitle("1_1_1 method (1g soil, 1ml spike in, 1ml 2M KCl) 300ul \n") +
  geom_abline(slope = 1, intercept=0, show.legend = "y=x")+
  mytheme_2d

# subtract innate nitrate in soil
df_111_300_soil <- df_111_300 %>% filter(Sample_type == "Spike")
innate_no3 <- df_111_300 %>% filter(Sample_type== "Spike", Nitrate_input == 0) %>% select(NO3_mM) %>% unlist()
df_111_300_soil$Retrieved_NO3_mM <- df_111_300_soil$NO3_mM - innate_no3

ggplot(df_111_300_soil, aes(x=Nitrate_input, y=Retrieved_NO3_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  geom_errorbar(aes(ymin=Retrieved_NO3_mM - sd_NO3_mM, ymax=Retrieved_NO3_mM + sd_NO3_mM), width=.05)+
  # scale_fill_brewer(palette='Set2') +
  scale_color_manual(values = c("brown3","deepskyblue2"))+
  ylab("Retrieved NO3 concentrations (mM) \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  # scale_y_continuous(breaks = seq(0,2.1,0.25), limits=c(0, 2))+
  # scale_x_continuous(breaks = seq(0,2.1,0.25), limits=c(0, 2))+
  ggtitle("1_1_1 method (1g soil, 1ml spike in, 1ml 2M KCl) 300ul \n") +
  geom_abline(slope = 1, intercept=0, show.legend = "y=x")+
  mytheme_2d

# Retrieved ratio of spike ins
df_111_300_soil$Ratio_retrieved <- df_111_300_soil$Retrieved_NO3_mM / df_111_300_soil$Nitrate_input 

ggplot(df_111_300_soil, aes(x=Nitrate_input, y=Ratio_retrieved)) +  ## I put fill=value which was wrong
  geom_bar(stat="identity",position="dodge", fill="brown3")+
  geom_line(size=0.2, color="brown")+
  ylab("Ratio of retrieved nitrate concentraion \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  # scale_y_continuous(breaks = seq(0,1,0.1), limits=c(0, 1))+
  # scale_x_continuous(breaks = seq(0,2.1,0.25), limits=c(0, 2.1))+
  ggtitle("1_1_1 method (1g soil, 1ml spike in, 1ml 2M KCl) 300ul \n") +
  geom_text(aes(label = round(Ratio_retrieved,3)), size = 3, vjust = -1.5, family="serif", show.legend = FALSE)+
  mytheme_2d
```

Compare same spike in concentrations but different ul
```{r}
# (1) 1_1_1 method (1g soil, 1ml spike in, 1ml 2M KCl)

# subtract innate nitrate in soil
df_111_full <- df_111 %>% filter(!(Extraction_ul %in% c(50, 100, 300)))
df_111_full_soil <- df_111_full %>% filter(Sample_type == "Spike")
# would have to use innate_no3 from 300ul
df_111_full_soil$Retrieved_NO3_mM <- df_111_full_soil$NO3_mM - innate_no3
# Retrieved ratio of spike ins
df_111_full_soil$Ratio_retrieved <- df_111_full_soil$Retrieved_NO3_mM / df_111_full_soil$Nitrate_input 

# import new data from 211019
df_full_innate <- openxlsx::read.xlsx("data/211020_df_full_innate.xlsx")
df_full_innate %<>% select(-Trouble_shooting, -Ave_NO2NO3_mM, -Std_NO2NO3_mM, -Innate_NO3_mM) %>% rename(NO2_mM = Ave_NO2_mM, NO3_mM = Ave_NO3_mM, sd_NO2_mM = Std_NO2_mM, sd_NO3_mM = Std_NO3_mM)

colnames(df_111_300_soil)
colnames(df_full_innate)

df_111_full_soil <- df_full_innate %>% filter(Extraction_method == "1_1_1")

df_111_retrieved <- rbind(df_111_100_soil, df_111_300_soil, df_111_full_soil)
df_111_retrieved$Extraction_ul <- factor(df_111_retrieved$Extraction_ul)
ggplot(df_111_retrieved, aes(x=Nitrate_input, y=Retrieved_NO3_mM, color=Extraction_ul, group=Extraction_ul)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  geom_errorbar(aes(ymin=Retrieved_NO3_mM - sd_NO3_mM, ymax=Retrieved_NO3_mM + sd_NO3_mM), width=.05)+
  scale_color_brewer(palette='Set1') +
  # scale_color_manual(values = c("brown3","deepskyblue2"))+
  ylab("Retrieved NO3 concentrations (mM) \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  # scale_y_continuous(breaks = seq(0,2.1,0.25), limits=c(0, 2))+
  # scale_x_continuous(breaks = seq(0,2.1,0.25), limits=c(0, 2))+
  ggtitle("1_1_1 method (1g soil, 1ml spike in, 1ml 2M KCl) 300ul \n") +
  geom_abline(slope = 1, intercept=0, show.legend = "y=x")+
  mytheme_2d

# Retrieved ratio of spike ins
df_111_retrieved$Nitrate_input <- factor(df_111_retrieved$Nitrate_input)

ggplot(df_111_retrieved, aes(x=Nitrate_input, y=Ratio_retrieved, fill=Extraction_ul, group=Extraction_ul)) +  ## I put fill=value which was wrong
  geom_bar(stat="identity",position="dodge")+
  # geom_line(size=0.2, color="brown")+
  ylab("Ratio of retrieved NO3 concentraion \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  # scale_y_continuous(breaks = seq(0,1,0.1), limits=c(0, 1))+
  # scale_x_continuous(breaks = seq(0,2.1,0.25), limits=c(0, 2.1))+
  ggtitle("1_1_1 method (1g soil, 1ml spike in, 1ml 2M KCl) \n") +
  geom_text(aes(label = round(Ratio_retrieved,3)), size = 3, vjust = -1.5, family="serif", show.legend = FALSE, position = position_dodge(width = .9))+
  mytheme_2d

```


## 3.2. 0.5_1_1.5 method (1g soil, 1ml spike in, 4ml 2.5M KCl)

```{r}
# (2) 1_1_4 method (1g soil, 1ml spike in, 4ml 2.5M KCl)
df_114 <- df_ave %>% filter(Extraction_method == "1_1_4")
dim(df_114)

# (2-1) 1_1_4 method (1g soil, 1ml spike in, 4ml 2.5M KCl) 50ul
df_114_50 <- df_114 %>% filter(Extraction_ul == 50)

ggplot(df_114_50, aes(x=Nitrate_input, y=NO3_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  geom_errorbar(aes(ymin=NO3_mM - sd_NO3_mM, ymax=NO3_mM + sd_NO3_mM), width=.05)+
  # scale_color_brewer(palette='Set2') +
  scale_color_manual(values = c("deepskyblue4","maroon2"))+
  ylab("Measured NO3- (mM) \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  # scale_y_continuous(breaks = seq(0,2.1,0.25), limits=c(0, 2))+
  # scale_x_continuous(breaks = seq(0,2.1,0.25), limits=c(0, 2))+
  ggtitle("1_1_4 method (1g soil, 1ml spike in, 4ml 2.5M KCl) 50ul \n") +
  geom_abline(slope = 1, intercept=0, show.legend = "y=x")+
  mytheme_2d

# subtract innate nitrate in soil
df_114_50_soil <- df_114_50 %>% filter(Sample_type == "Spike")
innate_no3 <- df_114_50 %>% filter(Sample_type== "Spike", Nitrate_input == 0) %>% select(NO3_mM) %>% unlist()
df_114_50_soil$Retrieved_NO3_mM <- df_114_50_soil$NO3_mM - innate_no3

ggplot(df_114_50_soil, aes(x=Nitrate_input, y=Retrieved_NO3_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  geom_errorbar(aes(ymin=Retrieved_NO3_mM - sd_NO3_mM, ymax=Retrieved_NO3_mM + sd_NO3_mM), width=.05)+
  # scale_fill_brewer(palette='Set2') +
  scale_color_manual(values = c("brown3","deepskyblue2"))+
  ylab("Retrieved NO3 concentrations (mM) \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  # scale_y_continuous(breaks = seq(0,2.1,0.25), limits=c(0, 2))+
  # scale_x_continuous(breaks = seq(0,2.1,0.25), limits=c(0, 2))+
  ggtitle("1_1_4 method (1g soil, 1ml spike in, 4ml 2.5M KCl) 50ul \n") +
  geom_abline(slope = 1, intercept=0, show.legend = "y=x")+
  mytheme_2d

# Retrieved ratio of spike ins
df_114_50_soil$Ratio_retrieved <- df_114_50_soil$Retrieved_NO3_mM / df_114_50_soil$Nitrate_input 

ggplot(df_114_50_soil, aes(x=Nitrate_input, y=Ratio_retrieved)) +  ## I put fill=value which was wrong
  geom_bar(stat="identity",position="dodge", fill="brown3")+
  geom_line(size=0.2, color="brown")+
  ylab("Ratio of retrieved nitrate concentraion \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  # scale_y_continuous(breaks = seq(0,1,0.1), limits=c(0, 1))+
  # scale_x_continuous(breaks = seq(0,2.1,0.25), limits=c(0, 2.1))+
  ggtitle("1_1_4 method (1g soil, 1ml spike in, 4ml 2.5M KCl) 50ul \n") +
  geom_text(aes(label = round(Ratio_retrieved,3)), size = 3, vjust = -1.5, family="serif", show.legend = FALSE)+
  mytheme_2d
```



```{r}
# (2-2) 1_1_4 method (1g soil, 1ml spike in, 4ml 2.5M KCl) 100ul
df_114_100 <- df_114 %>% filter(Extraction_ul == 100)

ggplot(df_114_100, aes(x=Nitrate_input, y=NO3_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  geom_errorbar(aes(ymin=NO3_mM - sd_NO3_mM, ymax=NO3_mM + sd_NO3_mM), width=.05)+
  # scale_color_brewer(palette='Set2') +
  scale_color_manual(values = c("deepskyblue4","maroon2"))+
  ylab("Measured NO3- (mM) \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  # scale_y_continuous(breaks = seq(0,2.1,0.25), limits=c(0, 2))+
  # scale_x_continuous(breaks = seq(0,2.1,0.25), limits=c(0, 2))+
  ggtitle("1_1_4 method (1g soil, 1ml spike in, 4ml 2.5M KCl) 100ul \n") +
  geom_abline(slope = 1, intercept=0, show.legend = "y=x")+
  mytheme_2d

# subtract innate nitrate in soil
df_114_100_soil <- df_114_100 %>% filter(Sample_type == "Spike")
innate_no3 <- df_114_100 %>% filter(Sample_type== "Spike", Nitrate_input == 0) %>% select(NO3_mM) %>% unlist()
df_114_100_soil$Retrieved_NO3_mM <- df_114_100_soil$NO3_mM - innate_no3

ggplot(df_114_100_soil, aes(x=Nitrate_input, y=Retrieved_NO3_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  geom_errorbar(aes(ymin=Retrieved_NO3_mM - sd_NO3_mM, ymax=Retrieved_NO3_mM + sd_NO3_mM), width=.05)+
  # scale_fill_brewer(palette='Set2') +
  scale_color_manual(values = c("brown3","deepskyblue2"))+
  ylab("Retrieved NO3 concentrations (mM) \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  # scale_y_continuous(breaks = seq(0,2.1,0.25), limits=c(0, 2))+
  # scale_x_continuous(breaks = seq(0,2.1,0.25), limits=c(0, 2))+
  ggtitle("1_1_4 method (1g soil, 1ml spike in, 4ml 2.5M KCl) 100ul \n") +
  geom_abline(slope = 1, intercept=0, show.legend = "y=x")+
  mytheme_2d

# Retrieved ratio of spike ins
df_114_100_soil$Ratio_retrieved <- df_114_100_soil$Retrieved_NO3_mM / df_114_100_soil$Nitrate_input 

ggplot(df_114_100_soil, aes(x=Nitrate_input, y=Ratio_retrieved)) +  ## I put fill=value which was wrong
  geom_bar(stat="identity",position="dodge", fill="brown3")+
  geom_line(size=0.2, color="brown")+
  ylab("Ratio of retrieved nitrate concentraion \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  # scale_y_continuous(breaks = seq(0,1,0.1), limits=c(0, 1))+
  # scale_x_continuous(breaks = seq(0,2.1,0.25), limits=c(0, 2.1))+
  ggtitle("1_1_4 method (1g soil, 1ml spike in, 4ml 2.5M KCl) 100ul \n") +
  geom_text(aes(label = round(Ratio_retrieved,3)), size = 3, vjust = -1.5, family="serif", show.legend = FALSE)+
  mytheme_2d

```

```{r}
# (2-3) 1_1_4 method (1g soil, 1ml spike in, 1ml 2M KCl) 300ul
df_114_300 <- df_114 %>% filter(Extraction_ul == 300)

ggplot(df_114_300, aes(x=Nitrate_input, y=NO3_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  geom_errorbar(aes(ymin=NO3_mM - sd_NO3_mM, ymax=NO3_mM + sd_NO3_mM), width=.05)+
  # scale_color_brewer(palette='Set2') +
  scale_color_manual(values = c("deepskyblue4","maroon2"))+
  ylab("Measured NO3- (mM) \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  # scale_y_continuous(breaks = seq(0,2.1,0.25), limits=c(0, 2))+
  # scale_x_continuous(breaks = seq(0,2.1,0.25), limits=c(0, 2))+
  ggtitle("1_1_4 method (1g soil, 1ml spike in, 4ml 2.5M KCl) 300ul \n") +
  geom_abline(slope = 1, intercept=0, show.legend = "y=x")+
  mytheme_2d

# subtract innate nitrate in soil
df_114_300_soil <- df_114_300 %>% filter(Sample_type == "Spike")
innate_no3 <- df_114_300 %>% filter(Sample_type== "Spike", Nitrate_input == 0) %>% select(NO3_mM) %>% unlist()
df_114_300_soil$Retrieved_NO3_mM <- df_114_300_soil$NO3_mM - innate_no3

ggplot(df_114_300_soil, aes(x=Nitrate_input, y=Retrieved_NO3_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  geom_errorbar(aes(ymin=Retrieved_NO3_mM - sd_NO3_mM, ymax=Retrieved_NO3_mM + sd_NO3_mM), width=.05)+
  # scale_fill_brewer(palette='Set2') +
  scale_color_manual(values = c("brown3","deepskyblue2"))+
  ylab("Retrieved NO3 concentrations (mM) \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  # scale_y_continuous(breaks = seq(0,2.1,0.25), limits=c(0, 2))+
  # scale_x_continuous(breaks = seq(0,2.1,0.25), limits=c(0, 2))+
  ggtitle("1_1_4 method (1g soil, 1ml spike in, 4ml 2.5M KCl) 300ul \n") +
  geom_abline(slope = 1, intercept=0, show.legend = "y=x")+
  mytheme_2d

# Retrieved ratio of spike ins
df_114_300_soil$Ratio_retrieved <- df_114_300_soil$Retrieved_NO3_mM / df_114_300_soil$Nitrate_input 

ggplot(df_114_300_soil, aes(x=Nitrate_input, y=Ratio_retrieved)) +  ## I put fill=value which was wrong
  geom_bar(stat="identity",position="dodge", fill="brown3")+
  geom_line(size=0.2, color="brown")+
  ylab("Ratio of retrieved nitrate concentraion \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  # scale_y_continuous(breaks = seq(0,1,0.1), limits=c(0, 1))+
  # scale_x_continuous(breaks = seq(0,2.1,0.25), limits=c(0, 2.1))+
  ggtitle("1_1_4 method (1g soil, 1ml spike in, 4ml 2.5M KCl) 300ul \n") +
  geom_text(aes(label = round(Ratio_retrieved,3)), size = 3, vjust = -1.5, family="serif", show.legend = FALSE)+
  mytheme_2d
```

Compare same spike in concentrations but different ul
```{r}
# (2) 1_1_4 method (1g soil, 1ml spike in, 1ml 2M KCl)

# subtract innate nitrate in soil
df_114_full <- df_114 %>% filter(!(Extraction_ul %in% c(50, 100, 300)))
df_114_full_soil <- df_114_full %>% filter(Sample_type == "Spike")
# would have to use innate_no3 from 300ul
df_114_full_soil$Retrieved_NO3_mM <- df_114_full_soil$NO3_mM - innate_no3
# Retrieved ratio of spike ins
df_114_full_soil$Ratio_retrieved <- df_114_full_soil$Retrieved_NO3_mM / df_114_full_soil$Nitrate_input 

# update with 211019 data
df_114_full_soil <- df_full_innate %>% filter(Extraction_method == "1_1_4")

df_114_retrieved <- rbind(df_114_50_soil, df_114_100_soil, df_114_300_soil, df_114_full_soil)
df_114_retrieved$Extraction_ul <- factor(df_114_retrieved$Extraction_ul)
ggplot(df_114_retrieved, aes(x=Nitrate_input, y=Retrieved_NO3_mM, color=Extraction_ul, group=Extraction_ul)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  geom_errorbar(aes(ymin=Retrieved_NO3_mM - sd_NO3_mM, ymax=Retrieved_NO3_mM + sd_NO3_mM), width=.05)+
  scale_color_brewer(palette='Set1') +
  # scale_color_manual(values = c("brown3","deepskyblue2"))+
  ylab("Retrieved NO3 concentrations (mM) \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  # scale_y_continuous(breaks = seq(0,2.1,0.25), limits=c(0, 2))+
  # scale_x_continuous(breaks = seq(0,2.1,0.25), limits=c(0, 2))+
  ggtitle("1_1_4 method (1g soil, 1ml spike in, 4ml 2.5M KCl) \n") +
  geom_abline(slope = 1, intercept=0, show.legend = "y=x")+
  mytheme_2d

# Retrieved ratio of spike ins
df_114_retrieved$Nitrate_input <- factor(df_114_retrieved$Nitrate_input)

ggplot(df_114_retrieved, aes(x=Nitrate_input, y=Ratio_retrieved, fill=Extraction_ul, group=Extraction_ul)) +  ## I put fill=value which was wrong
  geom_bar(stat="identity",position="dodge")+
  # geom_line(size=0.2, color="brown")+
  ylab("Ratio of retrieved NO3 concentraion \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  # scale_y_continuous(breaks = seq(0,1,0.1), limits=c(0, 1))+
  # scale_x_continuous(breaks = seq(0,2.1,0.25), limits=c(0, 2.1))+
  ggtitle("1_1_4 method (1g soil, 1ml spike in, 4ml 2.5M KCl) \n") +
  geom_text(aes(label = round(Ratio_retrieved,3)), size = 3, vjust = -1.5, family="serif", show.legend = FALSE, position = position_dodge(width = .9))+
  mytheme_2d

```

## 3.3. 0.5_1_1.5 method (0.5g soil, 1ml spike in, 1.5ml 3.3M KCl)

```{r}
# (2) 0.5_1_1.5 method (0.5g soil, 1ml spike in, 1.5ml 3.3M KCl)
df_05115 <- df_ave %>% filter(Extraction_method == "0.5_1_1.5")
dim(df_05115)

# (2-1) 0.5_1_1.5 method (0.5g soil, 1ml spike in, 1.5ml 3.3M KCl) 50ul
df_05115_50 <- df_05115 %>% filter(Extraction_ul == 50)

ggplot(df_05115_50, aes(x=Nitrate_input, y=NO3_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  geom_errorbar(aes(ymin=NO3_mM - sd_NO3_mM, ymax=NO3_mM + sd_NO3_mM), width=.05)+
  # scale_color_brewer(palette='Set2') +
  scale_color_manual(values = c("deepskyblue4","maroon2"))+
  ylab("Measured NO3- (mM) \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  # scale_y_continuous(breaks = seq(0,2.1,0.25), limits=c(0, 2))+
  # scale_x_continuous(breaks = seq(0,2.1,0.25), limits=c(0, 2))+
  ggtitle("0.5_1_1.5 method (0.5g soil, 1ml spike in, 1.5ml 3.3M KCl) 50ul \n") +
  geom_abline(slope = 1, intercept=0, show.legend = "y=x")+
  mytheme_2d

# subtract innate nitrate in soil
df_05115_50_soil <- df_05115_50 %>% filter(Sample_type == "Spike")
innate_no3 <- df_05115_50 %>% filter(Sample_type== "Spike", Nitrate_input == 0) %>% select(NO3_mM) %>% unlist()
df_05115_50_soil$Retrieved_NO3_mM <- df_05115_50_soil$NO3_mM - innate_no3

ggplot(df_05115_50_soil, aes(x=Nitrate_input, y=Retrieved_NO3_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  geom_errorbar(aes(ymin=Retrieved_NO3_mM - sd_NO3_mM, ymax=Retrieved_NO3_mM + sd_NO3_mM), width=.05)+
  # scale_fill_brewer(palette='Set2') +
  scale_color_manual(values = c("brown3","deepskyblue2"))+
  ylab("Retrieved NO3 concentrations (mM) \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  # scale_y_continuous(breaks = seq(0,2.1,0.25), limits=c(0, 2))+
  # scale_x_continuous(breaks = seq(0,2.1,0.25), limits=c(0, 2))+
  ggtitle("0.5_1_1.5 method (0.5g soil, 1ml spike in, 1.5ml 3.3M KCl) 50ul \n") +
  geom_abline(slope = 1, intercept=0, show.legend = "y=x")+
  mytheme_2d

# Retrieved ratio of spike ins
df_05115_50_soil$Ratio_retrieved <- df_05115_50_soil$Retrieved_NO3_mM / df_05115_50_soil$Nitrate_input 

ggplot(df_05115_50_soil, aes(x=Nitrate_input, y=Ratio_retrieved)) +  ## I put fill=value which was wrong
  geom_bar(stat="identity",position="dodge", fill="brown3")+
  geom_line(size=0.2, color="brown")+
  ylab("Ratio of retrieved nitrate concentraion \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  # scale_y_continuous(breaks = seq(0,1,0.1), limits=c(0, 1))+
  # scale_x_continuous(breaks = seq(0,2.1,0.25), limits=c(0, 2.1))+
  ggtitle("0.5_1_1.5 method (0.5g soil, 1ml spike in, 1.5ml 3.3M KCl) 50ul \n") +
  geom_text(aes(label = round(Ratio_retrieved,3)), size = 3, vjust = -1.5, family="serif", show.legend = FALSE)+
  mytheme_2d
```



```{r}
# (2-2) 0.5_1_1.5 method (0.5g soil, 1ml spike in, 1.5ml 3.3M KCl) 100ul
df_05115_100 <- df_05115 %>% filter(Extraction_ul == 100)

ggplot(df_05115_100, aes(x=Nitrate_input, y=NO3_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  geom_errorbar(aes(ymin=NO3_mM - sd_NO3_mM, ymax=NO3_mM + sd_NO3_mM), width=.05)+
  # scale_color_brewer(palette='Set2') +
  scale_color_manual(values = c("deepskyblue4","maroon2"))+
  ylab("Measured NO3- (mM) \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  # scale_y_continuous(breaks = seq(0,2.1,0.25), limits=c(0, 2))+
  # scale_x_continuous(breaks = seq(0,2.1,0.25), limits=c(0, 2))+
  ggtitle("0.5_1_1.5 method (0.5g soil, 1ml spike in, 1.5ml 3.3M KCl) 100ul \n") +
  geom_abline(slope = 1, intercept=0, show.legend = "y=x")+
  mytheme_2d

# subtract innate nitrate in soil
df_05115_100_soil <- df_05115_100 %>% filter(Sample_type == "Spike")
innate_no3 <- df_05115_100 %>% filter(Sample_type== "Spike", Nitrate_input == 0) %>% select(NO3_mM) %>% unlist()
df_05115_100_soil$Retrieved_NO3_mM <- df_05115_100_soil$NO3_mM - innate_no3

ggplot(df_05115_100_soil, aes(x=Nitrate_input, y=Retrieved_NO3_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  geom_errorbar(aes(ymin=Retrieved_NO3_mM - sd_NO3_mM, ymax=Retrieved_NO3_mM + sd_NO3_mM), width=.05)+
  # scale_fill_brewer(palette='Set2') +
  scale_color_manual(values = c("brown3","deepskyblue2"))+
  ylab("Retrieved NO3 concentrations (mM) \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  # scale_y_continuous(breaks = seq(0,2.1,0.25), limits=c(0, 2))+
  # scale_x_continuous(breaks = seq(0,2.1,0.25), limits=c(0, 2))+
  ggtitle("0.5_1_1.5 method (0.5g soil, 1ml spike in, 1.5ml 3.3M KCl) 100ul \n") +
  geom_abline(slope = 1, intercept=0, show.legend = "y=x")+
  mytheme_2d

# Retrieved ratio of spike ins
df_05115_100_soil$Ratio_retrieved <- df_05115_100_soil$Retrieved_NO3_mM / df_05115_100_soil$Nitrate_input 

ggplot(df_05115_100_soil, aes(x=Nitrate_input, y=Ratio_retrieved)) +  ## I put fill=value which was wrong
  geom_bar(stat="identity",position="dodge", fill="brown3")+
  geom_line(size=0.2, color="brown")+
  ylab("Ratio of retrieved nitrate concentraion \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  # scale_y_continuous(breaks = seq(0,1,0.1), limits=c(0, 1))+
  # scale_x_continuous(breaks = seq(0,2.1,0.25), limits=c(0, 2.1))+
  ggtitle("0.5_1_1.5 method (0.5g soil, 1ml spike in, 1.5ml 3.3M KCl) 100ul \n") +
  geom_text(aes(label = round(Ratio_retrieved,3)), size = 3, vjust = -1.5, family="serif", show.legend = FALSE)+
  mytheme_2d

```

```{r}
# (2-3) 0.5_1_1.5 method (1g soil, 1ml spike in, 1ml 2M KCl) 300ul
df_05115_300 <- df_05115 %>% filter(Extraction_ul == 300)

ggplot(df_05115_300, aes(x=Nitrate_input, y=NO3_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  geom_errorbar(aes(ymin=NO3_mM - sd_NO3_mM, ymax=NO3_mM + sd_NO3_mM), width=.05)+
  # scale_color_brewer(palette='Set2') +
  scale_color_manual(values = c("deepskyblue4","maroon2"))+
  ylab("Measured NO3- (mM) \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  # scale_y_continuous(breaks = seq(0,2.1,0.25), limits=c(0, 2))+
  # scale_x_continuous(breaks = seq(0,2.1,0.25), limits=c(0, 2))+
  ggtitle("0.5_1_1.5 method (0.5g soil, 1ml spike in, 1.5ml 3.3M KCl) 300ul \n") +
  geom_abline(slope = 1, intercept=0, show.legend = "y=x")+
  mytheme_2d

# subtract innate nitrate in soil
df_05115_300_soil <- df_05115_300 %>% filter(Sample_type == "Spike")
innate_no3 <- df_05115_300 %>% filter(Sample_type== "Spike", Nitrate_input == 0) %>% select(NO3_mM) %>% unlist()
df_05115_300_soil$Retrieved_NO3_mM <- df_05115_300_soil$NO3_mM - innate_no3

ggplot(df_05115_300_soil, aes(x=Nitrate_input, y=Retrieved_NO3_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  geom_errorbar(aes(ymin=Retrieved_NO3_mM - sd_NO3_mM, ymax=Retrieved_NO3_mM + sd_NO3_mM), width=.05)+
  # scale_fill_brewer(palette='Set2') +
  scale_color_manual(values = c("brown3","deepskyblue2"))+
  ylab("Retrieved NO3 concentrations (mM) \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  # scale_y_continuous(breaks = seq(0,2.1,0.25), limits=c(0, 2))+
  # scale_x_continuous(breaks = seq(0,2.1,0.25), limits=c(0, 2))+
  ggtitle("0.5_1_1.5 method (0.5g soil, 1ml spike in, 1.5ml 3.3M KCl) 300ul \n") +
  geom_abline(slope = 1, intercept=0, show.legend = "y=x")+
  mytheme_2d

# Retrieved ratio of spike ins
df_05115_300_soil$Ratio_retrieved <- df_05115_300_soil$Retrieved_NO3_mM / df_05115_300_soil$Nitrate_input 

ggplot(df_05115_300_soil, aes(x=Nitrate_input, y=Ratio_retrieved)) +  ## I put fill=value which was wrong
  geom_bar(stat="identity",position="dodge", fill="brown3")+
  geom_line(size=0.2, color="brown")+
  ylab("Ratio of retrieved nitrate concentraion \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  # scale_y_continuous(breaks = seq(0,1,0.1), limits=c(0, 1))+
  # scale_x_continuous(breaks = seq(0,2.1,0.25), limits=c(0, 2.1))+
  ggtitle("0.5_1_1.5 method (0.5g soil, 1ml spike in, 1.5ml 3.3M KCl) 300ul \n") +
  geom_text(aes(label = round(Ratio_retrieved,3)), size = 3, vjust = -1.5, family="serif", show.legend = FALSE)+
  mytheme_2d
```

Compare same spike in concentrations but different ul
```{r}
# (2) 0.5_1_1.5 method (1g soil, 1ml spike in, 1ml 2M KCl)

# subtract innate nitrate in soil
df_05115_full <- df_05115 %>% filter(!(Extraction_ul %in% c(50, 100, 300)))
df_05115_full_soil <- df_05115_full %>% filter(Sample_type == "Spike")
# would have to use innate_no3 from 300ul
df_05115_full_soil$Retrieved_NO3_mM <- df_05115_full_soil$NO3_mM - innate_no3
# Retrieved ratio of spike ins
df_05115_full_soil$Ratio_retrieved <- df_05115_full_soil$Retrieved_NO3_mM / df_05115_full_soil$Nitrate_input 

# update with 211019 data
df_05115_full_soil <- df_full_innate %>% filter(Extraction_method == "0.5_1_1.5")

# 50ul data seems to be messed up
df_05115_retrieved <- rbind(df_05115_50_soil, df_05115_100_soil, df_05115_300_soil, df_05115_full_soil)
df_05115_retrieved$Extraction_ul <- factor(df_05115_retrieved$Extraction_ul)
ggplot(df_05115_retrieved, aes(x=Nitrate_input, y=Retrieved_NO3_mM, color=Extraction_ul, group=Extraction_ul)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  geom_errorbar(aes(ymin=Retrieved_NO3_mM - sd_NO3_mM, ymax=Retrieved_NO3_mM + sd_NO3_mM), width=.05)+
  scale_color_brewer(palette='Set1') +
  # scale_color_manual(values = c("brown3","deepskyblue2"))+
  ylab("Retrieved NO3 concentrations (mM) \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  # scale_y_continuous(breaks = seq(0,2.1,0.25), limits=c(0, 2))+
  # scale_x_continuous(breaks = seq(0,2.1,0.25), limits=c(0, 2))+
  ggtitle("0.5_1_1.5 method (0.5g soil, 1ml spike in, 1.5ml 3.3M KCl) \n") +
  geom_abline(slope = 1, intercept=0, show.legend = "y=x")+
  mytheme_2d

# Retrieved ratio of spike ins
df_05115_retrieved$Nitrate_input <- factor(df_05115_retrieved$Nitrate_input)

ggplot(df_05115_retrieved, aes(x=Nitrate_input, y=Ratio_retrieved, fill=Extraction_ul, group=Extraction_ul)) +  ## I put fill=value which was wrong
  geom_bar(stat="identity",position="dodge")+
  # geom_line(size=0.2, color="brown")+
  ylab("Ratio of retrieved NO3 concentraion \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  # scale_y_continuous(breaks = seq(0,1,0.1), limits=c(0, 1))+
  # scale_x_continuous(breaks = seq(0,2.1,0.25), limits=c(0, 2.1))+
  ggtitle("0.5_1_1.5 method (0.5g soil, 1ml spike in, 1.5ml 3.3M KCl) \n") +
  geom_text(aes(label = round(Ratio_retrieved,3)), size = 3, vjust = -1.5, family="serif", show.legend = FALSE, position = position_dodge(width = .9))+
  mytheme_2d

# plot except for the 50ul
df_05115_retrieved %<>% filter(!(Extraction_ul == 50))

ggplot(df_05115_retrieved, aes(x=Nitrate_input, y=Ratio_retrieved, fill=Extraction_ul, group=Extraction_ul)) +  ## I put fill=value which was wrong
  geom_bar(stat="identity",position="dodge")+
  # geom_line(size=0.2, color="brown")+
  ylab("Ratio of retrieved NO3 concentraion \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  # scale_y_continuous(breaks = seq(0,1,0.1), limits=c(0, 1))+
  # scale_x_continuous(breaks = seq(0,2.1,0.25), limits=c(0, 2.1))+
  ggtitle("0.5_1_1.5 method (0.5g soil, 1ml spike in, 1.5ml 3.3M KCl) \n") +
  geom_text(aes(label = round(Ratio_retrieved,3)), size = 3, vjust = -1.5, family="serif", show.legend = FALSE, position = position_dodge(width = .9))+
  mytheme_2d

```







