---
title: "211128_Griess_time_series_3soil"
author: "KiseokUchicago"
date: "2021-11-29"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=11, fig.height=9,
                      error=TRUE, echo=TRUE, eval=TRUE, warning=FALSE, message=FALSE)
```

## Time series analysis - 3 soil (Griess assay)
Researcher: **Kiseok Lee** \
Experiment Date: 11/12/21 - 11/26/21 (2 weeks) \
Analysis Date: 11/28/21
Lab: **Seppe Kuehn**

```{r}
# libraries
library(dplyr)
library(ggplot2)
library(RColorBrewer)
library(vegan)
library(tidyverse)
library(magrittr)
library(readxl)
library(reshape2)
library(gtools)
library(devtools)
library(openxlsx)
library(ape)
library(stringr)
library(tidyr)
library(ggrepel)
library(ggpubr)

## theme for ggplot
mytheme <- theme_bw() + 
  theme(text = element_text(family="serif")) +
  theme(plot.title = element_text(size = 19,hjust = 0.5, family="serif")) + 
  theme(axis.title.x = element_text(size = 17,hjust = 0.5, family="serif")) + 
  theme(axis.title.y = element_text(size = 17,hjust = 0.5, family="serif")) + 
  theme(axis.text.x = element_text(hjust = 0.5, vjust=0.3,size=13, family="serif"))+
  theme(axis.text.y = element_text(size=10, family="serif"))+
  theme(panel.grid.major = element_blank()) +
  theme(panel.grid.minor = element_blank(),panel.background=element_blank(),panel.border=element_blank(),plot.background=element_blank()) +
  theme(axis.ticks = element_line(size = 1.1))

mytheme_2d <- theme_bw() + 
  theme(text = element_text(family="serif")) +
  theme(plot.title = element_text(size = 19,hjust = 0.5, family="serif")) + 
  theme(axis.title.x = element_text(size = 17,hjust = 0.5, family="serif")) + 
  theme(axis.title.y = element_text(size = 17,hjust = 0.5, family="serif")) + 
  theme(axis.text.x = element_text(hjust = 0.5, vjust=0.3,size=13, family="serif"))+
  theme(axis.text.y = element_text(size=13, family="serif"))+
  # theme(panel.grid.major = element_blank()) +
  # theme(panel.grid.minor = element_blank(),panel.background=element_blank(),plot.background=element_blank()) +
  theme(axis.ticks = element_line(size = 1.1))


# color collection
my_color_collection <- c(
  "#CBD588", "#5F7FC7", "orange", "#AD6F3B", "#673770", 
  "#D14285", "#652926", "#C84248", "#8569D5", "#5E738F",
  "#D1A33D", "#8A7C64", "#599861","#616163", "#FFCDB2",
  "#6D9F71", "#242F40",
  "#CCA43B", "#F92A82", "#ED7B84", "#7EB77F", 
  "#DEC4A1", "#E5D1D0", '#0E8482', '#C9DAEA', '#337357', 
  '#95C623', '#E55812', '#04471C', '#F2D7EE', '#D3BCC0', 
  '#A5668B', '#69306D', '#0E103D', '#1A535C', '#4ECDC4', 
  '#F7FFF7', '#FF6B6B', '#FFE66D', '#6699CC', '#FFF275', 
  '#FF8C42', '#FF3C38', '#A23E48', '#000000', '#CF5C36', 
  '#EEE5E9', '#7C7C7C', '#EFC88B', '#2E5266', '#6E8898', 
  '#9FB1BC', '#D3D0CB', '#E2C044', '#5BC0EB', '#FDE74C', 
  '#9BC53D', '#E55934', '#FA7921', "#CD9BCD", "#508578", "#DA5724")

# for git push, use this instead of using wflow_git_push()
# git push -u origin master (in the Git app / in the working directory)

```


## 1. Import data table from python code
We are going to use the vcl3 treated standard curve that is fitted with pure nitrate standards
```{r}
# import file
df_p1 <- openxlsx::read.xlsx("data/211128_Griess_plate1.xlsx")
df_p2 <- openxlsx::read.xlsx("data/211128_Griess_plate2.xlsx")
df_p3 <- openxlsx::read.xlsx("data/211128_Griess_plate3.xlsx")
df_p4 <- openxlsx::read.xlsx("data/211128_Griess_plate4.xlsx")
df_p5 <- openxlsx::read.xlsx("data/211128_Griess_plate5.xlsx")
df_p6 <- openxlsx::read.xlsx("data/211128_Griess_plate6.xlsx")
df_p7 <- openxlsx::read.xlsx("data/211128_Griess_plate7.xlsx")
df_p8 <- openxlsx::read.xlsx("data/211128_Griess_plate8.xlsx")
df_p9 <- openxlsx::read.xlsx("data/211128_Griess_plate9.xlsx")
df_p10 <- openxlsx::read.xlsx("data/211128_Griess_plate10.xlsx")
df_p11 <- openxlsx::read.xlsx("data/211128_Griess_plate11.xlsx")

head(df_p1)
colnames(df_p1)
dim(df_p1)

head(df_p2)
colnames(df_p2)
dim(df_p2)

head(df_p3)
colnames(df_p3)
dim(df_p3)

head(df_p4)
colnames(df_p4)
dim(df_p4)

head(df_p5)
colnames(df_p5)
dim(df_p5)

head(df_p6)
colnames(df_p6)
dim(df_p6)

dim(df_p7)
dim(df_p8)
dim(df_p9)
dim(df_p10)
dim(df_p11)

# remove wells that were contaminated during the experiment
# df_p1 %<>% filter(!(Well %in% c("F01","F02","F03","F04","F05","F06","F07","F08","F09","F10","F11","F12"))) # put griess reagents two times (190ul + 190ul)
# df_p2 %<>% filter(!(Well %in% c("A10","A11"))) # filter contamination
# dim(df_p2)
# df_p3 %<>% filter(!(Well %in% c("D05","F05"))) # blanks contaminated with soil
# dim(df_p3)
# df_p4 %<>% filter(!(Well %in% c("D01","F01"))) # blanks contaminated with soil
# dim(df_p4)

# bind two dataframe
df_p <- rbind(df_p1, df_p2, df_p3, df_p4, df_p5, df_p6, df_p7, df_p8, df_p9, df_p10, df_p11)
dim(df_p)

# remove NA
dim(df_p)
df_p <- na.omit(df_p)
dim(df_p)

# multiply dilution factor which is 5/2
df_p %<>% select(-NO2_OD540, -NO2NO3_OD540)
df_p %<>% mutate(NO2_mM = NO2_mM * (5/2), NO2NO3_mM = NO2NO3_mM * (5/2), NO3_mM = NO3_mM * (5/2))

# Get the metadata for time point and left join
Time_table <- openxlsx::read.xlsx("data/211128_time_table.xlsx")
Time_table %<>% select(-Date) 
dim(df_p)
df_p <- df_p %>% left_join(Time_table, by=("Time_point"="Time_point"))
dim(df_p)
colnames(df_p)
# time_point order
df_p$Time_point <-  factor(df_p$Time_point, levels = paste0("T",0:10))

```

## 2. Get average and standard deviation & Moisture correction & Blank correction
```{r}
# plot to see
ggplot(df_p, aes(x=Time_point, y=NO3_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  scale_fill_brewer(palette='Set2') +
  ylab("NO3- (mM) \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  # scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  ggtitle("Without averaging \n") +
  mytheme_2d

# plot to see
ggplot(df_p1, aes(x=Time_point, y=NO3_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  scale_fill_brewer(palette='Set2') +
  ylab("NO3- (mM) \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  # scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  ggtitle("Without averaging \n") +
  mytheme_2d

# plot to see
ggplot(df_p2, aes(x=Time_point, y=NO3_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  scale_fill_brewer(palette='Set2') +
  ylab("NO3- (mM) \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  # scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  ggtitle("Without averaging \n") +
  mytheme_2d

# plot to see
ggplot(df_p3, aes(x=Time_point, y=NO3_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  scale_fill_brewer(palette='Set2') +
  ylab("NO3- (mM) \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  # scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  ggtitle("Without averaging \n") +
  mytheme_2d

# plot to see
ggplot(df_p4, aes(x=Time_point, y=NO3_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  scale_fill_brewer(palette='Set2') +
  ylab("NO3- (mM) \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  # scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  ggtitle("Without averaging \n") +
  mytheme_2d

# plot to see
ggplot(df_p5, aes(x=Time_point, y=NO3_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  scale_fill_brewer(palette='Set2') +
  ylab("NO3- (mM) \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  # scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  ggtitle("Without averaging \n") +
  mytheme_2d

# plot to see
ggplot(df_p6, aes(x=Time_point, y=NO3_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  scale_fill_brewer(palette='Set2') +
  ylab("NO3- (mM) \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  # scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  ggtitle("Without averaging \n") +
  mytheme_2d

# plot to see
ggplot(df_p7, aes(x=Time_point, y=NO3_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  scale_fill_brewer(palette='Set2') +
  ylab("NO3- (mM) \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  # scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  ggtitle("Without averaging \n") +
  mytheme_2d

# plot to see
ggplot(df_p8, aes(x=Time_point, y=NO3_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  scale_fill_brewer(palette='Set2') +
  ylab("NO3- (mM) \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  # scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  ggtitle("Without averaging \n") +
  mytheme_2d

# plot to see
ggplot(df_p9, aes(x=Time_point, y=NO3_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  scale_fill_brewer(palette='Set2') +
  ylab("NO3- (mM) \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  # scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  ggtitle("Without averaging \n") +
  mytheme_2d

# plot to see
ggplot(df_p10, aes(x=Time_point, y=NO3_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  scale_fill_brewer(palette='Set2') +
  ylab("NO3- (mM) \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  # scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  ggtitle("Without averaging \n") +
  mytheme_2d

# plot to see
ggplot(df_p11, aes(x=Time_point, y=NO3_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  scale_fill_brewer(palette='Set2') +
  ylab("NO3- (mM) \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  # scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  ggtitle("Without averaging \n") +
  mytheme_2d

# average technical replicate
colnames(df_p)
dim(df_p)

df_NO2NO3 <- df_p %>% group_by(Sample, Nitrite_input, Nitrate_input, Category, Sample_type, Soil, pH, Time_point, Plate, Time_minutes, Time_hours, Time_days) %>% summarise(Ave_NO2_mM = mean(NO2_mM), Std_NO2_mM = sd(NO2_mM), Ave_NO3_mM = mean(NO3_mM), Std_NO3_mM = sd(NO3_mM)) %>% ungroup()

dim(df_NO2NO3)
dim(df_p)

df_NO2NO3$Sample_type
# Factor in orders
df_NO2NO3$Sample_type <-  factor(df_NO2NO3$Sample_type, levels = c("Soil", "Nitrite_Blank", "Nitrate_Blank"))
df_NO2NO3$Time_point <-  factor(df_NO2NO3$Time_point, levels = paste0("T",0:10))
dim(df_NO2NO3) #294

# Testing negative samples
df_no3_blank <- df_NO2NO3 %>% filter(Sample_type == "Nitrate_Blank")
df_no3_blank # 21

df_no2_blank <- df_NO2NO3 %>% filter(Sample_type == "Nitrite_Blank")
df_no2_blank # 21
# close to zero

# 1. Apply moisture correction factor (correcting for moisture in soil)
soil_spike_ratio = 0.5  # soil weight(0.7g) / spike in volume (1.4ml) 
moisture_percent_1 = 19.9 # MIDWAY-A 
moisture_percent_2 = 53.9 # Washington-A 
moisture_percent_3 = 16.52 # Nichols-A 

mcf_1 = (soil_spike_ratio*(moisture_percent_1/100) + 1)
mcf_1
mcf_2 = (soil_spike_ratio*(moisture_percent_2/100) + 1)
mcf_2
mcf_3 = (soil_spike_ratio*(moisture_percent_3/100) + 1)
mcf_3

# apply moisture factor to each soil
dim(df_NO2NO3)
df_NO2NO3 %>% select(Soil) %>% unique()

df_NO2NO3_mcf_1 <- df_NO2NO3 %>% filter(Soil == "Midway-A_6.89") %>% mutate(Ave_NO3_mM = Ave_NO3_mM * mcf_1, Ave_NO2_mM = Ave_NO2_mM * mcf_1, Std_NO2_mM = Std_NO2_mM * mcf_1, Std_NO3_mM = Std_NO3_mM * mcf_1)
dim(df_NO2NO3_mcf_1) #84
df_NO2NO3_mcf_2 <- df_NO2NO3 %>% filter(Soil == "Washington-A_7.88") %>% mutate(Ave_NO3_mM = Ave_NO3_mM * mcf_2, Ave_NO2_mM = Ave_NO2_mM * mcf_2, Std_NO2_mM = Std_NO2_mM * mcf_2, Std_NO3_mM = Std_NO3_mM * mcf_2)
dim(df_NO2NO3_mcf_2) #84
df_NO2NO3_mcf_3 <- df_NO2NO3 %>% filter(Soil == "Nichols-B_7.29") %>% mutate(Ave_NO3_mM = Ave_NO3_mM * mcf_3, Ave_NO2_mM = Ave_NO2_mM * mcf_3, Std_NO2_mM = Std_NO2_mM * mcf_3, Std_NO3_mM = Std_NO3_mM * mcf_3)
dim(df_NO2NO3_mcf_3) #84

df_NO2NO3_others_mcf <- df_NO2NO3 %>% filter(Sample_type %in% c("Nitrite_Blank", "Nitrate_Blank"))
dim(df_NO2NO3_others_mcf) #42
df_NO2NO3_mcf <- rbind(df_NO2NO3_mcf_1, df_NO2NO3_mcf_2, df_NO2NO3_mcf_3, df_NO2NO3_others_mcf)
dim(df_NO2NO3_mcf) # 294

# plot to see
ggplot(df_NO2NO3_mcf, aes(x=Time_hours, y=Ave_NO3_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  geom_errorbar(aes(ymin=Ave_NO3_mM - Std_NO3_mM, ymax=Ave_NO3_mM + Std_NO3_mM), width=.05)+
  scale_fill_brewer(palette='Set2') +
  ylab("NO3- (mM) \n") +
  xlab("\n Time (hours)") +
  # scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  ggtitle("After averaging with biological replicates \n") +
  mytheme_2d

# 2. Apply blank correction factor (drying effect during incubation)
# Blank reads
df_no3_blank <- df_NO2NO3 %>% filter(Sample_type == "Nitrate_Blank")
df_no3_blank
df_no2_blank <- df_NO2NO3 %>% filter(Sample_type == "Nitrite_Blank")
df_no2_blank

# df_aero_blank$Nitrate_input <- as.numeric(as.character(df_aero_blank$Nitrate_input))
df_no2_blank %<>% mutate(Correction_factor_NO2 = (Nitrite_input / Ave_NO2_mM)) 
df_no3_blank %<>% mutate(Correction_factor_NO3 = (Nitrate_input / Ave_NO3_mM)) 

cf_no2 <- df_no2_blank %>% select(Category, Time_point, Correction_factor_NO2)
cf_no3 <- df_no3_blank %>% select(Category, Time_point, Correction_factor_NO3)

# left join and multiply the correction factor
# left join to samples
df_sample_mcf <- df_NO2NO3_mcf %>% filter(!(Sample_type %in% c("Nitrite_Blank","Nitrate_Blank")))
dim(df_sample_mcf) #252

df_sample_bcf <- df_sample_mcf %>% left_join(cf_no2, by = c("Category"="Category", "Time_point"="Time_point")) %>% left_join(cf_no3, by = c("Category"="Category", "Time_point"="Time_point"))
dim(df_sample_bcf)

df_sample_bcf <- df_sample_bcf %>% mutate(Ave_NO3_mM = Ave_NO3_mM * Correction_factor_NO3, Ave_NO2_mM = Ave_NO2_mM * Correction_factor_NO2, Std_NO2_mM = Std_NO2_mM * Correction_factor_NO2, Std_NO3_mM = Std_NO3_mM * Correction_factor_NO3)
dim(df_sample_bcf)

# merge dataframe with blank just for convenience
df_NO2NO3_blanks_bcf <- df_NO2NO3_mcf %>% filter(Sample_type %in% c("Nitrite_Blank","Nitrate_Blank")) %>% left_join(cf_no2, by = c("Category"="Category", "Time_point"="Time_point")) %>% left_join(cf_no3, by = c("Category"="Category", "Time_point"="Time_point"))
dim(df_NO2NO3_blanks_bcf) #42
dim(df_sample_bcf) # 128 16
df_NO2NO3_bcf <- rbind(df_sample_bcf, df_NO2NO3_blanks_bcf)
dim(df_NO2NO3_bcf) # 150 16

```


## 3. Sanity check: moisture correction & blank correction factor 

Blank correction \
Use the nitrate concentration of the blank and use the ratio. \
For example, multiply to nitrate concentration x (2mM / changed [NO3]) \

```{r}
# without any correction
# nitrate blanks
dim(df_no3_blank)
ggplot(df_no3_blank, aes(x=Time_hours, y=Ave_NO3_mM, color=Category, group=Category)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  geom_errorbar(aes(ymin=Ave_NO3_mM - Std_NO3_mM, ymax=Ave_NO3_mM + Std_NO3_mM), width=.05)+
  # scale_color_brewer(palette='Set2') +
  # scale_color_manual(values = c("deepskyblue4","maroon2"))+
  ylab("Measured NO3- (mM) \n") +
  xlab("\n Time (hr)") +
  scale_y_continuous(breaks = seq(0,6.5,0.5), limits=c(0, 6.5))+
  # scale_x_continuous(breaks = seq(0,2.1,0.25), limits=c(0, 2.1))+
  ggtitle("Nitrate blank \n") +
  mytheme_2d

# nitrite blanks
dim(df_no2_blank)
ggplot(df_no2_blank, aes(x=Time_hours, y=Ave_NO2_mM, color=Category, group=Category)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  geom_errorbar(aes(ymin=Ave_NO2_mM - Std_NO2_mM, ymax=Ave_NO2_mM + Std_NO2_mM), width=.05)+
  # scale_color_brewer(palette='Set2') +
  # scale_color_manual(values = c("deepskyblue4","maroon2"))+
  ylab("Measured NO2- (mM) \n") +
  xlab("\n Time (hr)") +
  scale_y_continuous(breaks = seq(0,6.5,0.5), limits=c(0, 6.5))+
  # scale_x_continuous(breaks = seq(0,2.1,0.25), limits=c(0, 2.1))+
  ggtitle("Nitrite blank \n") +
  mytheme_2d

# without any correction
# all soils
df_soil <- df_NO2NO3 %>% filter(Sample_type == "Soil")
dim(df_soil)
ggplot(df_soil, aes(x=Time_hours, y=Ave_NO3_mM, color=Soil, group=Soil)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  geom_errorbar(aes(ymin=Ave_NO3_mM - Std_NO3_mM, ymax=Ave_NO3_mM + Std_NO3_mM), width=.05)+
  # scale_color_brewer(palette='Set2') +
  # scale_color_manual(values = c("deepskyblue4","maroon2"))+
  ylab("Measured NO3- (mM) \n") +
  xlab("\n Time (hr)") +
  # scale_y_continuous(breaks = seq(0,5.1,1), limits=c(0, 5.1))+
  # scale_x_continuous(breaks = seq(0,5.1,1), limits=c(0, 5.1))+
  ggtitle("(Without any correction) Soil \n") +
  mytheme_2d +
  facet_grid(. ~ Category) +
  theme(strip.background = element_rect(colour="black", fill="white", size=0.1))

# only anaerobic
df_soil_an <- df_soil %>% filter(Category == "Anaerobic")
df_soil_a <- df_soil %>% filter(Category == "Aerobic")
ggplot(df_soil_an, aes(x=Time_hours, y=Ave_NO3_mM, color=Soil, group=Soil)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  geom_errorbar(aes(ymin=Ave_NO3_mM - Std_NO3_mM, ymax=Ave_NO3_mM + Std_NO3_mM), width=.05)+
  # scale_color_brewer(palette='Set2') +
  # scale_color_manual(values = c("deepskyblue4","maroon2"))+
  ylab("Measured NO3- (mM) \n") +
  xlab("\n Time (hr)") +
  # scale_y_continuous(breaks = seq(0,5.1,1), limits=c(0, 5.1))+
  # scale_x_continuous(breaks = seq(0,5.1,1), limits=c(0, 5.1))+
  ggtitle("(Without any correction) Anaerobic \n") +
  mytheme_2d

# only aerobic
ggplot(df_soil_a, aes(x=Time_hours, y=Ave_NO3_mM, color=Soil, group=Soil)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  geom_errorbar(aes(ymin=Ave_NO3_mM - Std_NO3_mM, ymax=Ave_NO3_mM + Std_NO3_mM), width=.05)+
  # scale_color_brewer(palette='Set2') +
  # scale_color_manual(values = c("deepskyblue4","maroon2"))+
  ylab("Measured NO3- (mM) \n") +
  xlab("\n Time (hr)") +
  # scale_y_continuous(breaks = seq(0,5.1,1), limits=c(0, 5.1))+
  # scale_x_continuous(breaks = seq(0,5.1,1), limits=c(0, 5.1))+
  ggtitle("(Without any correction) Aerobic \n") +
  mytheme_2d

# After moisture correction
df_soil_mcf <- df_NO2NO3_mcf %>% filter(Sample_type == "Soil")
dim(df_soil_mcf)
ggplot(df_soil_mcf, aes(x=Time_hours, y=Ave_NO3_mM, color=Soil, group=Soil)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  geom_errorbar(aes(ymin=Ave_NO3_mM - Std_NO3_mM, ymax=Ave_NO3_mM + Std_NO3_mM), width=.05)+
  # scale_color_brewer(palette='Set2') +
  # scale_color_manual(values = c("deepskyblue4","maroon2"))+
  ylab("Measured NO3- (mM) \n") +
  xlab("\n Time (hr)") +
  # scale_y_continuous(breaks = seq(0,5.1,1), limits=c(0, 5.1))+
  # scale_x_continuous(breaks = seq(0,5.1,1), limits=c(0, 5.1))+
  ggtitle("(After moisture correction) Soil \n") +
  mytheme_2d +
  facet_grid(. ~ Category) +
  theme(strip.background = element_rect(colour="black", fill="white", size=0.1))

# only anaerobic
df_soil_an_mcf <- df_soil_mcf %>% filter(Category == "Anaerobic")
df_soil_a_mcf <- df_soil_mcf %>% filter(Category == "Aerobic")
ggplot(df_soil_an_mcf, aes(x=Time_hours, y=Ave_NO3_mM, color=Soil, group=Soil)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  geom_errorbar(aes(ymin=Ave_NO3_mM - Std_NO3_mM, ymax=Ave_NO3_mM + Std_NO3_mM), width=.05)+
  # scale_color_brewer(palette='Set2') +
  # scale_color_manual(values = c("deepskyblue4","maroon2"))+
  ylab("Measured NO3- (mM) \n") +
  xlab("\n Time (hr)") +
  # scale_y_continuous(breaks = seq(0,5.1,1), limits=c(0, 5.1))+
  # scale_x_continuous(breaks = seq(0,5.1,1), limits=c(0, 5.1))+
  ggtitle("(After moisture correction) Anaerobic \n") +
  mytheme_2d

# only aerobic
ggplot(df_soil_a_mcf, aes(x=Time_hours, y=Ave_NO3_mM, color=Soil, group=Soil)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  geom_errorbar(aes(ymin=Ave_NO3_mM - Std_NO3_mM, ymax=Ave_NO3_mM + Std_NO3_mM), width=.05)+
  # scale_color_brewer(palette='Set2') +
  # scale_color_manual(values = c("deepskyblue4","maroon2"))+
  ylab("Measured NO3- (mM) \n") +
  xlab("\n Time (hr)") +
  # scale_y_continuous(breaks = seq(0,5.1,1), limits=c(0, 5.1))+
  # scale_x_continuous(breaks = seq(0,5.1,1), limits=c(0, 5.1))+
  ggtitle("(After moisture correction) Aerobic \n") +
  mytheme_2d

# After blank correction (evaporation) - only slurry
df_soil_bcf <- df_sample_bcf %>% filter(Sample_type == "Soil")
ggplot(df_soil_bcf, aes(x=Time_hours, y=Ave_NO3_mM, color=Soil, group=Soil)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  geom_errorbar(aes(ymin=Ave_NO3_mM - Std_NO3_mM, ymax=Ave_NO3_mM + Std_NO3_mM), width=.05)+
  # scale_color_brewer(palette='Set2') +
  # scale_color_manual(values = c("deepskyblue4","maroon2"))+
  ylab("Measured NO3- (mM) \n") +
  xlab("\n Time (hr)") +
  # scale_y_continuous(breaks = seq(0,5.1,1), limits=c(0, 5.1))+
  # scale_x_continuous(breaks = seq(0,5.1,1), limits=c(0, 5.1))+
  ggtitle("(After moisture + blank correction) Slurry \n") +
  mytheme_2d +
  facet_grid(. ~ Category) +
  theme(strip.background = element_rect(colour="black", fill="white", size=0.1))

# only anaerobic
df_soil_an_bcf <- df_sample_bcf %>% filter(Category == "Anaerobic")
ggplot(df_soil_an_bcf, aes(x=Time_hours, y=Ave_NO3_mM, color=Soil, group=Soil)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  geom_errorbar(aes(ymin=Ave_NO3_mM - Std_NO3_mM, ymax=Ave_NO3_mM + Std_NO3_mM), width=.05)+
  # scale_color_brewer(palette='Set2') +
  # scale_color_manual(values = c("deepskyblue4","maroon2"))+
  ylab("Measured NO3- (mM) \n") +
  xlab("\n Time (hr)") +
  # scale_y_continuous(breaks = seq(0,5.1,1), limits=c(0, 5.1))+
  # scale_x_continuous(breaks = seq(0,5.1,1), limits=c(0, 5.1))+
  ggtitle("(After moisture + blank correction) Anaerobic \n") +
  mytheme_2d +
  facet_grid(. ~ Category) +
  theme(strip.background = element_rect(colour="black", fill="white", size=0.1))



```


## 4. Nitrogen dynamics

```{r}
# pH color
col_pH <- colorRampPalette(c("gold","purple"))

library(colorRamps)
colorRamps::green2red
plot(rep(1,4),col=col_pH(4),pch=19,cex=3)

# 1. Nitrate dynamics - Slurry
df_soil_bcf <- df_sample_bcf %>% filter(Sample_type == "Soil")
df_soil_bcf$pH <- factor(df_soil_bcf$pH)

# plot
df_anaerobic_bcf <- df_soil_bcf %>% filter(Category == "Anaerobic")

ggplot(df_anaerobic_bcf, aes(x=Time_hours, y=Ave_NO3_mM, color=pH, group=pH)) +
  geom_point(size=2.5, shape=16) +
  geom_line(size=1.5)+
  geom_errorbar(aes(ymin=Ave_NO3_mM - Std_NO3_mM, ymax=Ave_NO3_mM + Std_NO3_mM), width=.05)+
  scale_color_manual(values=col_pH(4)) +
  ylab("NO3- (mM) \n") +
  xlab("\n Time (hr)") +
  # scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  ggtitle("Anaerobic condition \n") +
  # label
  # geom_text(aes(label = round(Ave_NO3_mM,3)), size = 3, vjust = -1.5, family="serif", show.legend = FALSE)+
  mytheme_2d +
  facet_grid(. ~ Soil) +
  theme(strip.background = element_rect(colour="black", fill="white", size=0.1))

# plot
df_aerobic_bcf <- df_soil_bcf %>% filter(Category == "Aerobic")

ggplot(df_aerobic_bcf, aes(x=Time_hours, y=Ave_NO3_mM, color=pH, group=pH)) +
  geom_point(size=2.5, shape=16) +
  geom_line(size=1.5)+
  geom_errorbar(aes(ymin=Ave_NO3_mM - Std_NO3_mM, ymax=Ave_NO3_mM + Std_NO3_mM), width=.05)+
  scale_color_manual(values=col_pH(4)) +
  ylab("NO3- (mM) \n") +
  xlab("\n Time (hr)") +
  # scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  ggtitle("Aerobic condition \n") +
  # label
  # geom_text(aes(label = round(Ave_NO3_mM,3)), size = 3, vjust = -1.5, family="serif", show.legend = FALSE)+
  mytheme_2d +
  facet_grid(. ~ Soil) +
  theme(strip.background = element_rect(colour="black", fill="white", size=0.1))


# 2. Nitrite dynamics - Slurry
# plot
df_anaerobic_bcf <- df_soil_bcf %>% filter(Category == "Anaerobic")

ggplot(df_anaerobic_bcf, aes(x=Time_hours, y=Ave_NO2_mM, color=pH, group=pH)) +
  geom_point(size=2.5, shape=16) +
  geom_line(size=1.5)+
  geom_errorbar(aes(ymin=Ave_NO2_mM - Std_NO2_mM, ymax=Ave_NO2_mM + Std_NO2_mM), width=.05)+
  scale_color_manual(values=col_pH(4)) +
  ylab("NO2- (mM) \n") +
  xlab("\n Time (hr)") +
  # scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  ggtitle("Anaerobic condition \n") +
  # label
  # geom_text(aes(label = round(Ave_NO2_mM,3)), size = 3, vjust = -1.5, family="serif", show.legend = FALSE)+
  mytheme_2d +
  facet_grid(. ~ Soil) +
  theme(strip.background = element_rect(colour="black", fill="white", size=0.1))

# plot
df_aerobic_bcf <- df_soil_bcf %>% filter(Category == "Aerobic")

ggplot(df_aerobic_bcf, aes(x=Time_hours, y=Ave_NO2_mM, color=pH, group=pH)) +
  geom_point(size=2.5, shape=16) +
  geom_line(size=1.5)+
  geom_errorbar(aes(ymin=Ave_NO2_mM - Std_NO2_mM, ymax=Ave_NO2_mM + Std_NO2_mM), width=.05)+
  scale_color_manual(values=col_pH(4)) +
  ylab("NO2- (mM) \n") +
  xlab("\n Time (hr)") +
  # scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  ggtitle("Aerobic condition \n") +
  # label
  # geom_text(aes(label = round(Ave_NO2_mM,3)), size = 3, vjust = -1.5, family="serif", show.legend = FALSE)+
  mytheme_2d +
  facet_grid(. ~ Soil) +
  theme(strip.background = element_rect(colour="black", fill="white", size=0.1))




```



