---
title: "211224_TOC_spikein_test"
author: "KiseokUchicago"
date: "2021-12-31"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---



```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=11, fig.height=9,
                      error=TRUE, echo=TRUE, eval=TRUE, warning=FALSE, message=FALSE)
```

## TOC(Total organic carbon) measurements
Researcher: **Kiseok Lee** \
Experiment Date: 12/24/21 | 1/11/22 \
Analysis Date: 12/31/21 | 1/13/22 \
Lab: **Seppe Kuehn**

```{r}
# libraries
library(dplyr)
library(ggplot2)
library(RColorBrewer)
library(vegan)
library(tidyverse)
library(magrittr)
library(readxl)
library(reshape2)
library(gtools)
library(devtools)
library(openxlsx)
library(ape)
library(stringr)
library(tidyr)
library(ggrepel)
library(ggpubr)

## theme for ggplot
mytheme <- theme_bw() + 
  theme(text = element_text(family="serif")) +
  theme(plot.title = element_text(size = 19,hjust = 0.5, family="serif")) + 
  theme(axis.title.x = element_text(size = 17,hjust = 0.5, family="serif")) + 
  theme(axis.title.y = element_text(size = 17,hjust = 0.5, family="serif")) + 
  theme(axis.text.x = element_text(hjust = 0.5, vjust=0.3,size=13, family="serif"))+
  theme(axis.text.y = element_text(size=10, family="serif"))+
  theme(panel.grid.major = element_blank()) +
  theme(panel.grid.minor = element_blank(),panel.background=element_blank(),panel.border=element_blank(),plot.background=element_blank()) +
  theme(axis.ticks = element_line(size = 1.1))

mytheme_2d <- theme_bw() + 
  theme(text = element_text(family="serif")) +
  theme(plot.title = element_text(size = 19,hjust = 0.5, family="serif")) + 
  theme(axis.title.x = element_text(size = 17,hjust = 0.5, family="serif")) + 
  theme(axis.title.y = element_text(size = 17,hjust = 0.5, family="serif")) + 
  theme(axis.text.x = element_text(hjust = 0.5, vjust=0.3,size=13, family="serif"))+
  theme(axis.text.y = element_text(size=13, family="serif"))+
  # theme(panel.grid.major = element_blank()) +
  # theme(panel.grid.minor = element_blank(),panel.background=element_blank(),plot.background=element_blank()) +
  theme(axis.ticks = element_line(size = 1.1))


# color collection
my_color_collection <- c(
  "#CBD588", "#5F7FC7", "orange", "#AD6F3B", "#673770", 
  "#D14285", "#652926", "#C84248", "#8569D5", "#5E738F",
  "#D1A33D", "#8A7C64", "#599861","#616163", "#FFCDB2",
  "#6D9F71", "#242F40",
  "#CCA43B", "#F92A82", "#ED7B84", "#7EB77F", 
  "#DEC4A1", "#E5D1D0", '#0E8482', '#C9DAEA', '#337357', 
  '#95C623', '#E55812', '#04471C', '#F2D7EE', '#D3BCC0', 
  '#A5668B', '#69306D', '#0E103D', '#1A535C', '#4ECDC4', 
  '#F7FFF7', '#FF6B6B', '#FFE66D', '#6699CC', '#FFF275', 
  '#FF8C42', '#FF3C38', '#A23E48', '#000000', '#CF5C36', 
  '#EEE5E9', '#7C7C7C', '#EFC88B', '#2E5266', '#6E8898', 
  '#9FB1BC', '#D3D0CB', '#E2C044', '#5BC0EB', '#FDE74C', 
  '#9BC53D', '#E55934', '#FA7921', "#CD9BCD", "#508578", "#DA5724")

# for git push, use this instead of using wflow_git_push()
# git push -u origin master (in the Git app / in the working directory)

```

## 1. Import data table from python code
```{r}
# import file
# 10ul
df_100ul <- openxlsx::read.xlsx("data/211224_TOC_sample_plate1.xlsx")
df_filt <- openxlsx::read.xlsx("data/220111_TOC_sample_plate1.xlsx")

head(df_100ul)
colnames(df_100ul)
dim(df_100ul)
df_100ul$Method <- "No_filter"

dim(df_filt)
colnames(df_filt)
df_filt %<>% select(-Date)
df_filt$Method <- "Filtered"

# merge
df_toc <- rbind(df_100ul, df_filt)

# remove NA
dim(df_toc)
df_toc <- na.omit(df_toc)
dim(df_toc)

# remove wells H06, H09
# df_p %<>% filter(!(Well %in% c("H06","H09")))
# dim(df_p)

```

## 2. Preprocess data and select datapoints to visualize
```{r}
# 1. multiply dilution factor
df_100ul %<>% mutate(TOC_ppm = TOC_ppm * 5)

# 2. Apply moisture correction factor (correcting for moisture in soil)
soil_spike_ratio = 1  # soil weight(0.2g) / spike in volume (0.2ml) 
moisture_percent_1 = 19.9 # MIDWAY-A 
# moisture_percent_2 = 53.9 # Washington-A 
# moisture_percent_3 = 16.52 # Nichols-A

# Partial extraction moisture correction factor
# mcf_1 = (soil_spike_ratio*(moisture_percent_1/100) + 1)
# mcf_1
# mcf_2 = (soil_spike_ratio*(moisture_percent_2/100) + 1)
# mcf_2
# mcf_3 = (soil_spike_ratio*(moisture_percent_3/100) + 1)
# mcf_3

# Full extraction moisture correction factor
soil_g = 0.2
spike_in_ml = 0.4
KCl_ml  = 0.6
mcf_full_1 = (soil_g*(moisture_percent_1/100) + spike_in_ml + KCl_ml ) / (spike_in_ml + KCl_ml)
mcf_full_1

# apply moisture factor to each soil
df_100ul_mcf <- df_100ul %>% mutate(TOC_ppm = TOC_ppm * mcf_full_1)
# dim(df_NO2NO3_mcf_1) #84
# df_NO2NO3_mcf_2 <- df_NO2NO3 %>% filter(Soil == "Washington-A_7.88") %>% mutate(Ave_NO3_mM = Ave_NO3_mM * mcf_2, Ave_NO2_mM = Ave_NO2_mM * mcf_2, Std_NO2_mM = Std_NO2_mM * mcf_2, Std_NO3_mM = Std_NO3_mM * mcf_2)
# dim(df_NO2NO3_mcf_2) #84
# df_NO2NO3_mcf_3 <- df_NO2NO3 %>% filter(Sample_type %in% c("Slurry","Control")) %>% mutate(Ave_NO3_mM = Ave_NO3_mM * mcf_3, Ave_NO2_mM = Ave_NO2_mM * mcf_3, Std_NO2_mM = Std_NO2_mM * mcf_3, Std_NO3_mM = Std_NO3_mM * mcf_3)

# 3. Calculate soil TOC percent
soil_weight_g = 0.2
spike_in_volume_ml = 0.2
df_100ul_mcf %<>% mutate(TOC_percent = TOC_ppm * 0.001 * (spike_in_volume_ml / soil_weight_g) *100) 
df_percent <- df_100ul_mcf

colnames(df_percent)

# average technical replicate

df_ave <- df_percent %>% group_by(Sample, TOC, Sample_type) %>% summarise(Ave_TOC_percent = mean(TOC_percent), Std_TOC_percent = sd(TOC_percent), Ave_TOC_ppm = mean(TOC_ppm), Std_TOC_ppm = sd(TOC_ppm)) %>% ungroup()

colnames(df_ave)
```

## 3.1. Spike in testing
```{r}
# (1) Sucrose C mg/ml
ggplot(df_ave, aes(x=TOC, y=Ave_TOC_ppm)) +
  geom_point(size=2.5, shape=21, color = "brown") +
  geom_line(size=1, color='brown')+
  geom_errorbar(aes(ymin=Ave_TOC_ppm - Std_TOC_ppm, ymax=Ave_TOC_ppm + Std_TOC_ppm), width=.05)+
  scale_fill_brewer(palette='Set2') +
  ylab("Water Soluble Organic Carbon (ppm, C mg/ml) \n") +
  xlab("\n Sucrose spike in amount (ppm, C mg/ml)") +
  scale_x_continuous(breaks = seq(0,16,1), limits=c(0, 16))+
  #scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  ggtitle("Water soluble carbon of Midway-A soil (No filter method with 100ul supernatant) \n") +
  # label
  geom_text(aes(label = round(Ave_TOC_ppm,3)), size = 3, vjust = -1.5, family="serif", show.legend = FALSE)+
  mytheme_2d

# (2) Percentage
ggplot(df_ave, aes(x=TOC, y=Ave_TOC_percent)) +
  geom_point(size=2.5, shape=21, color = "brown") +
  geom_line(size=1, color='brown')+
  geom_errorbar(aes(ymin=Ave_TOC_percent - Std_TOC_percent, ymax=Ave_TOC_percent + Std_TOC_percent), width=.05)+
  scale_fill_brewer(palette='Set2') +
  ylab("Water Soluble Organic Carbon (% w/w) \n") +
  xlab("\n Sucrose spike in amount (ppm, C mg/ml)") +
  scale_x_continuous(breaks = seq(0,16,1), limits=c(0, 16))+
  #scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  ggtitle("Water soluble carbon of Midway-A soil (No filter method with 100ul supernatant) \n") +
  # label
  geom_text(aes(label = round(Ave_TOC_percent,3)), size = 3, vjust = -1.5, family="serif", show.legend = FALSE)+
  mytheme_2d


```

## 3.2. Extraction efficiency
```{r}
# get extraction ratio
# innate nitrate
add_innate <- df_ave %>% filter(TOC == 0) %>% rename(Innate_TOC_ppm = Ave_TOC_ppm) %>% select(Sample_type, Innate_TOC_ppm)

df_innate <- df_ave %>% filter(TOC != 0) %>% arrange(Sample) %>%
  left_join(add_innate, by=c("Sample_type"="Sample_type")) %>% 
  mutate(Retrieved_TOC_ppm = Ave_TOC_ppm - Innate_TOC_ppm)

# Retrieved ratio of spike ins
df_innate$Ratio_retrieved <- df_innate$Retrieved_TOC_ppm / df_innate$TOC
df_innate$Std_Ratio_retrieved <- df_innate$Std_TOC_ppm / df_innate$TOC 

# df_100$Nitrate_input <- factor(df_100$Nitrate_input)

ggplot(df_innate, aes(x=TOC, y=Ratio_retrieved)) +
  geom_bar(stat="identity",position="dodge", fill="brown")+
  geom_errorbar(aes(ymin=Ratio_retrieved - Std_Ratio_retrieved, ymax=Ratio_retrieved + Std_Ratio_retrieved), width=.05, position = position_dodge(0.8))+
  geom_line(size=0.2, color="brown")+
  scale_fill_brewer(palette='Set2') +
  ylab("Ratio of retrieved total organic carbon (ppm, C mg/ml) \n") +
  xlab("\n Sucrose spike in amount (ppm, C mg/ml)") +
  scale_y_continuous(breaks = seq(0,1.1,0.1), limits=c(0, 1.1))+
  scale_x_continuous(breaks = seq(0,17,1), limits=c(0, 17))+
  ggtitle("Organic carbon spike in extraction ratio (No filter method with 100ul supernatant) \n") +
  geom_text(aes(label = round(Ratio_retrieved,3)), size = 3, vjust = -1.5, family="serif", show.legend = FALSE, position = position_dodge(0.8))+
  mytheme_2d


```

## 3.3. Regression line
```{r}
## fit regression line
colnames(df_percent)
fit.toc <- lm(TOC_ppm ~ TOC, df_percent)

# Plot fitted linear regression line
ggplot(df_percent, aes(x=TOC, y=TOC_ppm)) +
  geom_point(size=2.5, shape=21, color = "brown") +
  # geom_line(size=1)+
  # geom_errorbar(aes(ymin=NO3_mM - sd_NO3_mM, ymax=NO3_mM + sd_NO3_mM), width=.05)+
  # scale_color_brewer(palette='Set2') +
  # scale_color_manual(values = c("maroon2","deepskyblue4"))+
  ylab("Water Soluble Organic Carbon (ppm, C mg/ml) \n") +
  xlab("\n Sucrose spike in amount (ppm, C mg/ml)") +
  scale_x_continuous(breaks = seq(0,16,1), limits=c(0, 16))+
  #scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  # geom_text_repel(aes(label = round(NO3_mM,3)), size = 3,family="serif", show.legend = FALSE)+
  ggtitle("Water soluble carbon of Midway-A soil (No filter method with 100ul supernatant) \n") +
  geom_abline(slope = 1, intercept=0, show.legend = "y=x")+
  # regression line
  geom_abline(slope = coef(fit.toc)[[2]], intercept = coef(fit.toc)[[1]],
              color = "maroon2") +
  # show equation
  # stat_cor(aes(label = paste(..rr.label.., ..p.label.., sep = "~`,`~"))) +
  annotate("text",x=8,y=10, label= paste0("y = ", round(coef(fit.toc)[[1]],3),"+",round(coef(fit.toc)[[2]],3),"x"), color = "maroon2") +
  mytheme_2d


```


## TOC(Total organic carbon) measurements - adding filtered samples
Researcher: **Kiseok Lee** \
Experiment Date: 12/24/21 | 1/11/22 \
Analysis Date: 12/31/21 | 1/13/22 \
Lab: **Seppe Kuehn**

## 2. Preprocess data and select datapoints to visualize
```{r}
# 1. multiply dilution factor
df_toc %<>% mutate(TOC_ppm = TOC_ppm * 5)

# 2. Apply moisture correction factor (correcting for moisture in soil)
soil_spike_ratio = 1  # soil weight(0.2g) / spike in volume (0.2ml) 
moisture_percent_1 = 19.9 # MIDWAY-A 
# moisture_percent_2 = 53.9 # Washington-A 
# moisture_percent_3 = 16.52 # Nichols-A

# Partial extraction moisture correction factor
# mcf_1 = (soil_spike_ratio*(moisture_percent_1/100) + 1)
# mcf_1
# mcf_2 = (soil_spike_ratio*(moisture_percent_2/100) + 1)
# mcf_2
# mcf_3 = (soil_spike_ratio*(moisture_percent_3/100) + 1)
# mcf_3

# Full extraction moisture correction factor
soil_g = 0.2
spike_in_ml = 0.4
KCl_ml  = 0.6
mcf_full_1 = (soil_g*(moisture_percent_1/100) + spike_in_ml + KCl_ml ) / (spike_in_ml + KCl_ml)
mcf_full_1

# apply moisture factor to each soil
df_toc_mcf <- df_toc %>% mutate(TOC_ppm = TOC_ppm * mcf_full_1)
# dim(df_NO2NO3_mcf_1) #84
# df_NO2NO3_mcf_2 <- df_NO2NO3 %>% filter(Soil == "Washington-A_7.88") %>% mutate(Ave_NO3_mM = Ave_NO3_mM * mcf_2, Ave_NO2_mM = Ave_NO2_mM * mcf_2, Std_NO2_mM = Std_NO2_mM * mcf_2, Std_NO3_mM = Std_NO3_mM * mcf_2)
# dim(df_NO2NO3_mcf_2) #84
# df_NO2NO3_mcf_3 <- df_NO2NO3 %>% filter(Sample_type %in% c("Slurry","Control")) %>% mutate(Ave_NO3_mM = Ave_NO3_mM * mcf_3, Ave_NO2_mM = Ave_NO2_mM * mcf_3, Std_NO2_mM = Std_NO2_mM * mcf_3, Std_NO3_mM = Std_NO3_mM * mcf_3)

# 3. Calculate soil TOC percent
soil_weight_g = 0.2
spike_in_volume_ml = 0.2
df_toc_mcf %<>% mutate(TOC_percent = TOC_ppm * 0.001 * (spike_in_volume_ml / soil_weight_g) *100) 
df_percent <- df_toc_mcf

colnames(df_percent)
dim(df_percent)

# average technical replicate

df_ave <- df_percent %>% group_by(Sample, TOC, Sample_type, Method) %>% summarise(Ave_TOC_percent = mean(TOC_percent), Std_TOC_percent = sd(TOC_percent), Ave_TOC_ppm = mean(TOC_ppm), Std_TOC_ppm = sd(TOC_ppm)) %>% ungroup()

colnames(df_ave)
dim(df_ave)
```

## 3.1. Spike in testing
```{r}
# (1) Sucrose C mg/ml
ggplot(df_ave, aes(x=TOC, y=Ave_TOC_ppm, group=Method, color=Method)) +
  geom_point(size=2.5, shape=21) +
  geom_line(size=1)+
  geom_errorbar(aes(ymin=Ave_TOC_ppm - Std_TOC_ppm, ymax=Ave_TOC_ppm + Std_TOC_ppm), width=.05)+
  scale_fill_brewer(palette='Set2') +
  ylab("Water Soluble Organic Carbon (ppm, C mg/ml) \n") +
  xlab("\n Sucrose spike in amount (ppm, C mg/ml)") +
  scale_x_continuous(breaks = seq(0,16,1), limits=c(0, 16))+
  #scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  ggtitle("Water soluble carbon of Midway-A soil (Filtered vs No filter) \n") +
  # label
  geom_text(aes(label = round(Ave_TOC_ppm,3)), size = 3, vjust = -1.5, family="serif", show.legend = FALSE)+
  mytheme_2d

# (2) Percentage
ggplot(df_ave, aes(x=TOC, y=Ave_TOC_percent, group=Method, color=Method)) +
  geom_point(size=2.5, shape=21) +
  geom_line(size=1)+
  geom_errorbar(aes(ymin=Ave_TOC_percent - Std_TOC_percent, ymax=Ave_TOC_percent + Std_TOC_percent), width=.05)+
  scale_fill_brewer(palette='Set2') +
  ylab("Water Soluble Organic Carbon (% w/w) \n") +
  xlab("\n Sucrose spike in amount (ppm, C mg/ml)") +
  scale_x_continuous(breaks = seq(0,16,1), limits=c(0, 16))+
  #scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  ggtitle("Water soluble carbon of Midway-A soil (Filtered vs No filter) \n") +
  # label
  geom_text(aes(label = round(Ave_TOC_percent,3)), size = 3, vjust = -1.5, family="serif", show.legend = FALSE)+
  mytheme_2d


```

## 3.2. Extraction efficiency
```{r}
# get extraction ratio
# innate nitrate
add_innate <- df_ave %>% filter(TOC == 0) %>% rename(Innate_TOC_ppm = Ave_TOC_ppm) %>% select(Method, Innate_TOC_ppm)

df_innate <- df_ave %>% filter(TOC != 0) %>% arrange(Sample) %>%
  left_join(add_innate, by=c("Method"="Method")) %>% 
  mutate(Retrieved_TOC_ppm = Ave_TOC_ppm - Innate_TOC_ppm)

# Retrieved ratio of spike ins
df_innate$Ratio_retrieved <- df_innate$Retrieved_TOC_ppm / df_innate$TOC
df_innate$Std_Ratio_retrieved <- df_innate$Std_TOC_ppm / df_innate$TOC 

# df_100$Nitrate_input <- factor(df_100$Nitrate_input)
df_innate$Method <- factor(df_innate$Method)

ggplot(df_innate, aes(x=TOC, y=Ratio_retrieved, fill=Method, group=Method)) +
  geom_bar(stat="identity",position="dodge")+
  geom_errorbar(aes(ymin=Ratio_retrieved - Std_Ratio_retrieved, ymax=Ratio_retrieved + Std_Ratio_retrieved), width=.05, position = position_dodge(0.8))+
  geom_line(size=0.2, aes(color=Method))+
  scale_fill_brewer(palette='Set2') +
  scale_color_brewer(palette='Set2') +
  ylab("Ratio of retrieved total organic carbon (ppm, C mg/ml) \n") +
  xlab("\n Sucrose spike in amount (ppm, C mg/ml)") +
  # scale_y_continuous(breaks = seq(0,1.1,0.1), limits=c(0, 1.1))+
  scale_x_continuous(breaks = seq(0,17,1), limits=c(0, 17))+
  ggtitle("Organic carbon spike in extraction ratio (Filtered vs No filter) \n") +
  geom_text(aes(label = round(Ratio_retrieved,3)), size = 3, vjust = -1.5, family="serif", show.legend = FALSE, position = position_dodge(0.8))+
  mytheme_2d


```

## 3.3. Regression line
```{r}
## fit regression line
# we need to subtract the innate TOC before we do a regression right? yes
df_innate_all <- df_percent %>% filter(TOC != 0) %>% arrange(Sample) %>%
  left_join(add_innate, by=c("Method"="Method")) %>% 
  mutate(Retrieved_TOC_ppm = TOC_ppm - Innate_TOC_ppm)

df_nf <- df_innate_all %>% filter(Method == "No_filter")
df_f <- df_innate_all %>% filter(Method == "Filtered")

fit.toc_nf <- lm(Retrieved_TOC_ppm ~ TOC, df_nf)
fit.toc_f <- lm(Retrieved_TOC_ppm ~ TOC, df_f)

# (1) No filter method: Plot fitted linear regression line
ggplot(df_nf, aes(x=TOC, y=Retrieved_TOC_ppm)) +
  geom_point(size=2.5, shape=21, color = "brown") +
  # geom_line(size=1)+
  # geom_errorbar(aes(ymin=NO3_mM - sd_NO3_mM, ymax=NO3_mM + sd_NO3_mM), width=.05)+
  # scale_color_brewer(palette='Set2') +
  # scale_color_manual(values = c("maroon2","deepskyblue4"))+
  ylab("Water Soluble Organic Carbon (ppm, C mg/ml) \n") +
  xlab("\n Sucrose spike in amount (ppm, C mg/ml)") +
  scale_x_continuous(breaks = seq(0,16,1), limits=c(0, 16))+
  #scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  # geom_text_repel(aes(label = round(NO3_mM,3)), size = 3,family="serif", show.legend = FALSE)+
  ggtitle("(Subtracted innate carbon) Water soluble carbon of Midway-A soil (No filter) \n") +
  geom_abline(slope = 1, intercept=0, show.legend = "y=x")+
  # regression line
  geom_abline(slope = coef(fit.toc_nf)[[2]], intercept = coef(fit.toc_nf)[[1]],
              color = "maroon2") +
  # show equation
  # stat_cor(aes(label = paste(..rr.label.., ..p.label.., sep = "~`,`~"))) +
  annotate("text",x=8,y=10, label= paste0("y = ", round(coef(fit.toc_nf)[[1]],3),"+",round(coef(fit.toc_nf)[[2]],3),"x"), color = "maroon2") +
  mytheme_2d


# (2) Filter method: Plot fitted linear regression line
ggplot(df_f, aes(x=TOC, y=Retrieved_TOC_ppm)) +
  geom_point(size=2.5, shape=21, color = "brown") +
  # geom_line(size=1)+
  # geom_errorbar(aes(ymin=NO3_mM - sd_NO3_mM, ymax=NO3_mM + sd_NO3_mM), width=.05)+
  # scale_color_brewer(palette='Set2') +
  # scale_color_manual(values = c("maroon2","deepskyblue4"))+
  ylab("Water Soluble Organic Carbon (ppm, C mg/ml) \n") +
  xlab("\n Sucrose spike in amount (ppm, C mg/ml)") +
  scale_x_continuous(breaks = seq(0,16,1), limits=c(0, 16))+
  #scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  # geom_text_repel(aes(label = round(NO3_mM,3)), size = 3,family="serif", show.legend = FALSE)+
  ggtitle("(Subtracted innate carbon) Water soluble carbon of Midway-A soil (Filtered) \n") +
  geom_abline(slope = 1, intercept=0, show.legend = "y=x")+
  # regression line
  geom_abline(slope = coef(fit.toc_f)[[2]], intercept = coef(fit.toc_f)[[1]],
              color = "maroon2") +
  # show equation
  # stat_cor(aes(label = paste(..rr.label.., ..p.label.., sep = "~`,`~"))) +
  annotate("text",x=8,y=10, label= paste0("y = ", round(coef(fit.toc_f)[[1]],3),"+",round(coef(fit.toc_f)[[2]],3),"x"), color = "maroon2") +
  mytheme_2d




```
