---
title: "220103_Griess_pH_perturbation"
author: "KiseokUchicago"
date: "2022-01-04"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---


```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=11, fig.height=9,
                      error=TRUE, echo=TRUE, eval=TRUE, warning=FALSE, message=FALSE)
```

## Time series analysis - pH perturbation experiment  (Griess assay)
Researcher: **Kiseok Lee** \
Experiment Date: 12/29/21 - 1/3/22 (3 days) \
Analysis Date: 1/4/21
Lab: **Seppe Kuehn**

```{r}
# libraries
library(dplyr)
library(ggplot2)
library(RColorBrewer)
library(vegan)
library(tidyverse)
library(magrittr)
library(readxl)
library(reshape2)
library(gtools)
library(devtools)
library(openxlsx)
library(ape)
library(stringr)
library(tidyr)
library(ggrepel)
library(ggpubr)

## theme for ggplot
mytheme <- theme_bw() + 
  theme(text = element_text(family="serif")) +
  theme(plot.title = element_text(size = 19,hjust = 0.5, family="serif")) + 
  theme(axis.title.x = element_text(size = 17,hjust = 0.5, family="serif")) + 
  theme(axis.title.y = element_text(size = 17,hjust = 0.5, family="serif")) + 
  theme(axis.text.x = element_text(hjust = 0.5, vjust=0.3,size=13, family="serif"))+
  theme(axis.text.y = element_text(size=10, family="serif"))+
  theme(panel.grid.major = element_blank()) +
  theme(panel.grid.minor = element_blank(),panel.background=element_blank(),panel.border=element_blank(),plot.background=element_blank()) +
  theme(axis.ticks = element_line(size = 1.1))

mytheme_2d <- theme_bw() + 
  theme(text = element_text(family="serif")) +
  theme(plot.title = element_text(size = 19,hjust = 0.5, family="serif")) + 
  theme(axis.title.x = element_text(size = 17,hjust = 0.5, family="serif")) + 
  theme(axis.title.y = element_text(size = 17,hjust = 0.5, family="serif")) + 
  theme(axis.text.x = element_text(hjust = 0.5, vjust=0.3,size=13, family="serif"))+
  theme(axis.text.y = element_text(size=13, family="serif"))+
  # theme(panel.grid.major = element_blank()) +
  # theme(panel.grid.minor = element_blank(),panel.background=element_blank(),plot.background=element_blank()) +
  theme(axis.ticks = element_line(size = 1.1))


# color collection
my_color_collection <- c(
  "#CBD588", "#5F7FC7", "orange", "#AD6F3B", "#673770", 
  "#D14285", "#652926", "#C84248", "#8569D5", "#5E738F",
  "#D1A33D", "#8A7C64", "#599861","#616163", "#FFCDB2",
  "#6D9F71", "#242F40",
  "#CCA43B", "#F92A82", "#ED7B84", "#7EB77F", 
  "#DEC4A1", "#E5D1D0", '#0E8482', '#C9DAEA', '#337357', 
  '#95C623', '#E55812', '#04471C', '#F2D7EE', '#D3BCC0', 
  '#A5668B', '#69306D', '#0E103D', '#1A535C', '#4ECDC4', 
  '#F7FFF7', '#FF6B6B', '#FFE66D', '#6699CC', '#FFF275', 
  '#FF8C42', '#FF3C38', '#A23E48', '#000000', '#CF5C36', 
  '#EEE5E9', '#7C7C7C', '#EFC88B', '#2E5266', '#6E8898', 
  '#9FB1BC', '#D3D0CB', '#E2C044', '#5BC0EB', '#FDE74C', 
  '#9BC53D', '#E55934', '#FA7921', "#CD9BCD", "#508578", "#DA5724")

# for git push, use this instead of using wflow_git_push()
# git push -u origin master (in the Git app / in the working directory)

```


## 1. Import data table from python code
We are going to use the vcl3 treated standard curve that is fitted with pure nitrate standards
```{r}
# import file
df_T0 <- openxlsx::read.xlsx("data/220103_Griess_T0.xlsx")
df_T1 <- openxlsx::read.xlsx("data/220103_Griess_T1.xlsx")
df_T2 <- openxlsx::read.xlsx("data/220103_Griess_T2.xlsx")
df_T3 <- openxlsx::read.xlsx("data/220103_Griess_T3.xlsx")
df_T4 <- openxlsx::read.xlsx("data/220103_Griess_T4.xlsx")
df_T5 <- openxlsx::read.xlsx("data/220103_Griess_T5.xlsx")
df_T6 <- openxlsx::read.xlsx("data/220103_Griess_T6.xlsx")
df_T7 <- openxlsx::read.xlsx("data/220103_Griess_T7.xlsx")
df_T8 <- openxlsx::read.xlsx("data/220103_Griess_T8.xlsx")
df_T9 <- openxlsx::read.xlsx("data/220103_Griess_T9.xlsx")
# df_T10 <- openxlsx::read.xlsx("data/220103_Griess_T10.xlsx") # is still in freezer (2M KCl treated & spin down)
df_T11 <- openxlsx::read.xlsx("data/220103_Griess_T11.xlsx")
df_T12 <- openxlsx::read.xlsx("data/220103_Griess_T12.xlsx")

head(df_T0)
colnames(df_T0)
dim(df_T0)

head(df_T1)
colnames(df_T1)
dim(df_T1)

head(df_T2)
colnames(df_T2)
dim(df_T2)

head(df_T3)
colnames(df_T3)
dim(df_T3)

head(df_T4)
colnames(df_T4)
dim(df_T4)

head(df_T5)
colnames(df_T5)
dim(df_T5)

dim(df_T6)
dim(df_T7)
dim(df_T8)
dim(df_T9)
dim(df_T10)
dim(df_T11)
dim(df_T12)

# X1 to Well
# df_T0 %<>% rename(Well = X1)
# df_T2 %<>% rename(Well = X1)
# df_T3 %<>% rename(Well = X1)
# df_T4 %<>% rename(Well = X1)
# df_T5 %<>% rename(Well = X1)
# df_T6 %<>% rename(Well = X1)
# df_T7 %<>% rename(Well = X1)
# df_T8 %<>% rename(Well = X1)
# df_T9 %<>% rename(Well = X1)
# df_T10 %<>% rename(Well = X1)
# df_T11 %<>% rename(Well = X1)

# remove wells that were contaminated during the experiment
df_T1 %<>% filter(!(Well %in% c("B03","A05","A12","B12"))) # filter burst issue
df_T6 %<>% filter(!(Well %in% c("A11"))) # filter burst issue
df_T8 %<>% filter(!(Well %in% c("A07", "A08", "E08"))) # filter burst issue
df_T11 %<>% filter(!(Well %in% c("A01"))) # filter burst issue  # G11 was removed because of abnormal value compared to other 2 replicates
# dim(df_T4)

# bind two dataframe
df_T <- rbind(df_T0, df_T1, df_T2, df_T3, df_T4, df_T5, df_T6, df_T7, df_T8, df_T9, df_T11, df_T12)
dim(df_T)

# remove NA
dim(df_T)
df_T <- na.omit(df_T)
dim(df_T)

# multiply dilution factor which is 5/2
df_T %<>% select(-NO2_OD540, -NO2NO3_OD540)
df_T %<>% mutate(NO2_mM = NO2_mM * (5/2), NO2NO3_mM = NO2NO3_mM * (5/2), NO3_mM = NO3_mM * (5/2))

# Get the metadata for time point and left join
Time_table <- openxlsx::read.xlsx("data/220103_time_table.xlsx")
# Time_table_BN <- openxlsx::read.xlsx("data/220103_time_table_BN.xlsx")
# Time_table <- rbind(Time_table_AU, Time_table_BN)

Time_table %<>% select(-Date) 
dim(df_T)
df_T <- df_T %>% left_join(Time_table, by=("Time_point"="Time_point"))
dim(df_T)
colnames(df_T)
# time_point order
# df_T$Time_point <-  factor(df_T$Time_point, levels = paste0("T",0:10))

```

## 2. Get average and standard deviation & Moisture correction & Blank correction
```{r}
# plot to see
ggplot(df_T, aes(x=Time_point, y=NO3_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  scale_fill_brewer(palette='Set2') +
  ylab("NO3- (mM) \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  # scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  ggtitle("Without averaging \n") +
  mytheme_2d

# plot to see
ggplot(df_T0, aes(x=Time_point, y=NO3_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  scale_fill_brewer(palette='Set2') +
  ylab("NO3- (mM) \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  # scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  ggtitle("Without averaging \n") +
  mytheme_2d

# plot to see
ggplot(df_T1, aes(x=Time_point, y=NO3_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  scale_fill_brewer(palette='Set2') +
  ylab("NO3- (mM) \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  # scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  ggtitle("Without averaging \n") +
  mytheme_2d

# plot to see
ggplot(df_T2, aes(x=Time_point, y=NO3_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  scale_fill_brewer(palette='Set2') +
  ylab("NO3- (mM) \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  # scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  ggtitle("Without averaging \n") +
  mytheme_2d

# plot to see
ggplot(df_T3, aes(x=Time_point, y=NO3_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  scale_fill_brewer(palette='Set2') +
  ylab("NO3- (mM) \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  # scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  ggtitle("Without averaging \n") +
  mytheme_2d

# plot to see
ggplot(df_T4, aes(x=Time_point, y=NO3_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  scale_fill_brewer(palette='Set2') +
  ylab("NO3- (mM) \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  # scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  ggtitle("Without averaging \n") +
  mytheme_2d

# plot to see
ggplot(df_T5, aes(x=Time_point, y=NO3_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  scale_fill_brewer(palette='Set2') +
  ylab("NO3- (mM) \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  # scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  ggtitle("Without averaging \n") +
  mytheme_2d

# plot to see
ggplot(df_T6, aes(x=Time_point, y=NO3_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  scale_fill_brewer(palette='Set2') +
  ylab("NO3- (mM) \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  # scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  ggtitle("Without averaging \n") +
  mytheme_2d

# plot to see
ggplot(df_T7, aes(x=Time_point, y=NO3_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  scale_fill_brewer(palette='Set2') +
  ylab("NO3- (mM) \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  # scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  ggtitle("Without averaging \n") +
  mytheme_2d

# plot to see
ggplot(df_T8, aes(x=Time_point, y=NO3_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  scale_fill_brewer(palette='Set2') +
  ylab("NO3- (mM) \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  # scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  ggtitle("Without averaging \n") +
  mytheme_2d

# plot to see
ggplot(df_T9, aes(x=Time_point, y=NO3_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  scale_fill_brewer(palette='Set2') +
  ylab("NO3- (mM) \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  # scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  ggtitle("Without averaging \n") +
  mytheme_2d

# plot to see
ggplot(df_T10, aes(x=Time_point, y=NO3_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  scale_fill_brewer(palette='Set2') +
  ylab("NO3- (mM) \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  # scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  ggtitle("Without averaging \n") +
  mytheme_2d

# plot to see
ggplot(df_T11, aes(x=Time_point, y=NO3_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  scale_fill_brewer(palette='Set2') +
  ylab("NO3- (mM) \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  # scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  ggtitle("Without averaging \n") +
  mytheme_2d

# plot to see
ggplot(df_T12, aes(x=Time_point, y=NO3_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  scale_fill_brewer(palette='Set2') +
  ylab("NO3- (mM) \n") +
  xlab("\n Nitrate_spike_in (mM)") +
  # scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  ggtitle("Without averaging \n") +
  mytheme_2d


# average technical replicate
colnames(df_T)
dim(df_T)

df_NO2NO3 <- df_T %>% group_by(Nitrite_input, Nitrate_input, Soil, Titration_type, Concentration_M, Added_ul, Sample_type, Time_point, Time_minutes, Time_hours, Time_days) %>% summarise(Ave_NO2_mM = mean(NO2_mM), Std_NO2_mM = sd(NO2_mM), Ave_NO3_mM = mean(NO3_mM), Std_NO3_mM = sd(NO3_mM)) %>% ungroup()

dim(df_NO2NO3)
dim(df_T)

df_NO2NO3$Sample_type
# Factor in orders
df_NO2NO3$Sample_type <-  factor(df_NO2NO3$Sample_type, levels = c("Slurry", "Sucrose_Blank", "Nitrite_Blank", "Nitrate_Blank"))
# df_NO2NO3$Time_point <-  factor(df_NO2NO3$Time_point, levels = c(paste0("AU",0:11),paste0("BN",0:9)))
# Change name
df_NO2NO3$Soil <- str_replace(df_NO2NO3$Soil,"NicholsC","NicholsC_pH7")
df_NO2NO3$Soil <- str_replace(df_NO2NO3$Soil,"Allandale","Allandale_pH4")
df_NO2NO3$Soil <-  factor(df_NO2NO3$Soil, levels = c("NicholsC_pH7", "Allandale_pH4"))
# Remove sucrose blank
df_NO2NO3 %<>% filter(!(Sample_type == "Sucrose_Blank")) 
dim(df_NO2NO3) #360

# Testing negative samples
df_no3_blank <- df_NO2NO3 %>% filter(Sample_type == "Nitrate_Blank")
df_no3_blank # 24

df_no2_blank <- df_NO2NO3 %>% filter(Sample_type == "Nitrite_Blank")
df_no2_blank # 24
# close to zero

# 1. Apply moisture correction factor (correcting for moisture in soil)
soil_spike_ratio = 0.5  # soil weight(0.85g) / spike in volume (1.7ml) 
moisture_percent_1 = 19 # NicholsC
moisture_percent_2 = 33.2 # Allandale
# moisture_percent_3 = 16.52 # Nichols-A

mcf_1 = (soil_spike_ratio*(moisture_percent_1/100) + 1)
mcf_1
mcf_2 = (soil_spike_ratio*(moisture_percent_2/100) + 1)
mcf_2
# mcf_3 = (soil_spike_ratio*(moisture_percent_3/100) + 1)
# mcf_3

# apply moisture factor to each soil
dim(df_NO2NO3)
df_NO2NO3 %>% select(Soil) %>% unique()

df_NO2NO3_mcf_1 <- df_NO2NO3 %>% filter(Soil == "NicholsC_pH7", Sample_type == "Slurry") %>% mutate(Ave_NO3_mM = Ave_NO3_mM * mcf_1, Ave_NO2_mM = Ave_NO2_mM * mcf_1, Std_NO2_mM = Std_NO2_mM * mcf_1, Std_NO3_mM = Std_NO3_mM * mcf_1)
dim(df_NO2NO3_mcf_1) #156
df_NO2NO3_mcf_2 <- df_NO2NO3 %>% filter(Soil == "Allandale_pH4", Sample_type == "Slurry") %>% mutate(Ave_NO3_mM = Ave_NO3_mM * mcf_2, Ave_NO2_mM = Ave_NO2_mM * mcf_2, Std_NO2_mM = Std_NO2_mM * mcf_2, Std_NO3_mM = Std_NO3_mM * mcf_2)
dim(df_NO2NO3_mcf_2) #156
# df_NO2NO3_mcf_3 <- df_NO2NO3 %>% filter(Sample_type %in% c("Slurry","Control")) %>% mutate(Ave_NO3_mM = Ave_NO3_mM * mcf_3, Ave_NO2_mM = Ave_NO2_mM * mcf_3, Std_NO2_mM = Std_NO2_mM * mcf_3, Std_NO3_mM = Std_NO3_mM * mcf_3)
# dim(df_NO2NO3_mcf_3) #130 15

df_NO2NO3_others_mcf <- df_NO2NO3 %>% filter(Sample_type %in% c("Nitrite_Blank", "Nitrate_Blank"))
dim(df_NO2NO3_others_mcf) #72
df_NO2NO3_mcf <- rbind(df_NO2NO3_mcf_1, df_NO2NO3_mcf_2, df_NO2NO3_others_mcf)
dim(df_NO2NO3_mcf) # 360

# plot to see
ggplot(df_NO2NO3_mcf, aes(x=Time_hours, y=Ave_NO3_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  geom_errorbar(aes(ymin=Ave_NO3_mM - Std_NO3_mM, ymax=Ave_NO3_mM + Std_NO3_mM), width=.05)+
  scale_fill_brewer(palette='Set2') +
  ylab("NO3- (mM) \n") +
  xlab("\n Time (hours)") +
  # scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  ggtitle("After averaging with biological replicates \n") +
  mytheme_2d

# 2. Apply blank correction factor (drying effect during incubation)
# Blank reads
df_no3_blank <- df_NO2NO3 %>% filter(Sample_type == "Nitrate_Blank")
df_no3_blank
df_no2_blank <- df_NO2NO3 %>% filter(Sample_type == "Nitrite_Blank")
df_no2_blank

# df_aero_blank$Nitrate_input <- as.numeric(as.character(df_aero_blank$Nitrate_input))
df_no2_blank %<>% mutate(Correction_factor_NO2 = (Nitrite_input / Ave_NO2_mM)) 
df_no3_blank %<>% mutate(Correction_factor_NO3 = (Nitrate_input / Ave_NO3_mM)) 

cf_no2 <- df_no2_blank %>% select(Soil, Time_point, Correction_factor_NO2)
cf_no3 <- df_no3_blank %>% select(Soil, Time_point, Correction_factor_NO3)

# left join and multiply the correction factor
# left join to samples
df_sample_mcf <- df_NO2NO3_mcf %>% filter(!(Sample_type %in% c("Nitrite_Blank","Nitrate_Blank")))
dim(df_sample_mcf) #312
df_sample_mcf$Sample_type %>% unique()

df_sample_bcf <- df_sample_mcf %>% left_join(cf_no2, by = c("Soil"="Soil", "Time_point"="Time_point")) %>% left_join(cf_no3, by = c("Soil"="Soil", "Time_point"="Time_point"))
dim(df_sample_bcf)

df_sample_bcf <- df_sample_bcf %>% mutate(Ave_NO3_mM = Ave_NO3_mM * Correction_factor_NO3, Ave_NO2_mM = Ave_NO2_mM * Correction_factor_NO2, Std_NO2_mM = Std_NO2_mM * Correction_factor_NO2, Std_NO3_mM = Std_NO3_mM * Correction_factor_NO3)
dim(df_sample_bcf) #312

# merge dataframe with blank just for convenience
df_NO2NO3_blanks_bcf <- df_NO2NO3_mcf %>% filter(Sample_type %in% c("Nitrite_Blank","Nitrate_Blank")) %>% left_join(cf_no2, by = c("Soil"="Soil", "Time_point"="Time_point")) %>% left_join(cf_no3, by = c("Soil"="Soil", "Time_point"="Time_point"))
dim(df_NO2NO3_blanks_bcf) #48
dim(df_sample_bcf) # 312
df_NO2NO3_bcf <- rbind(df_sample_bcf, df_NO2NO3_blanks_bcf)
dim(df_NO2NO3_bcf) # 360

```


## 3. Sanity check: moisture correction & blank correction factor 

Blank correction \
Use the nitrate concentration of the blank and use the ratio. \
For example, multiply to nitrate concentration x (2mM / changed [NO3]) \

```{r}
# without any correction
# nitrate blanks
dim(df_no3_blank)
ggplot(df_no3_blank, aes(x=Time_hours, y=Ave_NO3_mM, color=Soil, group=Soil)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  geom_errorbar(aes(ymin=Ave_NO3_mM - Std_NO3_mM, ymax=Ave_NO3_mM + Std_NO3_mM), width=.05)+
  # scale_color_brewer(palette='Set2') +
  # scale_color_manual(values = c("deepskyblue4","maroon2"))+
  ylab("Measured NO3- (mM) \n") +
  xlab("\n Time (hr)") +
  scale_y_continuous(breaks = seq(0,2.5,0.5), limits=c(0, 2.5))+
  # scale_x_continuous(breaks = seq(0,2.1,0.25), limits=c(0, 2.1))+
  ggtitle("Nitrate blank \n") +
  mytheme_2d

# nitrite blanks
dim(df_no2_blank)
ggplot(df_no2_blank, aes(x=Time_hours, y=Ave_NO2_mM, color=Soil, group=Soil)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  geom_errorbar(aes(ymin=Ave_NO2_mM - Std_NO2_mM, ymax=Ave_NO2_mM + Std_NO2_mM), width=.05)+
  # scale_color_brewer(palette='Set2') +
  # scale_color_manual(values = c("deepskyblue4","maroon2"))+
  ylab("Measured NO2- (mM) \n") +
  xlab("\n Time (hr)") +
  scale_y_continuous(breaks = seq(0,2.5,0.5), limits=c(0, 2.5))+
  # scale_x_continuous(breaks = seq(0,2.1,0.25), limits=c(0, 2.1))+
  ggtitle("Nitrite blank \n") +
  mytheme_2d

# without any correction
ggplot(df_NO2NO3, aes(x=Time_hours, y=Ave_NO3_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  geom_errorbar(aes(ymin=Ave_NO3_mM - Std_NO3_mM, ymax=Ave_NO3_mM + Std_NO3_mM), width=.05)+
  # scale_color_brewer(palette='Set2') +
  # scale_color_manual(values = c("deepskyblue4","maroon2"))+
  ylab("Measured NO3- (mM) \n") +
  xlab("\n Time (hr)") +
  # scale_y_continuous(breaks = seq(0,5.1,1), limits=c(0, 5.1))+
  # scale_x_continuous(breaks = seq(0,5.1,1), limits=c(0, 5.1))+
  ggtitle("(Without any correction) All samples \n") +
  mytheme_2d +
  facet_grid(. ~ Soil) +
  theme(strip.background = element_rect(colour="black", fill="white", size=0.1))


### What are those points with very high std?
colnames(df_NO2NO3)
df_NO2NO3 %>% arrange(desc(Std_NO3_mM)) %>% select(Soil, Titration_type, Concentration_M, Sample_type, Time_point, Std_NO3_mM) 
## based on this I corrected the wrongly removed E02 -< removed E01 (filter burst). Eliminated point P11 G11.

# After moisture correction
ggplot(df_NO2NO3_mcf, aes(x=Time_hours, y=Ave_NO3_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  geom_errorbar(aes(ymin=Ave_NO3_mM - Std_NO3_mM, ymax=Ave_NO3_mM + Std_NO3_mM), width=.05)+
  # scale_color_brewer(palette='Set2') +
  # scale_color_manual(values = c("deepskyblue4","maroon2"))+
  ylab("Measured NO3- (mM) \n") +
  xlab("\n Time (hr)") +
  # scale_y_continuous(breaks = seq(0,5.1,1), limits=c(0, 5.1))+
  # scale_x_continuous(breaks = seq(0,5.1,1), limits=c(0, 5.1))+
  ggtitle("(After moisture correction) All samples \n") +
  mytheme_2d +
  facet_grid(. ~ Soil) +
  theme(strip.background = element_rect(colour="black", fill="white", size=0.1))

# After blank correction (evaporation) 
ggplot(df_NO2NO3_bcf, aes(x=Time_hours, y=Ave_NO3_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  geom_errorbar(aes(ymin=Ave_NO3_mM - Std_NO3_mM, ymax=Ave_NO3_mM + Std_NO3_mM), width=.05)+
  # scale_color_brewer(palette='Set2') +
  # scale_color_manual(values = c("deepskyblue4","maroon2"))+
  ylab("Measured NO3- (mM) \n") +
  xlab("\n Time (hr)") +
  # scale_y_continuous(breaks = seq(0,5.1,1), limits=c(0, 5.1))+
  # scale_x_continuous(breaks = seq(0,5.1,1), limits=c(0, 5.1))+
  ggtitle("(After moisture + blank correction) All samples \n") +
  mytheme_2d +
  facet_grid(. ~ Soil) +
  theme(strip.background = element_rect(colour="black", fill="white", size=0.1))


```


## 4. Nitrogen dynamics

## 4.1. pH perturbation experiment.
- Is there a difference in pH perturbation levels?
```{r}
# pH color
col_pH <- colorRampPalette(c("gold","purple"))

library(colorRamps)
colorRamps::green2red
plot(rep(1,13),col=col_pH(13),pch=19,cex=3)
grad_pH <- scale_colour_gradientn(colours = col_pH(100))

# Confer this page (https://stackoverflow.com/questions/21537782/how-to-set-fixed-continuous-colour-values-in-ggplot2)
# myPalette <- colorRampPalette(rev(brewer.pal(11, "Spectral")))
# sc <- scale_colour_gradientn(colours = myPalette(100), limits=c(1, 8))


# first HCl, NaOH mM calculation
df_NO2NO3_bcf
# mols and molarity unit conversion
fun_df_convert <- function(df_pH_p1){
  df_pH_p1$Added_ul <- ifelse(df_pH_p1$Titration_type == "NaOH",-1*df_pH_p1$Added_ul, df_pH_p1$Added_ul)
  df_pH_p1 %<>% mutate(H_mol = Concentration_M * Added_ul * 10^(-6))
  df_pH_p1 %<>% mutate(H_Molarity = H_mol / (300 * 10^(-6)))
  df_pH_p1 %<>% mutate(H_mM = H_Molarity * 1000)
  return(df_pH_p1)
}

# test
df_pH <- df_NO2NO3_bcf %>% filter(Titration_type %in% c("NaOH","HCl"))
dim(df_pH)
Added_Volume <- 1.7 # ml
moisture_percent_1 = 19 # NicholsC
moisture_percent_2 = 33.2 # Allandale
df_pH$Added_ul <- ifelse(df_pH$Titration_type == "NaOH", -1*df_pH$Added_ul, df_pH$Added_ul) # HCl is +, NaOH is -
df_pH %<>% mutate(H_mol = Concentration_M * Added_ul * 10^(-6)) # Calculate H mol 
df_pH$Volume <- ifelse(df_pH$Soil == "NicholsC_pH7", Added_Volume*(1+ moisture_percent_1/100), 0) # Calc total volume
df_pH$Volume <- ifelse(df_pH$Soil == "Allandale_pH4", Added_Volume*(1+ moisture_percent_2/100), df_pH$Volume) # Calc total volume
# df_pH$Volume %>% unique()
df_pH %<>% mutate(H_Molarity = H_mol / (Volume * 10^(-3)))
df_pH %<>% mutate(H_mM = H_Molarity * 1000)
# openxlsx::write.xlsx(df_pH, "df_pH.xlsx")

# how many levels of H_mM?
pH_pert <- df_pH %>% select(H_mM) %>% unique() %>% arrange()
df_pH %>% filter(Soil == "NicholsC_pH7")%>% select(H_mM) %>% unique() %>% arrange()
df_pH %>% filter(Soil == "Allandale_pH4")%>% select(H_mM) %>% unique() %>% arrange()

# 1. pH perturbation
# plot Nitrate
dim(df_pH)

ggplot(df_pH, aes(x=Time_hours, y=Ave_NO3_mM, color=H_mM, group=H_mM)) +
  geom_point(size=2.5, shape=16) +
  geom_line(size=1.2)+
  geom_errorbar(aes(ymin=Ave_NO3_mM - Std_NO3_mM, ymax=Ave_NO3_mM + Std_NO3_mM), width=.05)+
  scale_colour_gradientn(colours = col_pH(100)) +
  # scale_color_manual(values=grad_pH) +
  ylab("NO3- (mM) \n") +
  xlab("\n Time (hr)") +
  # scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  ggtitle("pH perturbation \n") +
  # label
  # geom_text(aes(label = round(Ave_NO3_mM,3)), size = 3, vjust = -1.5, family="serif", show.legend = FALSE)+
  mytheme_2d +
  facet_grid(. ~ Soil) +
  theme(strip.background = element_rect(colour="black", fill="white", size=0.1))

# plot it separately: NicholsC
df_nic <- df_pH %>% filter(Soil == "NicholsC_pH7")
ggplot(df_nic, aes(x=Time_hours, y=Ave_NO3_mM, color=H_mM, group=H_mM)) +
  geom_point(size=2.5, shape=16) +
  geom_line(size=1.2)+
  geom_errorbar(aes(ymin=Ave_NO3_mM - Std_NO3_mM, ymax=Ave_NO3_mM + Std_NO3_mM), width=.05)+
  scale_colour_gradientn(colours = col_pH(100)) +
  # scale_color_manual(values=grad_pH) +
  ylab("NO3- (mM) \n") +
  xlab("\n Time (hr)") +
  # scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  ggtitle("pH perturbation (NicholsC: pH 6.98) \n") +
  # label
  # geom_text(aes(label = round(Ave_NO3_mM,3)), size = 3, vjust = -1.5, family="serif", show.legend = FALSE)+
  mytheme_2d +
  # facet_grid(. ~ Soil) +
  theme(strip.background = element_rect(colour="black", fill="white", size=0.1))

# plot it separately: Allandale
df_al <- df_pH %>% filter(Soil == "Allandale_pH4")
ggplot(df_al, aes(x=Time_hours, y=Ave_NO3_mM, color=H_mM, group=H_mM)) +
  geom_point(size=2.5, shape=16) +
  geom_line(size=1.2)+
  geom_errorbar(aes(ymin=Ave_NO3_mM - Std_NO3_mM, ymax=Ave_NO3_mM + Std_NO3_mM), width=.05)+
  scale_colour_gradientn(colours = col_pH(100)) +
  # scale_color_manual(values=grad_pH) +
  ylab("NO3- (mM) \n") +
  xlab("\n Time (hr)") +
  # scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  ggtitle("pH perturbation (Allandale: pH 4) \n") +
  # label
  # geom_text(aes(label = round(Ave_NO3_mM,3)), size = 3, vjust = -1.5, family="serif", show.legend = FALSE)+
  mytheme_2d +
  # facet_grid(. ~ Soil) +
  theme(strip.background = element_rect(colour="black", fill="white", size=0.1))


# plot Nitrite
ggplot(df_pH, aes(x=Time_hours, y=Ave_NO2_mM, color=H_mM, group=H_mM)) +
  geom_point(size=2.5, shape=16) +
  geom_line(size=1.5)+
  geom_errorbar(aes(ymin=Ave_NO2_mM - Std_NO2_mM, ymax=Ave_NO2_mM + Std_NO2_mM), width=.05)+
  scale_colour_gradientn(colours = col_pH(100)) +
  # scale_color_manual(values=col_pH(4)) +
  ylab("NO2- (mM) \n") +
  xlab("\n Time (hr)") +
  # scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  ggtitle("pH perturbation \n") +
  # label
  # geom_text(aes(label = round(Ave_NO2_mM,3)), size = 3, vjust = -1.5, family="serif", show.legend = FALSE)+
  mytheme_2d +
  facet_grid(. ~ Soil) +
  theme(strip.background = element_rect(colour="black", fill="white", size=0.1))

# plot separately: NicholsC
df_nic <- df_pH %>% filter(Soil == "NicholsC_pH7")
ggplot(df_nic, aes(x=Time_hours, y=Ave_NO2_mM, color=H_mM, group=H_mM)) +
  geom_point(size=2.5, shape=16) +
  geom_line(size=1.2)+
  geom_errorbar(aes(ymin=Ave_NO2_mM - Std_NO2_mM, ymax=Ave_NO2_mM + Std_NO2_mM), width=.05)+
  scale_colour_gradientn(colours = col_pH(100)) +
  # scale_color_manual(values=grad_pH) +
  ylab("NO2- (mM) \n") +
  xlab("\n Time (hr)") +
  # scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  ggtitle("pH perturbation (NicholsC: pH 6.98) \n") +
  # label
  # geom_text(aes(label = round(Ave_NO3_mM,3)), size = 3, vjust = -1.5, family="serif", show.legend = FALSE)+
  mytheme_2d +
  # facet_grid(. ~ Soil) +
  theme(strip.background = element_rect(colour="black", fill="white", size=0.1))

# plot it separately: Allandale
df_al <- df_pH %>% filter(Soil == "Allandale_pH4")
ggplot(df_al, aes(x=Time_hours, y=Ave_NO2_mM, color=H_mM, group=H_mM)) +
  geom_point(size=2.5, shape=16) +
  geom_line(size=1.2)+
  geom_errorbar(aes(ymin=Ave_NO2_mM - Std_NO2_mM, ymax=Ave_NO2_mM + Std_NO2_mM), width=.05)+
  scale_colour_gradientn(colours = col_pH(100)) +
  # scale_color_manual(values=grad_pH) +
  ylab("NO2- (mM) \n") +
  xlab("\n Time (hr)") +
  # scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  ggtitle("pH perturbation (Allandale: pH 4) \n") +
  # label
  # geom_text(aes(label = round(Ave_NO3_mM,3)), size = 3, vjust = -1.5, family="serif", show.legend = FALSE)+
  mytheme_2d +
  # facet_grid(. ~ Soil) +
  theme(strip.background = element_rect(colour="black", fill="white", size=0.1))



```

