---
title: "220128_Ammonia_pH_perturbation2"
author: "KiseokUchicago"
date: "2022-01-31"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---


```{r global_options, include=FALSE}
library(knitr)
knitr::opts_chunk$set(fig.width=11, fig.height=9,
                      error=TRUE, echo=TRUE, eval=TRUE, warning=FALSE, message=FALSE,
                      tidy.opts=list(width.cutoff=40),tidy=TRUE)
```

## Time series analysis - pH perturbation experiment-2 (Ammonia assay - Salicylate-Hypochloride assay)
Researcher: **Kiseok Lee** \
Experiment Date: 1/21/22 - 1/25/22 (5 days) \
Analysis Date: 1/31/21
Lab: **Seppe Kuehn**

```{r}
# libraries
library(dplyr)
library(ggplot2)
library(RColorBrewer)
library(vegan)
library(tidyverse)
library(magrittr)
library(readxl)
library(reshape2)
library(gtools)
library(devtools)
library(openxlsx)
library(ape)
library(stringr)
library(tidyr)
library(ggrepel)
library(ggpubr)

## theme for ggplot
mytheme <- theme_bw() + 
  theme(text = element_text(family="serif")) +
  theme(plot.title = element_text(size = 19,hjust = 0.5, family="serif")) + 
  theme(axis.title.x = element_text(size = 17,hjust = 0.5, family="serif")) + 
  theme(axis.title.y = element_text(size = 17,hjust = 0.5, family="serif")) + 
  theme(axis.text.x = element_text(hjust = 0.5, vjust=0.3,size=13, family="serif"))+
  theme(axis.text.y = element_text(size=10, family="serif"))+
  theme(panel.grid.major = element_blank()) +
  theme(panel.grid.minor = element_blank(),panel.background=element_blank(),panel.border=element_blank(),plot.background=element_blank()) +
  theme(axis.ticks = element_line(size = 1.1))

mytheme_2d <- theme_bw() + 
  theme(text = element_text(family="serif")) +
  theme(plot.title = element_text(size = 19,hjust = 0.5, family="serif")) + 
  theme(axis.title.x = element_text(size = 17,hjust = 0.5, family="serif")) + 
  theme(axis.title.y = element_text(size = 17,hjust = 0.5, family="serif")) + 
  theme(axis.text.x = element_text(hjust = 0.5, vjust=0.3,size=13, family="serif"))+
  theme(axis.text.y = element_text(size=13, family="serif"))+
  # theme(panel.grid.major = element_blank()) +
  # theme(panel.grid.minor = element_blank(),panel.background=element_blank(),plot.background=element_blank()) +
  theme(axis.ticks = element_line(size = 1.1))


# color collection
my_color_collection <- c(
  "#CBD588", "#5F7FC7", "orange", "#AD6F3B", "#673770", 
  "#D14285", "#652926", "#C84248", "#8569D5", "#5E738F",
  "#D1A33D", "#8A7C64", "#599861","#616163", "#FFCDB2",
  "#6D9F71", "#242F40",
  "#CCA43B", "#F92A82", "#ED7B84", "#7EB77F", 
  "#DEC4A1", "#E5D1D0", '#0E8482', '#C9DAEA', '#337357', 
  '#95C623', '#E55812', '#04471C', '#F2D7EE', '#D3BCC0', 
  '#A5668B', '#69306D', '#0E103D', '#1A535C', '#4ECDC4', 
  '#F7FFF7', '#FF6B6B', '#FFE66D', '#6699CC', '#FFF275', 
  '#FF8C42', '#FF3C38', '#A23E48', '#000000', '#CF5C36', 
  '#EEE5E9', '#7C7C7C', '#EFC88B', '#2E5266', '#6E8898', 
  '#9FB1BC', '#D3D0CB', '#E2C044', '#5BC0EB', '#FDE74C', 
  '#9BC53D', '#E55934', '#FA7921', "#CD9BCD", "#508578", "#DA5724")

# for git push, use this instead of using wflow_git_push()
# git push -u origin master (in the Git app / in the working directory)

# for making pdf file
library(rmarkdown)
# render("analysis/~~.Rmd", "pdf_document")
```


## 1. Import data table from python code
We are going to use the vcl3 treated standard curve that is fitted with pure Ammonia standards
```{r}
# import file
df_plate1 <- openxlsx::read.xlsx("data/220128_Ammonia_sample_plate1.xlsx")
df_plate2 <- openxlsx::read.xlsx("data/220128_Ammonia_sample_plate2.xlsx")
df_plate3 <- openxlsx::read.xlsx("data/220128_Ammonia_sample_plate3.xlsx")
df_plate4 <- openxlsx::read.xlsx("data/220128_Ammonia_sample_plate4.xlsx")
df_plate5 <- openxlsx::read.xlsx("data/220128_Ammonia_sample_plate5.xlsx")
df_plate6 <- openxlsx::read.xlsx("data/220128_Ammonia_sample_plate6.xlsx")

head(df_plate1)
colnames(df_plate1)
dim(df_plate1)

head(df_plate2)
colnames(df_plate2)
dim(df_plate2)

head(df_plate3)
colnames(df_plate3)
dim(df_plate3)

head(df_plate4)
colnames(df_plate4)
dim(df_plate4)

head(df_plate5)
colnames(df_plate5)
dim(df_plate5)

head(df_plate6)
colnames(df_plate6)
dim(df_plate6)

# X1 to Well
# df_p0 %<>% rename(Well = X1)
# df_p2 %<>% rename(Well = X1)
# df_p3 %<>% rename(Well = X1)
# df_p4 %<>% rename(Well = X1)
# df_p5 %<>% rename(Well = X1)
# df_p6 %<>% rename(Well = X1)
# df_p7 %<>% rename(Well = X1)
# df_p8 %<>% rename(Well = X1)
# df_p9 %<>% rename(Well = X1)
# df_p10 %<>% rename(Well = X1)
# df_p11 %<>% rename(Well = X1)

# remove wells that were contaminated during the experiment
# df_p1 %<>% filter(!(Well %in% c("B03","A05","A12","B12"))) # filter burst issue
# df_p6 %<>% filter(!(Well %in% c("A11"))) # filter burst issue
# df_p8 %<>% filter(!(Well %in% c("A07", "A08", "E08"))) # filter burst issue
# df_p11 %<>% filter(!(Well %in% c("A01"))) # filter burst issue  # G11 was removed because of abnormal value compared to other 2 replicates
# dim(df_p4)

# bind two dataframe
df_a <- rbind(df_plate1, df_plate2, df_plate3, df_plate4, df_plate5, df_plate6)
colnames(df_a)

# remove NA
dim(df_a)
rowSums(is.na(df_a)) > 0
df_a[rowSums(is.na(df_a)) > 0,]
df_a <- na.omit(df_a) # what is being omitted?
dim(df_a) # 532 -> 531

# multiply dilution factor which is 5/2
df_a %<>% mutate(Ammonia_ppm = Ammonia_ppm * (5/2))
head(df_a)

# extraction correction factor (only about 80% extraction)
df_a %<>% mutate(Ammonia_ppm = Ammonia_ppm * (5/4))

# converting to mM
df_a %<>% mutate(NH4_M = Ammonia_ppm / (14.0067*1000))   # Nitrogen molecular weight 
df_a %<>% mutate(NH4_mM = NH4_M * 1000)   # Nitrogen molecular weight 

colnames(df_a)

# get out the T0_deep
df_T0_deep <- df_a %>% filter(Time_point == "T0_deep")
df_a %<>% filter(!(Time_point == "T0_deep")) 
dim(df_a) # 531 -> 527

# Get the metadata for time point and left join
Time_table <- openxlsx::read.xlsx("data/220128_time_table.xlsx")
# Time_table_BN <- openxlsx::read.xlsx("data/220111_time_table_BN.xlsx")
# Time_table <- rbind(Time_table_AU, Time_table_BN)

Time_table %<>% select(-Date) 
dim(df_a)
df_a <- df_a %>% left_join(Time_table, by=("Time_point"="Time_point"))
dim(df_a)
colnames(df_a)
# time_point order
df_a$Time_point <-  factor(df_a$Time_point, levels = paste0("T",0:10))

```

## 2. Get average and standard deviation & Moisture correction & Blank correction
```{r}
# plot to see
ggplot(df_a, aes(x=Time_point, y=NH4_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  scale_fill_brewer(palette='Set2') +
  ylab("NH4+ (mM) \n") +
  xlab("\n Time point") +
  # scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  ggtitle("Without averaging \n") +
  mytheme_2d

# Setting H_mM column
# df_soil <- df_a %>% filter(Titration_type %in% c("NaOH","HCl"))

Added_Volume <- 1.7 # ml
Soil_mg <- 0.85
moisture_percent_1 = 23.6 # LaBaghWoods1
Added_Volume + Soil_mg*(moisture_percent_1/100)
# moisture_percent_2 = 33.2 # Allandale
df_a$Added_ul <- ifelse(df_a$Titration_type == "NaOH", -1*df_a$Added_ul, df_a$Added_ul) # HCl is +, NaOH is -
df_a %<>% mutate(H_mol = Concentration_M * Added_ul * 10^(-6)) # Calculate H mol 
df_a$Volume <- ifelse(df_a$Soil == "LaBaghWoods_pH6.66", Added_Volume + Soil_mg*(moisture_percent_1/100), 0) # Calc total volume
# df_a$Volume <- ifelse(df_a$Soil == "Allandale_pH4", Added_Volume + Soil_mg*(moisture_percent_2/100), df_a$Volume) # Calc total volume
# df_a$Volume %>% unique()
df_a %<>% mutate(H_Molarity = H_mol / (Volume * 10^(-3)))
df_a %<>% mutate(H_mM = H_Molarity * 1000)
# openxlsx::write.xlsx(df_a, "df_a.xlsx")

# how many levels of H_mM?
df_a %>% filter(Soil == "LaBaghWoods_pH6.66")%>% select(H_mM) %>% unique() %>% arrange(H_mM)
# df_a %>% filter(Soil == "Allandale_pH4")%>% select(H_mM) %>% unique() %>% arrange()
colnames(df_a)

## Moisture correction
dim(df_a)

# Testing negative samples
df_no3_blank <- df_a %>% filter(Sample_type == "Blank_Nitrate")  # Use Blank_Nitrate instead in the future
df_no3_blank # 33

df_no2_blank <- df_a %>% filter(Sample_type == "Blank_Nitrite")
df_no2_blank # 33
# close to zero

# 1. Apply moisture correction factor (correcting for moisture in soil)
soil_spike_ratio = 0.5 # soil weight(0.85g) / spike in volume (1.7ml) 
moisture_percent_1 = 23.6 # LaBaghWoods1

mcf_1 = (soil_spike_ratio*(moisture_percent_1/100) + 1)
mcf_1

# apply moisture factor to each soil
dim(df_a)
df_a %>% select(Soil) %>% unique()

# this is a special case with no replicates
df_a_mcf_1 <- df_a %>% filter(Titration_type %in% c("NaOH","HCl")) %>% mutate(Ammonia_ppm = Ammonia_ppm * mcf_1, NH4_M = NH4_M * mcf_1, NH4_mM = NH4_mM * mcf_1)
dim(df_a_mcf_1) #462 18

df_a_others_mcf <- df_a %>% filter(Sample_type %in% c("Blank_Nitrite", "Blank_Nitrate")) # Use Blank_Nitrate instead in the future
dim(df_a_others_mcf) #65
df_a_mcf <- rbind(df_a_mcf_1, df_a_others_mcf)
dim(df_a_mcf) # 527
colnames(df_a_mcf)

# plot to see
ggplot(df_a_mcf, aes(x=Time_hours, y=NH4_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  # geom_errorbar(aes(ymin=NO3_mM - Std_NO3_mM, ymax=NO3_mM + Std_NO3_mM), width=.05)+
  scale_fill_brewer(palette='Set2') +
  ylab("NO3- (mM) \n") +
  xlab("\n Time (hours)") +
  # scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  ggtitle("No averaging with biological replicates \n") +
  mytheme_2d

# 2. Apply blank correction factor (drying effect during incubation)
# Blank reads
# Get this from nitrate, nitrite reads
df_no2_blank <- df_p %>% filter(Sample_type == "Blank_Nitrite")
df_no2_blank

# df_aero_blank$Nitrate_input <- as.numeric(as.character(df_aero_blank$Nitrate_input))
df_no2_blank %<>% mutate(Correction_factor_NO2 = (Nitrite_input / NO2_mM)) 

# average the blanks by time point
cf_no2 <- df_no2_blank %>% select(Soil, Time_point, Correction_factor_NO2) %>% group_by(Soil, Time_point) %>% summarize(Correction_factor_NO2 = mean(Correction_factor_NO2)) %>% ungroup()

# left join and multiply the correction factor
# left join to samples
df_sample_mcf <- df_a_mcf %>% filter(!(Sample_type %in% c("Blank_Nitrite","Blank_Nitrate")))
dim(df_sample_mcf) #462
df_sample_mcf$Sample_type %>% unique()

df_sample_bcf <- df_sample_mcf %>% left_join(cf_no2, by = c("Soil"="Soil", "Time_point"="Time_point"))
dim(df_sample_bcf)

df_sample_bcf <- df_sample_bcf %>% mutate(Ammonia_ppm = Ammonia_ppm * Correction_factor_NO2, NH4_M = NH4_M * Correction_factor_NO2, NH4_mM = NH4_mM * Correction_factor_NO2)
dim(df_sample_bcf) #462 22

# merge dataframe with blank just for convenience
df_a_blanks_bcf <- df_a_mcf %>% filter(Sample_type %in% c("Blank_Nitrite","Blank_Nitrate")) %>% left_join(cf_no2, by = c("Soil"="Soil", "Time_point"="Time_point"))
dim(df_a_blanks_bcf) #66 22
dim(df_sample_bcf) # 462
df_a_bcf <- rbind(df_sample_bcf, df_a_blanks_bcf)
dim(df_a_bcf) # 528 22

```


## 3. Sanity check: moisture correction & blank correction factor 

Blank correction \
Use the Ammonia concentration of the blank and use the ratio. \
For example, multiply to Ammonia concentration x (2mM / changed [NO3]) \

```{r}
# without any correction
ggplot(df_a, aes(x=Time_hours, y=NH4_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  # geom_errorbar(aes(ymin=NH4_mM - Std_NH4_mM, ymax=NH4_mM + Std_NH4_mM), width=.05)+
  # scale_color_brewer(palette='Set2') +
  # scale_color_manual(values = c("deepskyblue4","maroon2"))+
  ylab("Measured NH4+ (mM) \n") +
  xlab("\n Time (hr)") +
  # scale_y_continuous(breaks = seq(0,5.1,1), limits=c(0, 5.1))+
  # scale_x_continuous(breaks = seq(0,5.1,1), limits=c(0, 5.1))+
  ggtitle("(Before moisture correction) All samples \n") +
  mytheme_2d +
  facet_grid(. ~ Soil) +
  theme(strip.background = element_rect(colour="black", fill="white", size=0.1))

# After moisture correction
ggplot(df_a_mcf, aes(x=Time_hours, y=NH4_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  # geom_errorbar(aes(ymin=NH4_mM - Std_NH4_mM, ymax=NH4_mM + Std_NH4_mM), width=.05)+
  # scale_color_brewer(palette='Set2') +
  # scale_color_manual(values = c("deepskyblue4","maroon2"))+
  ylab("Measured NH4+ (mM) \n") +
  xlab("\n Time (hr)") +
  # scale_y_continuous(breaks = seq(0,5.1,1), limits=c(0, 5.1))+
  # scale_x_continuous(breaks = seq(0,5.1,1), limits=c(0, 5.1))+
  ggtitle("(After moisture correction) All samples \n") +
  mytheme_2d +
  facet_grid(. ~ Soil) +
  theme(strip.background = element_rect(colour="black", fill="white", size=0.1))

# After blank correction (evaporation) 
ggplot(df_a_bcf, aes(x=Time_hours, y=NH4_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  # geom_errorbar(aes(ymin=NH4_mM - Std_NH4_mM, ymax=NH4_mM + Std_NH4_mM), width=.05)+
  # scale_color_brewer(palette='Set2') +
  # scale_color_manual(values = c("deepskyblue4","maroon2"))+
  ylab("Measured NH4+ (mM) \n") +
  xlab("\n Time (hr)") +
  # scale_y_continuous(breaks = seq(0,5.1,1), limits=c(0, 5.1))+
  # scale_x_continuous(breaks = seq(0,5.1,1), limits=c(0, 5.1))+
  ggtitle("(After moisture + blank correction) All samples \n") +
  mytheme_2d +
  facet_grid(. ~ Soil) +
  theme(strip.background = element_rect(colour="black", fill="white", size=0.1))


```


## 4. Nitrogen dynamics

## 4.1. pH perturbation experiment.
- Is there a difference in pH perturbation levels?
```{r}
# pH color
col_pH <- colorRampPalette(c("gold","purple"))

library(colorRamps)
colorRamps::green2red
plot(rep(1,13),col=col_pH(13),pch=19,cex=3)
grad_pH <- scale_colour_gradientn(colours = col_pH(100))

# Confer this page (https://stackoverflow.com/questions/21537782/how-to-set-fixed-continuous-colour-values-in-ggplot2)
# myPalette <- colorRampPalette(rev(brewer.pal(11, "Spectral")))
# sc <- scale_colour_gradientn(colours = myPalette(100), limits=c(1, 8))

# 1. pH perturbation
# plot Ammonia
df_a_pH <- df_a_bcf %>% filter(Titration_type %in% c("NaOH","HCl"))

dim(df_a_pH)

ggplot(df_a_pH, aes(x=Time_hours, y=NH4_mM, color=H_mM, group=H_mM)) +
  geom_point(size=2.5, shape=16) +
  geom_line(size=1.2)+
  # geom_errorbar(aes(ymin=NH4_mM - Std_NH4_mM, ymax=NH4_mM + Std_NH4_mM), width=.05)+
  scale_colour_gradientn(colours = col_pH(100)) +
  # scale_color_manual(values=grad_pH) +
  ylab("NH4+ (mM) \n") +
  xlab("\n Time (hr)") +
  # scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  ggtitle("pH perturbation \n") +
  # label
  # geom_text(aes(label = round(NH4_mM,3)), size = 3, vjust = -1.5, family="serif", show.legend = FALSE)+
  mytheme_2d +
  facet_grid(. ~ Soil) +
  theme(strip.background = element_rect(colour="black", fill="white", size=0.1))

```


