---
title: "220414_Ammonium_compare_with_Brookside"
author: "KiseokUchicago"
date: "2022-04-16"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---


```{r global_options, include=FALSE}
library(knitr)
knitr::opts_chunk$set(fig.width=11, fig.height=9,
                      error=TRUE, echo=TRUE, eval=TRUE, warning=FALSE, message=FALSE,
                      tidy.opts=list(width.cutoff=40),tidy=TRUE)
```

## 220414 Ammonium compare with Brookside one more time
Researcher: **Kiseok Lee** \
Experiment Date: 4/14/22 \
Analysis Date: 4/16/22
Lab: **Seppe Kuehn**

```{r, include=FALSE}
# libraries
library(dplyr)
library(ggplot2)
library(RColorBrewer)
library(vegan)
library(tidyverse)
library(magrittr)
library(readxl)
library(reshape2)
library(gtools)
library(devtools)
library(openxlsx)
library(ape)
library(stringr)
library(tidyr)
library(ggrepel)
library(ggpubr)

## theme for ggplot
mytheme <- theme_bw() + 
  theme(text = element_text(family="serif")) +
  theme(plot.title = element_text(size = 19,hjust = 0.5, family="serif")) + 
  theme(axis.title.x = element_text(size = 17,hjust = 0.5, family="serif")) + 
  theme(axis.title.y = element_text(size = 17,hjust = 0.5, family="serif")) + 
  theme(axis.text.x = element_text(hjust = 0.5, vjust=0.3,size=13, family="serif"))+
  theme(axis.text.y = element_text(size=10, family="serif"))+
  theme(panel.grid.major = element_blank()) +
  theme(panel.grid.minor = element_blank(),panel.background=element_blank(),panel.border=element_blank(),plot.background=element_blank()) +
  theme(axis.ticks = element_line(size = 1.1))

mytheme_2d <- theme_bw() + 
  theme(text = element_text(family="serif")) +
  theme(plot.title = element_text(size = 19,hjust = 0.5, family="serif")) + 
  theme(axis.title.x = element_text(size = 17,hjust = 0.5, family="serif")) + 
  theme(axis.title.y = element_text(size = 17,hjust = 0.5, family="serif")) + 
  theme(axis.text.x = element_text(hjust = 0.5, vjust=0.3,size=13, family="serif"))+
  theme(axis.text.y = element_text(size=13, family="serif"))+
  theme(axis.ticks = element_line(size = 1.1))
  # theme(panel.grid.major = element_blank()) +
  # theme(panel.grid.minor = element_blank(),panel.background=element_blank(),plot.background=element_blank()) +
  


# color collection
my_color_collection <- c(
  "#CBD588", "#5F7FC7", "orange", "#AD6F3B", "#673770", 
  "#D14285", "#652926", "#C84248", "#8569D5", "#5E738F",
  "#D1A33D", "#8A7C64", "#599861","#616163", "#FFCDB2",
  "#6D9F71", "#242F40",
  "#CCA43B", "#F92A82", "#ED7B84", "#7EB77F", 
  "#DEC4A1", "#E5D1D0", '#0E8482', '#C9DAEA', '#337357', 
  '#95C623', '#E55812', '#04471C', '#F2D7EE', '#D3BCC0', 
  '#A5668B', '#69306D', '#0E103D', '#1A535C', '#4ECDC4', 
  '#F7FFF7', '#FF6B6B', '#FFE66D', '#6699CC', '#FFF275', 
  '#FF8C42', '#FF3C38', '#A23E48', '#000000', '#CF5C36', 
  '#EEE5E9', '#7C7C7C', '#EFC88B', '#2E5266', '#6E8898', 
  '#9FB1BC', '#D3D0CB', '#E2C044', '#5BC0EB', '#FDE74C', 
  '#9BC53D', '#E55934', '#FA7921', "#CD9BCD", "#508578", "#DA5724")

# for git push, use this instead of using wflow_git_push()
# git push -u origin master (in the Git app / in the working directory)

# for making pdf file
library(rmarkdown)
# render("analysis/~~.Rmd", "pdf_document")
```

## 1. (220414) Compare with Brookside
The standards are not great, but let's try to use this to see if the results are close enough. \\
The only conversion I need to do is the 10x dilution when I was sending the samples to Brookside. Therefore, for the new ammonium assays, just multiply by 0.1 to directly compare to Brookside's results.

```{r}
df_brook <- read.xlsx("data/SPNa_86437_021122_edit2.xlsx")
head(df_brook)
# don't use My_measurement_mM, this is the ammonium assay I've done with the 60ul sampling.

df_220414 <- read.xlsx("data/220414_Ammonia_sample_plate0.xlsx")

colnames(df_brook)
colnames(df_220414)
df_220414

# let's compare the ppm
df_220414$Sample

df_brook$Sample

# merge dataframe

df_ave_220414 <- df_220414 %>% group_by(Sample) %>% summarize(`NH4-N_ppm_mine` = mean(Ammonia_ppm)*0.1)

df_merged <- df_brook %>% filter(Sample_type == "Slurry") %>%  select(Sample, `NH4-N_ppm`) %>% left_join(df_ave_220414, by=c("Sample"="Sample"))

## Comparing with my measurments
df_melt <- df_merged 
df_melt %<>% select(Sample, `NH4-N_ppm`, `NH4-N_ppm_mine`) %>% melt()
df_melt$Measurement <- ifelse(df_melt$variable == "NH4-N_ppm", "Brookside", "Mine") 

df_melt$Sample <- factor(df_melt$Sample, levels = c("Am-25ppm","Am-1","Am-2","Am-3","HCl-9","HCl-10","HCl-11",
                                                      "HCl0-1","HCl0-2","HCl0-3", "NN-1", "NN-2", "NN-3", "NaOH-9","NaOH-10","NaOH-11"))

ggplot(df_melt, aes(x=Sample, y=value, fill= Measurement)) +
  geom_bar(stat="identity",position="dodge")+
  # geom_errorbar(aes(ymin=Ratio_retrieved - Std_Ratio_retrieved, ymax=Ratio_retrieved + Std_Ratio_retrieved), width=.05, position = position_dodge(0.8))+
  # geom_line(size=0.2)+
  scale_fill_brewer(palette='Set1') +
  ylab("NH4+ (ppm) \n") +
  xlab("\n Sample ") +
  # scale_y_continuous(breaks = seq(0,1.5,0.1), limits=c(0, 1.5))+
  # scale_x_continuous(breaks = seq(0,17,1), limits=c(0, 17))+
  ggtitle("NH4 measurement comparison (220414 Assay of stored frozen sample) \n") +
  geom_text(aes(label = round(value,3)), size = 3, vjust = -1.5, family="serif", show.legend = FALSE, position = position_dodge(0.8))+
  mytheme_2d 




```




