---
title: "220428_Ammonia_211128_aerobic_vs_anaerobic"
author: "KiseokUchicago"
date: "2022-04-30"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---


```{r global_options, include=FALSE}
library(knitr)
knitr::opts_chunk$set(fig.width=11, fig.height=9,
                      error=TRUE, echo=TRUE, eval=TRUE, warning=FALSE, message=FALSE,
                      tidy.opts=list(width.cutoff=40),tidy=TRUE)
```

## 220428 Aerobic incubation and ammonium accumulation (Ammonia assay - Salicylate-Hypochloride assay)
Researcher: **Kiseok Lee** \
Experiment Date: 211128 experiment comparing aerobic vs anaerobic \
Analysis Date: 4/30/21
Lab: **Seppe Kuehn**

```{r}
# libraries
library(dplyr)
library(ggplot2)
library(RColorBrewer)
library(vegan)
library(tidyverse)
library(magrittr)
library(readxl)
library(reshape2)
library(gtools)
library(devtools)
library(openxlsx)
library(ape)
library(stringr)
library(tidyr)
library(ggrepel)
library(ggpubr)

## theme for ggplot
mytheme <- theme_bw() + 
  theme(text = element_text(face="bold", colour = 'black')) +
  theme(plot.title = element_text(size = 19,hjust = 0.5,face="bold", colour = 'black')) + 
  theme(axis.title.x = element_text(size = 17,hjust = 0.5,face="bold", colour = 'black')) + 
  theme(axis.title.y = element_text(size = 17,hjust = 0.5,face="bold", colour = 'black')) + 
  theme(axis.text.x = element_text(hjust = 0.5, vjust=0.3,size=13,face="bold", colour = 'black'))+
  theme(axis.text.y = element_text(size=13,face="bold", colour = 'black'))+
  theme(panel.grid.major = element_blank()) +
  theme(panel.grid.minor = element_blank(),panel.background=element_blank(),panel.border=element_blank(),plot.background=element_blank()) +
  theme(axis.ticks = element_line(size = 1.1))+
  theme(legend.text=element_text(size=10,face="bold", colour = 'black'))


mytheme_2d <- theme_bw() + 
  theme(text = element_text(face="bold", colour = 'black')) +
  theme(plot.title = element_text(size = 19,hjust = 0.5,face="bold", colour = 'black')) + 
  theme(axis.title.x = element_text(size = 17,hjust = 0.5,face="bold", colour = 'black')) + 
  theme(axis.title.y = element_text(size = 17,hjust = 0.5,face="bold", colour = 'black')) + 
  theme(axis.text.x = element_text(hjust = 0.5, vjust=0.3,size=13,face="bold", colour = 'black'))+
  theme(axis.text.y = element_text(size=13,face="bold", colour = 'black'))+
  # theme(panel.grid.major = element_blank()) +
  # theme(panel.grid.minor = element_blank(),panel.background=element_blank(),plot.background=element_blank()) +
  theme(axis.ticks = element_line(size = 1.1))+
  theme(legend.text=element_text(size=10,face="bold", colour = 'black'))



# color collection
my_color_collection <- c(
  "#CBD588", "#5F7FC7", "orange", "#AD6F3B", "#673770", 
  "#D14285", "#652926", "#C84248", "#8569D5", "#5E738F",
  "#D1A33D", "#8A7C64", "#599861","#616163", "#FFCDB2",
  "#6D9F71", "#242F40",
  "#CCA43B", "#F92A82", "#ED7B84", "#7EB77F", 
  "#DEC4A1", "#E5D1D0", '#0E8482', '#C9DAEA', '#337357', 
  '#95C623', '#E55812', '#04471C', '#F2D7EE', '#D3BCC0', 
  '#A5668B', '#69306D', '#0E103D', '#1A535C', '#4ECDC4', 
  '#F7FFF7', '#FF6B6B', '#FFE66D', '#6699CC', '#FFF275', 
  '#FF8C42', '#FF3C38', '#A23E48', '#000000', '#CF5C36', 
  '#EEE5E9', '#7C7C7C', '#EFC88B', '#2E5266', '#6E8898', 
  '#9FB1BC', '#D3D0CB', '#E2C044', '#5BC0EB', '#FDE74C', 
  '#9BC53D', '#E55934', '#FA7921', "#CD9BCD", "#508578", "#DA5724")

# for git push, use this instead of using wflow_git_push()
# git push -u origin master (in the Git app / in the working directory)

# for making pdf file
library(rmarkdown)
# render("analysis/~~.Rmd", "pdf_document")
```


## 1. Import data table from python code
We are going to use the vcl3 treated standard curve that is fitted with pure Ammonia standards
```{r}
# import file
df_plate10 <- openxlsx::read.xlsx("data/211128_Ammonia_sample_plate10.xlsx")
df_plate11 <- openxlsx::read.xlsx("data/211128_Ammonia_sample_plate11.xlsx")

head(df_plate10)
colnames(df_plate10)
dim(df_plate10)

head(df_plate11)
colnames(df_plate11)
dim(df_plate11)

# X1 to Well
# df_p0 %<>% rename(Well = X1)
# df_p2 %<>% rename(Well = X1)
# df_p3 %<>% rename(Well = X1)
# df_p4 %<>% rename(Well = X1)
# df_p5 %<>% rename(Well = X1)
# df_p6 %<>% rename(Well = X1)
# df_p7 %<>% rename(Well = X1)
# df_p8 %<>% rename(Well = X1)
# df_p9 %<>% rename(Well = X1)
# df_p10 %<>% rename(Well = X1)
# df_p11 %<>% rename(Well = X1)

# remove wells that were contaminated during the experiment
# df_plate2 %<>% filter(!(Well %in% c("D02", "D03"))) # filter defect
# df_plate4 %<>% filter(!(Well %in% c("H05"))) # filter defect
# df_plate5 %<>% filter(!(Well %in% c("B03", "B04", "C03"))) # filter defect
# df_plate8 %<>% filter(!(Well %in% c("A01", "A09"))) # filter defect
# df_plate9 %<>% filter(!(Well %in% c("D11"))) # NA detected below...
# df_plate11 %<>% filter(!(Well %in% c("A12"))) # filter defect

# bind two dataframe
df_a <- rbind(df_plate10, df_plate11)
colnames(df_a)

# remove NA
dim(df_a) # 1046
rowSums(is.na(df_a)) > 0
df_a[rowSums(is.na(df_a)) > 0,]
df_a <- na.omit(df_a) # what is being omitted?
dim(df_a) # 1046

# multiply dilution factor which is 5/2
df_a %<>% mutate(NH4_mM = Ammonia_mM * (5/2))
head(df_a)

# extraction correction factor (only about 80% extraction)
# let's not multiply this at this moment.
# df_a %<>% mutate(Ammonia_ppm = Ammonia_ppm * (5/4))

colnames(df_a)

# Get the metadata for time point and left join
Time_table <- openxlsx::read.xlsx("data/211128_time_table.xlsx")
# Time_table_BN <- openxlsx::read.xlsx("data/220111_time_table_BN.xlsx")
# Time_table <- rbind(Time_table_AU, Time_table_BN)
Time_table %<>% select(-Date) 
Time_table$Time_hours <- round(Time_table$Time_hours, 1)
Time_table$Time_days <- round(Time_table$Time_days, 1)
df_time <- Time_table

dim(df_a)
df_a <- df_a %>% left_join(Time_table, by=("Time_point"="Time_point"))
dim(df_a)
colnames(df_a)
# time_point order
df_a$Time_point <-  factor(df_a$Time_point, levels = c("T9","T10"))
# df_a$Soil <-  factor(df_a$Soil, levels = c("LaBaghWoods_pH6.66","LaBaghWoods_autoclaved_pH6.66"))

```

## 2. Get average and standard deviation & Moisture correction & Blank correction
```{r}
# plot to see
ggplot(df_a, aes(x=Time_point, y=NH4_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  scale_fill_brewer(palette='Set2') +
  ylab("NH4+ (mM) \n") +
  xlab("\n Time point") +
  # scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  ggtitle("Without averaging \n") +
  mytheme_2d+
  theme(axis.text.x = element_text(hjust = 0.8, vjust=0.8, size=13, face="bold", angle = 40))

# plot all of blank together
df_a_blank <- df_a %>% filter(Sample_type %in% c("No_Nitrate", "Nitrate_Blank", "Ammonium_Blank", "Nitrite_Blank"))
df_a_blank$Time_point <- str_replace(df_a_blank$Time_point, ".*_","")

ggplot(df_a_blank, aes(x=Time_hours, y=NH4_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=3, shape=16, alpha=0.6) +
  # geom_line(size=1)+
  scale_fill_brewer(palette='Set2') +
  ylab("NH4+ (mM) \n") +
  xlab("\n Time_point") +
  # scale_y_continuous(breaks = seq(0,0.5,0.05), limits=c(0, 0.5))+
  ggtitle("Samples without moisture/blank correction \n") +
  mytheme_2d +
  theme(axis.text.x = element_text(hjust = 0.8, vjust=0.8, size=13, face="bold", angle = 40))+
  facet_grid(. ~ Soil) +
  theme(strip.background = element_rect(colour="black", fill="white", size=0.1))+
  theme(strip.text.x = element_text(size = 17))


# let's plot the no nitrate sample's nitrate, nitrite levels
df_no_nitrite <- df_a %>% filter(Sample_type == "No_Nitrate")

ggplot(df_no_nitrite, aes(x=Time_point, y=NH4_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  scale_fill_brewer(palette='Set2') +
  ylab("NH4+ (mM) \n") +
  xlab("\n Time_point") +
  # scale_y_continuous(breaks = seq(0,0.5,0.05), limits=c(0, 0.5))+
  ggtitle("Samples without nitrate addition \n") +
  mytheme_2d +
  theme(axis.text.x = element_text(hjust = 0.8, vjust=0.8, size=13, family="serif", angle = 40))
  

# let's plot the blank sample's nitrate, nitrite levels
df_A_blank <- df_a %>% filter(Sample_type == "Nitrate_Blank")
ggplot(df_A_blank, aes(x=Time_point, y=NH4_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  scale_fill_brewer(palette='Set2') +
  ylab("NH4+ (mM) \n") +
  xlab("\n Time_point") +
  scale_y_continuous(breaks = seq(0,2.5,0.1), limits=c(0, 2.5))+
  ggtitle("Nitrate blanks \n") +
  mytheme_2d +
  theme(axis.text.x = element_text(hjust = 0.8, vjust=0.8, size=13, family="serif", angle = 40))

# let's plot the Ammonium blank sample's nitrate, nitrite levels
df_NH4_blank <- df_a %>% filter(Sample_type == "Ammonium_Blank")
ggplot(df_NH4_blank, aes(x=Time_point, y=NH4_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  scale_fill_brewer(palette='Set2') +
  ylab("NH4+ (mM) \n") +
  xlab("\n Time_point") +
  scale_y_continuous(breaks = seq(0,2.5,0.1), limits=c(0, 2.5))+
  ggtitle("Ammonium blanks \n") +
  mytheme_2d +
  theme(axis.text.x = element_text(hjust = 0.8, vjust=0.8, size=13, family="serif", angle = 40))

# 1. Apply moisture correction factor (correcting for moisture in soil)
Added_Volume <- 1.4 # ml
Soil_mg <- 0.7

# soil_spike_ratio = 0.5  # soil weight(0.7g) / spike in volume (1.4ml) 
moisture_percent_1 = 19.9 # MIDWAY-A 
moisture_percent_2 = 53.9 # Washington-A 
moisture_percent_3 = 16.52 # Nichols-A 

mcf_1 = (soil_spike_ratio*(moisture_percent_1/100) + 1)
mcf_1
mcf_2 = (soil_spike_ratio*(moisture_percent_2/100) + 1)
mcf_2
mcf_3 = (soil_spike_ratio*(moisture_percent_3/100) + 1)
mcf_3

# apply moisture factor to each soil
dim(df_a)
df_a %>% select(Soil) %>% unique()

# this is a special case with no replicates
df_a_mcf_1 <- df_a %>% filter(Soil == "Midway-A_6.89") %>% filter(Sample_type == "Soil") %>% mutate(NH4_mM = NH4_mM * mcf_1)
dim(df_a_mcf_1) #423
df_a_mcf_2 <- df_a %>% filter(Soil == "Washington-A_7.88") %>%  filter(Sample_type == "Soil") %>% mutate(NH4_mM = NH4_mM * mcf_2)
dim(df_a_mcf_2) #426
df_a_mcf_3 <- df_a %>% filter(Soil == "Nichols-B_7.29") %>% filter(Sample_type == "Soil") %>% mutate(NH4_mM = NH4_mM * mcf_1)
dim(df_a_mcf_3) #426

df_a_others_mcf <- df_a %>% filter(Sample_type %in% c("Nitrite_Blank", "Nitrate_Blank", "Ammonium_Blank")) # Use Nitrate_Blank instead in the future
dim(df_a_others_mcf) #197
df_a_mcf <- rbind(df_a_mcf_1, df_a_mcf_2, df_a_mcf_3, df_a_others_mcf)
dim(df_a_mcf) # 1046

# plot to see
ggplot(df_a_mcf, aes(x=Time_hours, y=NH4_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  # geom_errorbar(aes(ymin=NO3_mM - Std_NO3_mM, ymax=NO3_mM + Std_NO3_mM), width=.05)+
  scale_fill_brewer(palette='Set2') +
  ylab("NH4+ (mM) \n") +
  xlab("\n Time (hours)") +
  # scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  ggtitle("No averaging with biological replicates \n") +
  mytheme_2d


```


## 3. Sanity check: moisture correction & blank correction factor 

Blank correction \
Use the Ammonia concentration of the blank and use the ratio. \
For example, multiply to Ammonia concentration x (2mM / changed [NO3]) \

```{r}
# without any correction
ggplot(df_a, aes(x=Time_hours, y=NH4_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  # geom_errorbar(aes(ymin=NH4_mM - Std_NH4_mM, ymax=NH4_mM + Std_NH4_mM), width=.05)+
  # scale_color_brewer(palette='Set2') +
  # scale_color_manual(values = c("deepskyblue4","maroon2"))+
  ylab("Measured NH4+ (mM) \n") +
  xlab("\n Time (hr)") +
  # scale_y_continuous(breaks = seq(0,5.1,1), limits=c(0, 5.1))+
  # scale_x_continuous(breaks = seq(0,5.1,1), limits=c(0, 5.1))+
  ggtitle("(Before moisture correction) All samples \n") +
  mytheme_2d +
  facet_grid(. ~ Soil) +
  theme(strip.background = element_rect(colour="black", fill="white", size=0.1))+
  theme(strip.text.x = element_text(size = 17))

# After moisture correction
ggplot(df_a_mcf, aes(x=Time_hours, y=NH4_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  # geom_errorbar(aes(ymin=NH4_mM - Std_NH4_mM, ymax=NH4_mM + Std_NH4_mM), width=.05)+
  # scale_color_brewer(palette='Set2') +
  # scale_color_manual(values = c("deepskyblue4","maroon2"))+
  ylab("Measured NH4+ (mM) \n") +
  xlab("\n Time (hr)") +
  # scale_y_continuous(breaks = seq(0,5.1,1), limits=c(0, 5.1))+
  # scale_x_continuous(breaks = seq(0,5.1,1), limits=c(0, 5.1))+
  ggtitle("(After moisture correction) All samples \n") +
  mytheme_2d +
  facet_grid(. ~ Soil) +
  theme(strip.background = element_rect(colour="black", fill="white", size=0.1))+
  theme(strip.text.x = element_text(size = 17))

```

## 4. Comparing aerobic and anaerobic samples

```{r}
colnames(df_a_mcf)
df_a_mcf$Category

df_compare <- df_a_mcf %>% filter(Sample_type == "Soil") 
ggplot(df_compare, aes(x=Time_hours, y=NH4_mM, color=Soil, group=Soil)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  # geom_errorbar(aes(ymin=NH4_mM - Std_NH4_mM, ymax=NH4_mM + Std_NH4_mM), width=.05)+
  # scale_color_brewer(palette='Set2') +
  # scale_color_manual(values = c("deepskyblue4","maroon2"))+
  ylab("Measured NH4+ (mM) \n") +
  xlab("\n Time (hr)") +
  # scale_y_continuous(breaks = seq(0,5.1,1), limits=c(0, 5.1))+
  # scale_x_continuous(breaks = seq(0,5.1,1), limits=c(0, 5.1))+
  ggtitle("Comparing aerobic and anaerobic samples \n") +
  mytheme_2d +
  facet_grid(. ~ Category) +
  theme(strip.background = element_rect(colour="black", fill="white", size=0.1))+
  theme(strip.text.x = element_text(size = 17))

# time point
ggplot(df_compare, aes(x=Time_point, y=NH4_mM, color=Soil, group=Soil)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  # geom_errorbar(aes(ymin=NH4_mM - Std_NH4_mM, ymax=NH4_mM + Std_NH4_mM), width=.05)+
  # scale_color_brewer(palette='Set2') +
  # scale_color_manual(values = c("deepskyblue4","maroon2"))+
  ylab("Measured NH4+ (mM) \n") +
  xlab("\n Time point") +
  # scale_y_continuous(breaks = seq(0,5.1,1), limits=c(0, 5.1))+
  # scale_x_continuous(breaks = seq(0,5.1,1), limits=c(0, 5.1))+
  ggtitle("Comparing aerobic and anaerobic samples \n") +
  mytheme_2d +
  facet_grid(. ~ Category) +
  theme(strip.background = element_rect(colour="black", fill="white", size=0.1))+
  theme(strip.text.x = element_text(size = 17))

# only timepoint T9

df_compare_T9 <- df_compare %>% filter(Time_point == "T9")
ggplot(df_compare_T9, aes(x=Category, y=NH4_mM, color=Soil)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  # geom_errorbar(aes(ymin=NH4_mM - Std_NH4_mM, ymax=NH4_mM + Std_NH4_mM), width=.05)+
  # scale_color_brewer(palette='Set2') +
  # scale_color_manual(values = c("deepskyblue4","maroon2"))+
  ylab("Measured NH4+ (mM) \n") +
  xlab("\n Time point") +
  # scale_y_continuous(breaks = seq(0,5.1,1), limits=c(0, 5.1))+
  # scale_x_continuous(breaks = seq(0,5.1,1), limits=c(0, 5.1))+
  ggtitle("Comparing aerobic and anaerobic samples (Time point T9: +200hr) \n") +
  mytheme_2d

```

