---
title: "220407_pH_troubleshooting"
author: "KiseokUchicago"
date: "2022-04-07"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---


```{r global_options, include=FALSE}
library(knitr)
knitr::opts_chunk$set(fig.width=11, fig.height=9,
                      error=TRUE, echo=TRUE, eval=TRUE, warning=FALSE, message=FALSE,
                      tidy.opts=list(width.cutoff=40),tidy=TRUE)
```

## Time series analysis - pH troubleshooting
Researcher: **Kiseok Lee** \
Experiment Date: 4/7/22 \
Analysis Date: 4/7/21 \
Lab: **Seppe Kuehn**

```{r, include=FALSE}
# libraries
library(dplyr)
library(ggplot2)
library(RColorBrewer)
library(vegan)
library(tidyverse)
library(magrittr)
library(readxl)
library(reshape2)
library(gtools)
library(devtools)
library(openxlsx)
library(ape)
library(stringr)
library(tidyr)
library(ggrepel)
library(ggpubr)

## theme for ggplot
mytheme <- theme_bw() + 
  theme(text = element_text(family="serif")) +
  theme(plot.title = element_text(size = 19,hjust = 0.5, family="serif")) + 
  theme(axis.title.x = element_text(size = 17,hjust = 0.5, family="serif")) + 
  theme(axis.title.y = element_text(size = 17,hjust = 0.5, family="serif")) + 
  theme(axis.text.x = element_text(hjust = 0.5, vjust=0.3,size=13, family="serif"))+
  theme(axis.text.y = element_text(size=10, family="serif"))+
  theme(panel.grid.major = element_blank()) +
  theme(panel.grid.minor = element_blank(),panel.background=element_blank(),panel.border=element_blank(),plot.background=element_blank()) +
  theme(axis.ticks = element_line(size = 1.1))

mytheme_2d <- theme_bw() + 
  theme(text = element_text(family="serif")) +
  theme(plot.title = element_text(size = 19,hjust = 0.5, family="serif")) + 
  theme(axis.title.x = element_text(size = 17,hjust = 0.5, family="serif")) + 
  theme(axis.title.y = element_text(size = 17,hjust = 0.5, family="serif")) + 
  theme(axis.text.x = element_text(hjust = 0.5, vjust=0.3,size=13, family="serif"))+
  theme(axis.text.y = element_text(size=13, family="serif"))+
  theme(axis.ticks = element_line(size = 1.1))
  # theme(panel.grid.major = element_blank()) +
  # theme(panel.grid.minor = element_blank(),panel.background=element_blank(),plot.background=element_blank()) +
  


# color collection
my_color_collection <- c(
  "#CBD588", "#5F7FC7", "orange", "#AD6F3B", "#673770", 
  "#D14285", "#652926", "#C84248", "#8569D5", "#5E738F",
  "#D1A33D", "#8A7C64", "#599861","#616163", "#FFCDB2",
  "#6D9F71", "#242F40",
  "#CCA43B", "#F92A82", "#ED7B84", "#7EB77F", 
  "#DEC4A1", "#E5D1D0", '#0E8482', '#C9DAEA', '#337357', 
  '#95C623', '#E55812', '#04471C', '#F2D7EE', '#D3BCC0', 
  '#A5668B', '#69306D', '#0E103D', '#1A535C', '#4ECDC4', 
  '#F7FFF7', '#FF6B6B', '#FFE66D', '#6699CC', '#FFF275', 
  '#FF8C42', '#FF3C38', '#A23E48', '#000000', '#CF5C36', 
  '#EEE5E9', '#7C7C7C', '#EFC88B', '#2E5266', '#6E8898', 
  '#9FB1BC', '#D3D0CB', '#E2C044', '#5BC0EB', '#FDE74C', 
  '#9BC53D', '#E55934', '#FA7921', "#CD9BCD", "#508578", "#DA5724")

# for git push, use this instead of using wflow_git_push()
# git push -u origin master (in the Git app / in the working directory)

# for making pdf file
library(rmarkdown)
# render("analysis/~~.Rmd", "pdf_document")
```

## First part, let's see how OD434 and OD585 are affected.
## Import data
```{r}
df_pH1 <- openxlsx::read.xlsx("data/220407_pH_colorimetric_pH_base_treatment_mu_opt_T0.xlsx")

dim(df_pH1)

# filter wells with too much soil
df_pH1 %<>% filter(!(Well %in% c("A06"))) # Filter defect A06 (I think I put 20ul of base)
# df_pH2 %<>% filter(!(Well %in% c("F11"))) # Less than 90ul of sample
# df_pH3 %<>% filter(!(Well %in% c("H01"))) # Filter defect A05
# df_pH4 %<>% filter(!(Well %in% c("F11"))) # Less than 90ul of sample
# df_pH6 %<>% filter(!(Well %in% c("A05"))) # Filter defect A05
# df_pH7 %<>% filter(!(Well %in% c("F11"))) # Less than 90ul of sample


# mols and molarity unit conversion
# test
# df_pH <- df_pH_T %>% filter(Titration_type %in% c("NaOH","HCl"))
df_pH <- df_pH1
dim(df_pH) # 160
Added_Volume <- 1.7 # ml
# Soil_mg <- 0.85
# moisture_percent_1 = 63.1 # Webster
# Added_Volume + Soil_mg*(moisture_percent_1/100)
# moisture_percent_2 = 6.8 # WarrenWoods1
# Added_Volume + Soil_mg*(moisture_percent_2/100)
# moisture_percent_3 = 9.0 # Crerar7
# Added_Volume + Soil_mg*(moisture_percent_3/100)

df_pH$Added_ul <- ifelse(df_pH$Titration_type == "NaOH", -1*df_pH$Added_ul, df_pH$Added_ul) # HCl is +, NaOH is -
df_pH %<>% mutate(H_mol = Concentration_M * Added_ul * 10^(-6)) # Calculate H mol 
df_pH$Volume = 1.7
# df_pH$Volume <- ifelse(df_pH$Soil == "Webster_pH3.3", Added_Volume + Soil_mg*(moisture_percent_1/100),
#                       ifelse(df_pH$Soil == "WarrenWoods1_pH5.23", Added_Volume + Soil_mg*(moisture_percent_2/100),
#                              ifelse(df_pH$Soil == "Crerar7_pH8.05", Added_Volume + Soil_mg*(moisture_percent_3/100),
#                                     0))) # Calc total volume# df_pH$Volume %>% unique()
df_pH %<>% mutate(H_Molarity = H_mol / (Volume * 10^(-3)))
df_pH %<>% mutate(H_mM = H_Molarity * 1000)
# openxlsx::write.xlsx(df_pH, "df_pH.xlsx")

# how many levels of H_mM?
df_pH %>% filter(Soil == "Webster_pH3.3")%>% select(H_mM) %>% unique() %>% arrange(H_mM)
df_pH %>% filter(Soil == "WarrenWoods1_pH5.23")%>% select(H_mM) %>% unique() %>% arrange(H_mM)
df_pH %>% filter(Soil == "Crerar7_pH8.05")%>% select(H_mM) %>% unique() %>% arrange(H_mM)
colnames(df_pH)

# average the pH
# 220407 only used 1 replicate. So, no need to average.
# df_pH_ave <- df_pH %>% group_by(Nitrite_input, Nitrate_input, Soil, Titration_type, Concentration_M, Added_ul, Sample_type, H_mol, H_Molarity, H_mM, Time_point, Time_minutes, Time_hours, Time_days) %>% summarise(Ave_pH = mean(pH_colorimetric), Std_pH = sd(pH_colorimetric)) %>% ungroup()

# colnames(df_pH_ave)

```

## plot OD434 and OD585
```{r}
df_OD <- read.xlsx("data/OD434_OD585_pH_base_treated_T0_220407.xlsx")
colnames(df_OD)[1] <- "Well"

# remove A06
df_OD %<>% filter(!(Well == "A06"))

df_OD_merged <- df_OD %>% left_join(df_pH, by=c("Well"="Well"))

df_OD <- df_OD_merged

# use this instead: OD434
plot(df_OD$H_mM, df_OD$OD434_background, col = "orange", lty = 1, pch = 17, lwd = 1, main = "OD434 (Control: water)",
     ylab = "OD434", xlab = "added [H+] mM", ylim = c(-1, 3), cex=2)

points(df_OD$H_mM, df_OD$OD434, col = "blue", pch = 17, cex=2)
points(df_OD$H_mM, df_OD$OD434_subtraction, col = 'red', pch = 17, lwd = 1)

legend("topright",legend = c("Background", "After dye", "(After dye - Background)"),
    col = c("orange", "blue", 'red'), bty = "n", pch = 17, cex = 1, box.lty = 0)


# use this instead
plot(df_OD$H_mM, df_OD$OD585_background, col = "orange", lty = 1, pch = 16, lwd = 1, main = "OD585 (Control: water)",
     ylab = "OD585", xlab = "added [H+] mM", ylim = c(0, 3), cex=2)

points(df_OD$H_mM, df_OD$OD585, col = "blue", pch = 16, cex=2)
points(df_OD$H_mM, df_OD$OD585_subtraction, col = 'red', pch = 16, lwd = 1)
legend("topright",legend = c("Background", "After dye", "(After dye - Background)"),
    col = c("orange", "blue", 'red'), bty = "n", pch = 16, cex = 1, box.lty = 0)

# R_multi?
plot(df_OD$H_mM, df_OD$R_multi, col = "red", lty = 1, pch = 15, lwd = 1, main = "R_multi (Control: water)",
     ylab = "R_multi", xlab = "added [H+] mM",cex=2)


# show R_multi and a_434, a_585
plot(df_OD$H_mM, df_OD$R_multi, col = "red", lty = 1, pch = 15, lwd = 1, main = "R_multi (Control: water)",
     ylab = "R_multi", xlab = "added [H+] mM",ylim = c(-20, 100), cex=2)
abline(a=0, b=0)
points(df_OD$H_mM, df_OD$OD434_subtraction, col = "red", pch = 17)
points(df_OD$H_mM, df_OD$OD585_subtraction, col = 'red', pch = 16, lwd = 1)

legend("topright",legend = c("OD434_corrected", "OC585_corrected", "R_multi = OD585/OD434"),
    pch = c(17, 16, 15), bty = "n", col = 'red', cex = 1.2, box.lty = 0)

# R_multi and pH

plot(df_OD$pH_colorimetric, df_OD$R_multi, col = "royalblue", lty = 1, pch = 18, lwd = 1, main = "R_multi (Control: water)",
     ylab = "R_multi", xlab = "pH_colorimetric", cex=1.5)


```


## For the second part, let's see how OD434 and OD585 are affected 
## Import data
```{r}
df_150ul <- openxlsx::read.xlsx("data/220407_pH_colorimetric_pH_standard_150ul_mu_opt_T0.xlsx")
df_300ul <- openxlsx::read.xlsx("data/220407_pH_colorimetric_pH_standard_300ul_mu_opt_T0.xlsx")
df_60ul <- openxlsx::read.xlsx("data/220407_pH_colorimetric_pH_standard_60ul_mu_opt_T0.xlsx")

df_OD_150ul <- read.xlsx("data/pH_standard_150ul_220407.xlsx")
df_OD_300ul <- read.xlsx("data/pH_standard_300ul_220407.xlsx")
df_OD_60ul <- read.xlsx("data/pH_standard_60ul_220407.xlsx")
colnames(df_OD_150ul)[1] <- "Well"
colnames(df_OD_300ul)[1] <- "Well"
colnames(df_OD_60ul)[1] <- "Well"

# merge
df_150_merged <- df_150ul %>% left_join(df_OD_150ul, by=c("Well"="Well")) %>% filter(!(Sample_type == "water"))
df_300_merged <- df_300ul %>% left_join(df_OD_300ul, by=c("Well"="Well")) %>% filter(!(Sample_type == "water"))
df_60_merged <- df_60ul %>% left_join(df_OD_60ul, by=c("Well"="Well")) %>% filter(!(Sample_type == "water"))
df_merged <- rbind(df_150_merged, df_300_merged, df_60_merged)

# Does this assay predict the standard's pH correctly?
df_merged$amount_ul <- factor(df_merged$amount_ul)

ggplot(df_merged, aes(x=pH, y=pH_colorimetric, color=amount_ul, group=amount_ul)) +
  geom_point(size=3, shape=16) +
  geom_abline(slope = 1, intercept=0, show.legend = "y=x")+
  # geom_line(size=1)+
  # scale_fill_brewer(palette='Set2') +
  ylab("pH by colorimetric assay \n") +
  xlab("\n pH standards (pH 4, 7, 10)") +
  scale_x_continuous(breaks = seq(4,10,1), limits=c(3.5, 10.5))+
  scale_y_continuous(breaks = seq(4,10,1), limits=c(3.5, 10.5))+
  ggtitle("Effect of sampling amount for pH assay (60ul vs 150ul vs 300ul, mu_opt from water) \n") +
  facet_grid(. ~ amount_ul) +
  mytheme_2d



# use this instead: OD434
plot(df_150_merged$pH, df_150_merged$OD434_background, col = "orange", lty = 1, pch = 17, lwd = 1, main = "OD434 (Control: water)",
     ylab = "OD434", xlab = "added [H+] mM", ylim = c(-1, 3), cex=2)

points(df_150_merged$pH, df_150_merged$OD434, col = "blue", pch = 17, cex=2)
points(df_150_merged$pH, df_150_merged$OD434_subtraction, col = 'red', pch = 17, lwd = 1)

legend("topright",legend = c("Background", "After dye", "(After dye - Background)"),
    col = c("orange", "blue", 'red'), bty = "n", pch = 17, cex = 1, box.lty = 0)


# use this instead
plot(df_150_merged$pH, df_150_merged$OD585_background, col = "orange", lty = 1, pch = 16, lwd = 1, main = "OD585 (Control: water)",
     ylab = "OD585", xlab = "added [H+] mM", ylim = c(-1, 10), xlim = c(1, 11), cex=2)

points(df_150_merged$pH, df_150_merged$OD585, col = "blue", pch = 16, cex=2)
points(df_150_merged$pH, df_150_merged$OD585_subtraction, col = 'red', pch = 16, lwd = 1)
legend("topright",legend = c("Background", "After dye", "(After dye - Background)"),
    col = c("orange", "blue", 'red'), bty = "n", pch = 16, cex = 1, box.lty = 0)

# R_multi?
plot(df_150_merged$pH, df_150_merged$R_multi, col = "red", lty = 1, pch = 15, lwd = 1, main = "R_multi (Control: water)",
     ylab = "R_multi", xlab = "added [H+] mM",cex=2)


# show R_multi and a_434, a_585
plot(df_150_merged$pH, df_150_merged$R_multi, col = "red", lty = 1, pch = 15, lwd = 1, main = "R_multi (Control: water)",
     ylab = "R_multi", xlab = "added [H+] mM",ylim = c(-20, 100), cex=2)
abline(a=0, b=0)
points(df_150_merged$pH, df_150_merged$OD434_subtraction, col = "red", pch = 17)
points(df_150_merged$pH, df_150_merged$OD585_subtraction, col = 'red', pch = 16, lwd = 1)

legend("topright",legend = c("OD434_corrected", "OC585_corrected", "R_multi = OD585/OD434"),
    pch = c(17, 16, 15), bty = "n", col = 'red', cex = 1.2, box.lty = 0)

# R_multi and pH

plot(df_150_merged$pH_colorimetric, df_150_merged$R_multi, col = "royalblue", lty = 1, pch = 18, lwd = 1, main = "R_multi (Control: water)",
     ylab = "R_multi", xlab = "pH_colorimetric", cex=1.5)


```


## Third part is to compare pH3 vs pH3_half
Same mu_opt_T0 was used for both plates.
```{r}

df_pH3 <- openxlsx::read.xlsx("data/220329_pH_colorimetric_pH3_mu_opt_T0.xlsx") 
df_pH3_half <- openxlsx::read.xlsx("data/220407_pH_colorimetric_pH3_half_mu_opt_T0.xlsx") 

df_pH3 %<>% filter(!(Well %in% c("H01", "G01"))) # Filter defect
df_pH3_half %<>% filter(!(Well %in% c("H01", "G01"))) # Filter defect

df_pH3$Plate_type <- "Normal"
df_pH3_half$Plate_type <- "Half_area"

df_time <- openxlsx::read.xlsx("data/220327_time_table.xlsx")
df_time$Time_hours <- round(df_time$Time_hours, 1)
df_time$Time_days <- round(df_time$Time_days, 2)

df_pH_T <- rbind(df_pH3, df_pH3_half)
df_pH_T %<>% left_join(df_time, by=c("Time_point"="Time_point"))
dim(df_pH_T) # 575

# remove NA
dim(df_pH_T) # 575
df_pH_T[is.na(df_pH_T)]
df_na <- df_pH_T[rowSums(is.na(df_pH_T)) > 0,]
# df_pH_T <- na.omit(df_pH_T)
df_pH_T <- df_pH_T[rowSums(is.na(df_pH_T)) == 0,]
dim(df_pH_T) # 548

# Change the soil names to include pH
# df_pH_T$Soil <- str_replace(df_pH_T$Soil,"NicholsC","NicholsC_pH7")
# df_pH_T$Soil <- str_replace(df_pH_T$Soil,"Allandale","Allandale_pH4")
# df_pH_T$Soil <-  factor(df_pH_T$Soil, levels = c("NicholsC_pH7", "Allandale_pH4"))

# mols and molarity unit conversion
# test
df_pH <- df_pH_T %>% filter(Titration_type %in% c("NaOH","HCl"))
dim(df_pH) # 160
Added_Volume <- 1.7 # ml
Soil_mg <- 0.85
moisture_percent_1 = 63.1 # Webster
Added_Volume + Soil_mg*(moisture_percent_1/100)
moisture_percent_2 = 6.8 # WarrenWoods1
Added_Volume + Soil_mg*(moisture_percent_2/100)
moisture_percent_3 = 9.0 # Crerar7
Added_Volume + Soil_mg*(moisture_percent_3/100)

df_pH$Added_ul <- ifelse(df_pH$Titration_type == "NaOH", -1*df_pH$Added_ul, df_pH$Added_ul) # HCl is +, NaOH is -
df_pH %<>% mutate(H_mol = Concentration_M * Added_ul * 10^(-6)) # Calculate H mol 
df_pH$Volume <- ifelse(df_pH$Soil == "Webster_pH3.3", Added_Volume + Soil_mg*(moisture_percent_1/100),
                      ifelse(df_pH$Soil == "WarrenWoods1_pH5.23", Added_Volume + Soil_mg*(moisture_percent_2/100),
                             ifelse(df_pH$Soil == "Crerar7_pH8.05", Added_Volume + Soil_mg*(moisture_percent_3/100),
                                    0))) # Calc total volume# df_pH$Volume %>% unique()
df_pH %<>% mutate(H_Molarity = H_mol / (Volume * 10^(-3)))
df_pH %<>% mutate(H_mM = H_Molarity * 1000)
# openxlsx::write.xlsx(df_pH, "df_pH.xlsx")

# how many levels of H_mM?
df_pH %>% filter(Soil == "Webster_pH3.3")%>% select(H_mM) %>% unique() %>% arrange(H_mM)
df_pH %>% filter(Soil == "WarrenWoods1_pH5.23")%>% select(H_mM) %>% unique() %>% arrange(H_mM)
df_pH %>% filter(Soil == "Crerar7_pH8.05")%>% select(H_mM) %>% unique() %>% arrange(H_mM)
colnames(df_pH)

df_pH$Plate_type

# there is something wrong about df_pH H_mM == 0
df_pH %>% filter(H_mM == 0)
# let's remove G1 as well
df_pH

```

plot titration curves

```{r}
df_plot <- df_pH

# let's plot Crerar first
df_plot %>% filter(Soil == "Crerar7_pH8.05")

ggplot(df_plot %>% filter(Soil == "Crerar7_pH8.05"), aes(x=H_mM, y=pH_colorimetric, color=Plate_type, group=Plate_type)) +
  geom_point(size=3, shape=16, alpha=1) +
  # geom_errorbar(aes(ymin=Ave_pH - Std_pH, ymax=Ave_pH + Std_pH), width=.05)+
  geom_line(size=1)+
  # scale_color_brewer(palette='Set1') +
  ylab("pH \n") +
  xlab("\n added [H+] mM") +
  scale_x_continuous(breaks = seq(-100,100,5))+
  scale_y_continuous(breaks = seq(0,14,1), limits=c(0, 14))+
  ggtitle("[Comparing normal vs half area plate] Soil pH perturbation titration curves (Crerar pH 8.05) \n") +
  # label
  # geom_text(aes(label = pH_colorimetric), size = 3, vjust = -1.5, family="serif", show.legend  = FALSE)+
  mytheme_2d

# let's plot Webster
df_plot %>% filter(Soil == "Webster_pH3.3")

ggplot(df_plot %>% filter(Soil == "Webster_pH3.3"), aes(x=H_mM, y=pH_colorimetric, color=Plate_type, group=Plate_type)) +
  geom_point(size=3, shape=16, alpha=1) +
  # geom_errorbar(aes(ymin=Ave_pH - Std_pH, ymax=Ave_pH + Std_pH), width=.05)+
  geom_line(size=1)+
  # scale_color_brewer(palette='Set1') +
  ylab("pH \n") +
  xlab("\n added [H+] mM") +
  scale_x_continuous(breaks = seq(-100,100,5), limits=c(-100, 100))+
  scale_y_continuous(breaks = seq(0,14,1), limits=c(0, 14))+
  ggtitle("[Comparing normal vs half area plate] Soil pH perturbation titration curves (Webster pH 3.3) \n") +
  # label
  # geom_text(aes(label = pH_colorimetric), size = 3, vjust = -1.5, family="serif", show.legend  = FALSE)+
  mytheme_2d


```

What is the reason for this??? \
Let's look at the OD434, OD585, and R_multi
```{r}
df_OD <- read.xlsx("data/OD434_OD585_pH3_half_area_220407.xlsx")
colnames(df_OD)[1] <- "Well"

# remove H01
df_OD %<>% filter(!(Well == "H01"))

df_pH_half <- df_pH %>% filter(Plate_type == "Half_area")
df_OD_merged <- df_OD %>% left_join(df_pH_half, by=c("Well"="Well"))

df_OD <- df_OD_merged

# first Crerar soil first
df_OD_C <- df_OD %>% filter(Soil == "Crerar7_pH8.05")

# use this instead: OD434
plot(df_OD_C$H_mM, df_OD_C$OD434_background, col = "orange", lty = 1, pch = 17, lwd = 1, main = "OD434 (Crerar7_T5 half_area plate)",
     ylab = "OD434", xlab = "added [H+] mM", ylim = c(-1, 4), cex=2)

points(df_OD_C$H_mM, df_OD_C$OD434, col = "blue", pch = 17, cex=2)
points(df_OD_C$H_mM, df_OD_C$OD434_subtraction, col = 'red', pch = 17, lwd = 1)

legend("topright",legend = c("Background", "After dye", "(After dye - Background)"),
    col = c("orange", "blue", 'red'), bty = "n", pch = 17, cex = 1, box.lty = 0)


# use this instead
plot(df_OD_C$H_mM, df_OD_C$OD585_background, col = "orange", lty = 1, pch = 16, lwd = 1, main = "OD585 (Crerar7_T5 half_area plate)",
     ylab = "OD585", xlab = "added [H+] mM", ylim = c(-2, 6), cex=2)

points(df_OD_C$H_mM, df_OD_C$OD585, col = "blue", pch = 16, cex=2)
points(df_OD_C$H_mM, df_OD_C$OD585_subtraction, col = 'red', pch = 16, lwd = 1)
legend("topright",legend = c("Background", "After dye", "(After dye - Background)"),
    col = c("orange", "blue", 'red'), bty = "n", pch = 16, cex = 1, box.lty = 0)

# R_multi?
plot(df_OD_C$H_mM, df_OD_C$R_multi, col = "red", lty = 1, pch = 15, lwd = 1, main = "R_multi (Crerar7_T5 half_area plate)",
     ylab = "R_multi", xlab = "added [H+] mM",cex=2)


# show R_multi and a_434, a_585
plot(df_OD_C$H_mM, df_OD_C$R_multi, col = "red", lty = 1, pch = 15, lwd = 1, main = "R_multi (Crerar7_T5 half_area plate)",
     ylab = "R_multi", xlab = "added [H+] mM",ylim = c(-80, 70), cex=2)
abline(a=0, b=0)
points(df_OD_C$H_mM, df_OD_C$OD434_subtraction, col = "red", pch = 17)
points(df_OD_C$H_mM, df_OD_C$OD585_subtraction, col = 'red', pch = 16, lwd = 1)

legend("topright",legend = c("OD434_corrected", "OC585_corrected", "R_multi = OD585/OD434"),
    pch = c(17, 16, 15), bty = "n", col = 'red', cex = 1.2, box.lty = 0)

# R_multi and pH

plot(df_OD_C$pH_colorimetric, df_OD_C$R_multi, col = "royalblue", lty = 1, pch = 18, lwd = 1, main = "R_multi (Crerar7_T5 half_area plate)",
     ylab = "R_multi", xlab = "pH_colorimetric", cex=1.5)


```

Next up, let's look at webster half area

```{r}
df_OD_WB <- df_OD %>% filter(Soil == "Webster_pH3.3")

# use this instead: OD434
plot(df_OD_WB$H_mM, df_OD_WB$OD434_background, col = "orange", lty = 1, pch = 17, lwd = 1, main = "OD434 (Webster_T5 half_area plate)",
     ylab = "OD434", xlab = "added [H+] mM", cex=2)

plot(df_OD_WB$H_mM, df_OD_WB$OD434_background, col = "orange", lty = 1, pch = 17, lwd = 1, main = "OD434 (Webster_T5 half_area plate)",
     ylab = "OD434", xlab = "added [H+] mM", ylim = c(-1, 10), cex=2)

points(df_OD_WB$H_mM, df_OD_WB$OD434, col = "blue", pch = 17, cex=2)
points(df_OD_WB$H_mM, df_OD_WB$OD434_subtraction, col = 'red', pch = 17, lwd = 1)

legend("topright",legend = c("Background", "After dye", "(After dye - Background)"),
    col = c("orange", "blue", 'red'), bty = "n", pch = 17, cex = 1, box.lty = 0)


# use this instead
plot(df_OD_WB$H_mM, df_OD_WB$OD585_background, col = "orange", lty = 1, pch = 16, lwd = 1, main = "OD585 (Webster_T5 half_area plate)",
     ylab = "OD585", xlab = "added [H+] mM",cex=2)

plot(df_OD_WB$H_mM, df_OD_WB$OD585_background, col = "orange", lty = 1, pch = 16, lwd = 1, main = "OD585 (Webster_T5 half_area plate)",
     ylab = "OD585", xlab = "added [H+] mM", ylim = c(-1, 5), cex=2)

points(df_OD_WB$H_mM, df_OD_WB$OD585, col = "blue", pch = 16, cex=2)
points(df_OD_WB$H_mM, df_OD_WB$OD585_subtraction, col = 'red', pch = 16, lwd = 1)
legend("topright",legend = c("Background", "After dye", "(After dye - Background)"),
    col = c("orange", "blue", 'red'), bty = "n", pch = 16, cex = 1, box.lty = 0)

# R_multi?
plot(df_OD_WB$H_mM, df_OD_WB$R_multi, col = "red", lty = 1, pch = 15, lwd = 1, main = "R_multi (Webster_T5 half_area plate)",
     ylab = "R_multi", xlab = "added [H+] mM",cex=2)


# show R_multi and a_434, a_585
plot(df_OD_WB$H_mM, df_OD_WB$R_multi, col = "red", lty = 1, pch = 15, lwd = 1, main = "R_multi (Webster_T5 half_area plate)",
     ylab = "R_multi", xlab = "added [H+] mM",ylim = c(-20, 120), cex=2)
abline(a=0, b=0)
points(df_OD_WB$H_mM, df_OD_WB$OD434_subtraction, col = "red", pch = 17)
points(df_OD_WB$H_mM, df_OD_WB$OD585_subtraction, col = 'red', pch = 16, lwd = 1)

legend("topright",legend = c("OD434_corrected", "OC585_corrected", "R_multi = OD585/OD434"),
    pch = c(17, 16, 15), bty = "n", col = 'red', cex = 1.2, box.lty = 0)

# R_multi and pH

plot(df_OD_WB$pH_colorimetric, df_OD_WB$R_multi, col = "royalblue", lty = 1, pch = 18, lwd = 1, main = "R_multi (Webster_T5 half_area plate)",
     ylab = "R_multi", xlab = "pH_colorimetric", cex=1.5)


```

Back to OD434_OD585_C_WB_T5_220329 \
This is normal area plate. 60ul.
```{r}
df_OD <- read.xlsx("data/OD434_OD585_C_WB_T5_220329.xlsx")
colnames(df_OD)[1] <- "Well"

# remove H01
df_OD %<>% filter(!(Well == "H01"))

df_pH_normal <- df_pH %>% filter(Plate_type == "Normal")
df_OD_merged <- df_OD %>% left_join(df_pH_normal, by=c("Well"="Well"))

df_OD <- df_OD_merged

# first Crerar soil first
df_OD_C <- df_OD %>% filter(Soil == "Crerar7_pH8.05")

# use this instead: OD434
plot(df_OD_C$H_mM, df_OD_C$OD434_background, col = "orange", lty = 1, pch = 17, lwd = 1, main = "OD434 (Crerar7_T5 normal plate)",
     ylab = "OD434", xlab = "added [H+] mM",  cex=2)

plot(df_OD_C$H_mM, df_OD_C$OD434_background, col = "orange", lty = 1, pch = 17, lwd = 1, main = "OD434 (Crerar7_T5 normal plate)",
     ylab = "OD434", xlab = "added [H+] mM", ylim = c(-1, 4), cex=2)

points(df_OD_C$H_mM, df_OD_C$OD434, col = "blue", pch = 17, cex=2)
points(df_OD_C$H_mM, df_OD_C$OD434_subtraction, col = 'red', pch = 17, lwd = 1)

legend("topright",legend = c("Background", "After dye", "(After dye - Background)"),
    col = c("orange", "blue", 'red'), bty = "n", pch = 17, cex = 1, box.lty = 0)


# use this instead
plot(df_OD_C$H_mM, df_OD_C$OD585_background, col = "orange", lty = 1, pch = 16, lwd = 1, main = "OD585 (Crerar7_T5 normal plate)",
     ylab = "OD585", xlab = "added [H+] mM", ylim = c(-2, 6), cex=2)

points(df_OD_C$H_mM, df_OD_C$OD585, col = "blue", pch = 16, cex=2)
points(df_OD_C$H_mM, df_OD_C$OD585_subtraction, col = 'red', pch = 16, lwd = 1)
legend("topright",legend = c("Background", "After dye", "(After dye - Background)"),
    col = c("orange", "blue", 'red'), bty = "n", pch = 16, cex = 1, box.lty = 0)

# R_multi?
plot(df_OD_C$H_mM, df_OD_C$R_multi, col = "red", lty = 1, pch = 15, lwd = 1, main = "R_multi (Crerar7_T5 normal plate)",
     ylab = "R_multi", xlab = "added [H+] mM",cex=2)


# show R_multi and a_434, a_585
plot(df_OD_C$H_mM, df_OD_C$R_multi, col = "red", lty = 1, pch = 15, lwd = 1, main = "R_multi (Crerar7_T5 normal plate)",
     ylab = "R_multi", xlab = "added [H+] mM",ylim = c(-80, 70), cex=2)
abline(a=0, b=0)
points(df_OD_C$H_mM, df_OD_C$OD434_subtraction, col = "red", pch = 17)
points(df_OD_C$H_mM, df_OD_C$OD585_subtraction, col = 'red', pch = 16, lwd = 1)

legend("topright",legend = c("OD434_corrected", "OC585_corrected", "R_multi = OD585/OD434"),
    pch = c(17, 16, 15), bty = "n", col = 'red', cex = 1.2, box.lty = 0)

# R_multi and pH

plot(df_OD_C$pH_colorimetric, df_OD_C$R_multi, col = "royalblue", lty = 1, pch = 18, lwd = 1, main = "R_multi (Crerar7_T5 normal plate)",
     ylab = "R_multi", xlab = "pH_colorimetric", cex=1.5)


```

Next up, let's look at webster half area

```{r}
df_OD_WB <- df_OD %>% filter(Soil == "Webster_pH3.3")

# use this instead: OD434
plot(df_OD_WB$H_mM, df_OD_WB$OD434_background, col = "orange", lty = 1, pch = 17, lwd = 1, main = "OD434 (Webster_T5 normal plate)",
     ylab = "OD434", xlab = "added [H+] mM", cex=2)

plot(df_OD_WB$H_mM, df_OD_WB$OD434_background, col = "orange", lty = 1, pch = 17, lwd = 1, main = "OD434 (Webster_T5 normal plate)",
     ylab = "OD434", xlab = "added [H+] mM", ylim = c(-1, 10), cex=2)

points(df_OD_WB$H_mM, df_OD_WB$OD434, col = "blue", pch = 17, cex=2)
points(df_OD_WB$H_mM, df_OD_WB$OD434_subtraction, col = 'red', pch = 17, lwd = 1)

legend("topright",legend = c("Background", "After dye", "(After dye - Background)"),
    col = c("orange", "blue", 'red'), bty = "n", pch = 17, cex = 1, box.lty = 0)


# use this instead
plot(df_OD_WB$H_mM, df_OD_WB$OD585_background, col = "orange", lty = 1, pch = 16, lwd = 1, main = "OD585 (Webster_T5 normal plate)",
     ylab = "OD585", xlab = "added [H+] mM",cex=2)

plot(df_OD_WB$H_mM, df_OD_WB$OD585_background, col = "orange", lty = 1, pch = 16, lwd = 1, main = "OD585 (Webster_T5 normal plate)",
     ylab = "OD585", xlab = "added [H+] mM", ylim = c(-1, 5), cex=2)

points(df_OD_WB$H_mM, df_OD_WB$OD585, col = "blue", pch = 16, cex=2)
points(df_OD_WB$H_mM, df_OD_WB$OD585_subtraction, col = 'red', pch = 16, lwd = 1)
legend("topright",legend = c("Background", "After dye", "(After dye - Background)"),
    col = c("orange", "blue", 'red'), bty = "n", pch = 16, cex = 1, box.lty = 0)

# R_multi?
plot(df_OD_WB$H_mM, df_OD_WB$R_multi, col = "red", lty = 1, pch = 15, lwd = 1, main = "R_multi (Webster_T5 normal plate)",
     ylab = "R_multi", xlab = "added [H+] mM",cex=2)


# show R_multi and a_434, a_585
plot(df_OD_WB$H_mM, df_OD_WB$R_multi, col = "red", lty = 1, pch = 15, lwd = 1, main = "R_multi (Webster_T5 normal plate)",
     ylab = "R_multi", xlab = "added [H+] mM",ylim = c(-20, 120), cex=2)
abline(a=0, b=0)
points(df_OD_WB$H_mM, df_OD_WB$OD434_subtraction, col = "red", pch = 17)
points(df_OD_WB$H_mM, df_OD_WB$OD585_subtraction, col = 'red', pch = 16, lwd = 1)

legend("topright",legend = c("OD434_corrected", "OC585_corrected", "R_multi = OD585/OD434"),
    pch = c(17, 16, 15), bty = "n", col = 'red', cex = 1.2, box.lty = 0)

# R_multi and pH

plot(df_OD_WB$pH_colorimetric, df_OD_WB$R_multi, col = "royalblue", lty = 1, pch = 18, lwd = 1, main = "R_multi (Webster_T5 normal plate)",
     ylab = "R_multi", xlab = "pH_colorimetric", cex=1.5)


```


