---
title: "220420_Ammonia_3_soil_pH_perturbation"
author: "KiseokUchicago"
date: "2022-04-28"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---


```{r global_options, include=FALSE}
library(knitr)
knitr::opts_chunk$set(fig.width=11, fig.height=9,
                      error=TRUE, echo=TRUE, eval=TRUE, warning=FALSE, message=FALSE,
                      tidy.opts=list(width.cutoff=40),tidy=TRUE)
```

## 3 soils with different pH levels (Ammonia assay - Salicylate-Hypochloride assay)
Researcher: **Kiseok Lee** \
Experiment Date: 3/6/22 - 3/10/22 (5 days) \
Analysis Date: 4/28/21
Lab: **Seppe Kuehn**

```{r}
# libraries
library(dplyr)
library(ggplot2)
library(RColorBrewer)
library(vegan)
library(tidyverse)
library(magrittr)
library(readxl)
library(reshape2)
library(gtools)
library(devtools)
library(openxlsx)
library(ape)
library(stringr)
library(tidyr)
library(ggrepel)
library(ggpubr)

## theme for ggplot
mytheme <- theme_bw() + 
  theme(text = element_text(face="bold", colour = 'black')) +
  theme(plot.title = element_text(size = 19,hjust = 0.5,face="bold", colour = 'black')) + 
  theme(axis.title.x = element_text(size = 17,hjust = 0.5,face="bold", colour = 'black')) + 
  theme(axis.title.y = element_text(size = 17,hjust = 0.5,face="bold", colour = 'black')) + 
  theme(axis.text.x = element_text(hjust = 0.5, vjust=0.3,size=13,face="bold", colour = 'black'))+
  theme(axis.text.y = element_text(size=13,face="bold", colour = 'black'))+
  theme(panel.grid.major = element_blank()) +
  theme(panel.grid.minor = element_blank(),panel.background=element_blank(),panel.border=element_blank(),plot.background=element_blank()) +
  theme(axis.ticks = element_line(size = 1.1))+
  theme(legend.text=element_text(size=10,face="bold", colour = 'black'))


mytheme_2d <- theme_bw() + 
  theme(text = element_text(face="bold", colour = 'black')) +
  theme(plot.title = element_text(size = 19,hjust = 0.5,face="bold", colour = 'black')) + 
  theme(axis.title.x = element_text(size = 17,hjust = 0.5,face="bold", colour = 'black')) + 
  theme(axis.title.y = element_text(size = 17,hjust = 0.5,face="bold", colour = 'black')) + 
  theme(axis.text.x = element_text(hjust = 0.5, vjust=0.3,size=13,face="bold", colour = 'black'))+
  theme(axis.text.y = element_text(size=13,face="bold", colour = 'black'))+
  # theme(panel.grid.major = element_blank()) +
  # theme(panel.grid.minor = element_blank(),panel.background=element_blank(),plot.background=element_blank()) +
  theme(axis.ticks = element_line(size = 1.1))+
  theme(legend.text=element_text(size=10,face="bold", colour = 'black'))



# color collection
my_color_collection <- c(
  "#CBD588", "#5F7FC7", "orange", "#AD6F3B", "#673770", 
  "#D14285", "#652926", "#C84248", "#8569D5", "#5E738F",
  "#D1A33D", "#8A7C64", "#599861","#616163", "#FFCDB2",
  "#6D9F71", "#242F40",
  "#CCA43B", "#F92A82", "#ED7B84", "#7EB77F", 
  "#DEC4A1", "#E5D1D0", '#0E8482', '#C9DAEA', '#337357', 
  '#95C623', '#E55812', '#04471C', '#F2D7EE', '#D3BCC0', 
  '#A5668B', '#69306D', '#0E103D', '#1A535C', '#4ECDC4', 
  '#F7FFF7', '#FF6B6B', '#FFE66D', '#6699CC', '#FFF275', 
  '#FF8C42', '#FF3C38', '#A23E48', '#000000', '#CF5C36', 
  '#EEE5E9', '#7C7C7C', '#EFC88B', '#2E5266', '#6E8898', 
  '#9FB1BC', '#D3D0CB', '#E2C044', '#5BC0EB', '#FDE74C', 
  '#9BC53D', '#E55934', '#FA7921', "#CD9BCD", "#508578", "#DA5724")

# for git push, use this instead of using wflow_git_push()
# git push -u origin master (in the Git app / in the working directory)

# for making pdf file
library(rmarkdown)
# render("analysis/~~.Rmd", "pdf_document")
```


## 1. Import data table from python code
We are going to use the vcl3 treated standard curve that is fitted with pure Ammonia standards
```{r}
# import file
df_plate1 <- openxlsx::read.xlsx("data/220420_Ammonia_sample_plate1.xlsx")
df_plate2 <- openxlsx::read.xlsx("data/220420_Ammonia_sample_plate2.xlsx")
df_plate3 <- openxlsx::read.xlsx("data/220420_Ammonia_sample_plate3.xlsx")
df_plate4 <- openxlsx::read.xlsx("data/220420_Ammonia_sample_plate4.xlsx")
df_plate5 <- openxlsx::read.xlsx("data/220420_Ammonia_sample_plate5.xlsx")
df_plate6 <- openxlsx::read.xlsx("data/220420_Ammonia_sample_plate6.xlsx")
df_plate7 <- openxlsx::read.xlsx("data/220420_Ammonia_sample_plate7.xlsx")
df_plate8 <- openxlsx::read.xlsx("data/220420_Ammonia_sample_plate8.xlsx")
df_plate9 <- openxlsx::read.xlsx("data/220420_Ammonia_sample_plate9.xlsx")
df_plate10 <- openxlsx::read.xlsx("data/220420_Ammonia_sample_plate10.xlsx")
df_plate11 <- openxlsx::read.xlsx("data/220420_Ammonia_sample_plate11.xlsx")
df_plate12 <- openxlsx::read.xlsx("data/220420_Ammonia_sample_plate12.xlsx")
df_plate13 <- openxlsx::read.xlsx("data/220420_Ammonia_sample_plate13.xlsx")
df_plate14 <- openxlsx::read.xlsx("data/220420_Ammonia_sample_plate14.xlsx")
df_plate15 <- openxlsx::read.xlsx("data/220420_Ammonia_sample_plate15.xlsx")
df_plate16 <- openxlsx::read.xlsx("data/220420_Ammonia_sample_plate16.xlsx")


head(df_plate1)
colnames(df_plate1)
dim(df_plate1)

head(df_plate2)
colnames(df_plate2)
dim(df_plate2)

head(df_plate3)
colnames(df_plate3)
dim(df_plate3)

head(df_plate4)
colnames(df_plate4)
dim(df_plate4)

head(df_plate5)
colnames(df_plate5)
dim(df_plate5)

head(df_plate6)
colnames(df_plate6)
dim(df_plate6)

head(df_plate7)
colnames(df_plate7)
dim(df_plate7)

head(df_plate8)
colnames(df_plate8)
dim(df_plate8)

head(df_plate9)
colnames(df_plate9)
dim(df_plate9)

head(df_plate10)
colnames(df_plate10)
dim(df_plate10)

head(df_plate11)
colnames(df_plate11)
dim(df_plate11)

head(df_plate12)
colnames(df_plate12)
dim(df_plate12)

head(df_plate13)
colnames(df_plate13)
dim(df_plate13)

head(df_plate14)
colnames(df_plate14)
dim(df_plate14)

head(df_plate15)
colnames(df_plate15)
dim(df_plate15)

head(df_plate16)
colnames(df_plate16)
dim(df_plate16)

# X1 to Well
df_plate1 %<>% rename(Well = X1)
df_plate2 %<>% rename(Well = X1)
df_plate3 %<>% rename(Well = X1)
df_plate4 %<>% rename(Well = X1)
df_plate5 %<>% rename(Well = X1)
df_plate6 %<>% rename(Well = X1)
df_plate7 %<>% rename(Well = X1)
df_plate8 %<>% rename(Well = X1)
df_plate9 %<>% rename(Well = X1)
df_plate10 %<>% rename(Well = X1)
df_plate11 %<>% rename(Well = X1)
df_plate12 %<>% rename(Well = X1)
df_plate13 %<>% rename(Well = X1)
df_plate14 %<>% rename(Well = X1)
df_plate15 %<>% rename(Well = X1)
df_plate16 %<>% rename(Well = X1)



# remove wells that were contaminated during the experiment
df_plate4 %<>% filter(!(Well %in% c("A12", "B12"))) # filter defect
df_plate12 %<>% filter(!(Well %in% c("A01"))) # filter defect

# bind two dataframe
df_a <- rbind(df_plate1, df_plate2, df_plate3, df_plate4, df_plate5, df_plate6, df_plate7, df_plate8, df_plate9, df_plate10, df_plate11, df_plate12, df_plate13, df_plate14, df_plate15, df_plate16)
colnames(df_a)

# remove NA
dim(df_a) # 1046
rowSums(is.na(df_a)) > 0
df_a[rowSums(is.na(df_a)) > 0,]
df_a <- na.omit(df_a) # what is being omitted?
dim(df_a) # 1453

# multiply dilution factor which is 5/2
df_a %<>% mutate(NH4_mM = Ammonia_mM * (5/2))
head(df_a)

# extraction correction factor (only about 80% extraction)
# let's not multiply this at this moment.
# df_a %<>% mutate(Ammonia_mM = Ammonia_mM * (5/4))

colnames(df_a)

# Get the metadata for time point and left join
Time_table <- openxlsx::read.xlsx("data/220327_time_table.xlsx")
# Time_table_BN <- openxlsx::read.xlsx("data/220111_time_table_BN.xlsx")
# Time_table <- rbind(Time_table_AU, Time_table_BN)
Time_table %<>% select(-Date) 
Time_table$Time_hours <- round(Time_table$Time_hours, 1)
Time_table$Time_days <- round(Time_table$Time_days, 1)
df_time <- Time_table

dim(df_a)
df_a <- df_a %>% left_join(Time_table, by=("Time_point"="Time_point"))
dim(df_a)
colnames(df_a)
# time_point order
df_a$Time_point <-  factor(df_a$Time_point, levels = c(paste0("C_T",0:10), paste0("WW_T",0:10), paste0("WB_T",0:10)))

```


## 2. Get average and standard deviation & Moisture correction & Blank correction
```{r}
# plot to see
ggplot(df_a, aes(x=Time_point, y=NH4_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  scale_fill_brewer(palette='Set2') +
  ylab("NH4+ (mM) \n") +
  xlab("\n Time point") +
  # scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  ggtitle("Without averaging \n") +
  mytheme_2d+
  theme(axis.text.x = element_text(hjust = 0.8, vjust=0.8, size=13, face="bold", angle = 40))

# plot all of blank together
df_a_blank <- df_a %>% filter(Sample_type %in% c("No_Nitrate", "Nitrate_Blank", "Ammonium_Blank", "Nitrite_Blank"))
df_a_blank$Time_point <- str_replace(df_a_blank$Time_point, ".*_","")

ggplot(df_a_blank, aes(x=Time_hours, y=NH4_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=3, shape=16, alpha=0.6) +
  # geom_line(size=1)+
  scale_fill_brewer(palette='Set2') +
  ylab("NH4+ (mM) \n") +
  xlab("\n Time_point") +
  # scale_y_continuous(breaks = seq(0,0.5,0.05), limits=c(0, 0.5))+
  ggtitle("Samples without moisture/blank correction \n") +
  mytheme_2d +
  theme(axis.text.x = element_text(hjust = 0.8, vjust=0.8, size=13, face="bold", angle = 40))+
  facet_grid(. ~ Soil) +
  theme(strip.background = element_rect(colour="black", fill="white", size=0.1))+
  theme(strip.text.x = element_text(size = 17))


# let's plot the no nitrate sample's nitrate, nitrite levels
df_no_nitrite <- df_a %>% filter(Sample_type == "No_Nitrate")

ggplot(df_no_nitrite, aes(x=Time_point, y=NH4_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  scale_fill_brewer(palette='Set2') +
  ylab("NH4+ (mM) \n") +
  xlab("\n Time_point") +
  # scale_y_continuous(breaks = seq(0,0.5,0.05), limits=c(0, 0.5))+
  ggtitle("Samples without nitrate addition \n") +
  mytheme_2d +
  theme(axis.text.x = element_text(hjust = 0.8, vjust=0.8, size=13, face="bold", angle = 40))

# let's plot the blank sample's nitrate, nitrite levels
df_A_blank <- df_a %>% filter(Sample_type == "Nitrate_Blank")
ggplot(df_A_blank, aes(x=Time_point, y=NH4_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  scale_fill_brewer(palette='Set2') +
  ylab("NH4+ (mM) \n") +
  xlab("\n Time_point") +
  scale_y_continuous(breaks = seq(0,2.5,0.1), limits=c(0, 2.5))+
  ggtitle("Nitrate blanks \n") +
  mytheme_2d +
  theme(axis.text.x = element_text(hjust = 0.8, vjust=0.8, size=13, face="bold", angle = 40))

# let's plot the Ammonium blank sample's nitrate, nitrite levels
df_NH4_blank <- df_a %>% filter(Sample_type == "Ammonium_Blank")
ggplot(df_NH4_blank, aes(x=Time_point, y=NH4_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  scale_fill_brewer(palette='Set2') +
  ylab("NH4+ (mM) \n") +
  xlab("\n Time_point") +
  scale_y_continuous(breaks = seq(0,2.5,0.1), limits=c(0, 2.5))+
  ggtitle("Ammonium blanks \n") +
  mytheme_2d +
  theme(axis.text.x = element_text(hjust = 0.8, vjust=0.8, size=13, face="bold", angle = 40))




# Setting H_mM column
# df_soil <- df_a %>% filter(Titration_type %in% c("NaOH","HCl"))

## moisture correction
Added_Volume <- 1.7 # ml
Soil_mg <- 0.85
moisture_percent_1 = 63.1 # Webster
Added_Volume + Soil_mg*(moisture_percent_1/100)
moisture_percent_2 = 6.8 # WarrenWoods1
Added_Volume + Soil_mg*(moisture_percent_2/100)
moisture_percent_3 = 9.0 # Crerar7
Added_Volume + Soil_mg*(moisture_percent_3/100)

df_a$Added_ul <- ifelse(df_a$Titration_type == "NaOH", -1*df_a$Added_ul, df_a$Added_ul) # HCl is +, NaOH is -
df_a %<>% mutate(H_mol = Concentration_M * Added_ul * 10^(-6)) # Calculate H mol 
df_a$Volume <- ifelse(df_a$Soil == "Webster_pH3.3", Added_Volume + Soil_mg*(moisture_percent_1/100),
                      ifelse(df_a$Soil == "WarrenWoods1_pH5.23", Added_Volume + Soil_mg*(moisture_percent_2/100),
                             ifelse(df_a$Soil == "Crerar1_pH8.05", Added_Volume + Soil_mg*(moisture_percent_3/100),
                                    0))) # Calc total volume

# df_a$Volume <- ifelse(df_a$Soil == "Allandale_pH4", Added_Volume + Soil_mg*(moisture_percent_2/100), df_a$Volume) # Calc total volume
# df_a$Volume %>% unique()
df_a %<>% mutate(H_Molarity = H_mol / (Volume * 10^(-3)))
df_a %<>% mutate(H_mM = H_Molarity * 1000)
dim(df_a) # 1453
# openxlsx::write.xlsx(df_a, "df_a.xlsx")

# how many levels of H_mM?
df_a %>% filter(Soil == "Webster_pH3.3")%>% select(H_mM) %>% unique() %>% arrange(H_mM)
df_a %>% filter(Soil == "WarrenWoods1_pH5.23")%>% select(H_mM) %>% unique() %>% arrange(H_mM)
df_a %>% filter(Soil == "Crerar1_pH8.05")%>% select(H_mM) %>% unique() %>% arrange(H_mM)
colnames(df_a)


dim(df_a)

# Testing negative samples
df_no3_blank <- df_a %>% filter(Sample_type == "Nitrate_Blank")  # Use Nitrate_Blank instead in the future
df_no3_blank # 33

df_no2_blank <- df_a %>% filter(Sample_type == "Nitrite_Blank")
df_no2_blank # 33
# close to zero

# 1. Apply moisture correction factor (correcting for moisture in soil)
soil_spike_ratio = 0.5 # soil weight(0.85g) / spike in volume (1.7ml) 

mcf_1 = (soil_spike_ratio*(moisture_percent_1/100) + 1)
mcf_1
mcf_2 = (soil_spike_ratio*(moisture_percent_2/100) + 1)
mcf_2
mcf_3 = (soil_spike_ratio*(moisture_percent_3/100) + 1)
mcf_3

# apply moisture factor to each soil
dim(df_a)
df_a %>% select(Soil) %>% unique()

# this is a special case with no replicates
df_a_mcf_1 <- df_a %>% filter(Soil == "Webster_pH3.3") %>% filter(Titration_type %in% c("NaOH","HCl","No_Nitrate")) %>% mutate(NH4_mM = NH4_mM * mcf_1)
dim(df_a_mcf_1) #310
df_a_mcf_2 <- df_a %>% filter(Soil == "WarrenWoods1_pH5.23") %>%  filter(Titration_type %in% c("NaOH","HCl","No_Nitrate")) %>% mutate(NH4_mM = NH4_mM * mcf_1)
dim(df_a_mcf_2) #429
df_a_mcf_3 <- df_a %>% filter(Soil == "Crerar1_pH8.05") %>% filter(Titration_type %in% c("NaOH","HCl","No_Nitrate")) %>% mutate(NH4_mM = NH4_mM * mcf_1)
dim(df_a_mcf_3) #426


df_a_others_mcf <- df_a %>% filter(Sample_type %in% c("Nitrite_Blank", "Nitrate_Blank", "Ammonium_Blank")) 
dim(df_a_others_mcf) #197
df_a_mcf <- rbind(df_a_mcf_1, df_a_mcf_2, df_a_mcf_3, df_a_others_mcf)
dim(df_a_mcf) # 1046

# plot to see
ggplot(df_a_mcf, aes(x=Time_hours, y=NH4_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  # geom_errorbar(aes(ymin=NO3_mM - Std_NO3_mM, ymax=NO3_mM + Std_NO3_mM), width=.05)+
  scale_fill_brewer(palette='Set2') +
  ylab("NO3- (mM) \n") +
  xlab("\n Time (hours)") +
  # scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  ggtitle("No averaging with biological replicates \n") +
  mytheme_2d

# 2. Apply blank correction factor (drying effect during incubation)
# Blank reads
# Get this from nitrate, nitrite reads
df_nh4_blank <- df_a %>% filter(Sample_type == "Ammonium_Blank")
df_nh4_blank

# df_aero_blank$Nitrate_input <- as.numeric(as.character(df_aero_blank$Nitrate_input))
df_nh4_blank %<>% mutate(Correction_factor_NH4 = (Ammonium_input / NH4_mM)) 

# average the blanks by time point
cf_nh4 <- df_nh4_blank %>% select(Soil, Time_point, Correction_factor_NH4) %>% group_by(Soil, Time_point) %>% summarize(Correction_factor_NH4 = mean(Correction_factor_NH4)) %>% ungroup()

# left join and multiply the correction factor
# left join to samples
df_sample_mcf <- df_a_mcf %>% filter(!(Sample_type %in% c("Nitrite_Blank","Nitrate_Blank","Ammonium_Blank")))
dim(df_sample_mcf) #1165
df_sample_mcf$Sample_type %>% unique()

df_sample_bcf <- df_sample_mcf %>% left_join(cf_nh4, by = c("Soil"="Soil", "Time_point"="Time_point"))
dim(df_sample_bcf) # 849

df_sample_bcf <- df_sample_bcf %>% mutate(NH4_mM = NH4_mM * Correction_factor_NH4)
dim(df_sample_bcf) #849

# merge dataframe with blank just for convenience
df_a_blanks_bcf <- df_a_mcf %>% filter(Sample_type %in% c("Nitrite_Blank","Nitrate_Blank","Ammonium_Blank")) %>% left_join(cf_nh4, by = c("Soil"="Soil", "Time_point"="Time_point"))
dim(df_a_blanks_bcf) #288
dim(df_sample_bcf) # 1165

colnames(df_sample_bcf)
colnames(df_a_blanks_bcf)

df_a_bcf <- rbind(df_sample_bcf, df_a_blanks_bcf)
dim(df_a_bcf) # 1046 24

# write.xlsx(df_a_bcf, "df_a_bcf.xlsx")
```


## 3. Sanity check: moisture correction & blank correction factor 

Blank correction \
Use the Ammonia concentration of the blank and use the ratio. \
For example, multiply to Ammonia concentration x (2mM / changed [NO3]) \

```{r}
# without any correction
ggplot(df_a, aes(x=Time_hours, y=NH4_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  # geom_errorbar(aes(ymin=NH4_mM - Std_NH4_mM, ymax=NH4_mM + Std_NH4_mM), width=.05)+
  # scale_color_brewer(palette='Set2') +
  # scale_color_manual(values = c("deepskyblue4","maroon2"))+
  ylab("Measured NH4+ (mM) \n") +
  xlab("\n Time (hr)") +
  # scale_y_continuous(breaks = seq(0,5.1,1), limits=c(0, 5.1))+
  # scale_x_continuous(breaks = seq(0,5.1,1), limits=c(0, 5.1))+
  ggtitle("(Before moisture correction) All samples \n") +
  mytheme_2d +
  facet_grid(. ~ Soil) +
  theme(strip.background = element_rect(colour="black", fill="white", size=0.1))+
  theme(strip.text.x = element_text(size = 17))

# After moisture correction
ggplot(df_a_mcf, aes(x=Time_hours, y=NH4_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  # geom_errorbar(aes(ymin=NH4_mM - Std_NH4_mM, ymax=NH4_mM + Std_NH4_mM), width=.05)+
  # scale_color_brewer(palette='Set2') +
  # scale_color_manual(values = c("deepskyblue4","maroon2"))+
  ylab("Measured NH4+ (mM) \n") +
  xlab("\n Time (hr)") +
  # scale_y_continuous(breaks = seq(0,5.1,1), limits=c(0, 5.1))+
  # scale_x_continuous(breaks = seq(0,5.1,1), limits=c(0, 5.1))+
  ggtitle("(After moisture correction) All samples \n") +
  mytheme_2d +
  facet_grid(. ~ Soil) +
  theme(strip.background = element_rect(colour="black", fill="white", size=0.1))+
  theme(strip.text.x = element_text(size = 17))

# After blank correction (evaporation) 
ggplot(df_a_bcf, aes(x=Time_hours, y=NH4_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  # geom_errorbar(aes(ymin=NH4_mM - Std_NH4_mM, ymax=NH4_mM + Std_NH4_mM), width=.05)+
  # scale_color_brewer(palette='Set2') +
  # scale_color_manual(values = c("deepskyblue4","maroon2"))+
  ylab("Measured NH4+ (mM) \n") +
  xlab("\n Time (hr)") +
  # scale_y_continuous(breaks = seq(0,5.1,1), limits=c(0, 5.1))+
  # scale_x_continuous(breaks = seq(0,5.1,1), limits=c(0, 5.1))+
  ggtitle("(After moisture + blank correction) All samples \n") +
  mytheme_2d +
  facet_grid(. ~ Soil) +
  theme(strip.background = element_rect(colour="black", fill="white", size=0.1))+
  theme(strip.text.x = element_text(size = 17))


```


## 4. Nitrogen dynamics

## 4.1. pH perturbation experiment.
- Is there a difference in pH perturbation levels?
```{r}
# pH color
col_pH <- colorRampPalette(c("gold","red","purple"))

library(colorRamps)
colorRamps::green2red
plot(rep(1,13),col=col_pH(13),pch=19,cex=3)
grad_pH <- scale_colour_gradientn(colours = col_pH(100))

# Confer this page (https://stackoverflow.com/questions/21537782/how-to-set-fixed-continuous-colour-values-in-ggplot2)
# myPalette <- colorRampPalette(rev(brewer.pal(11, "Spectral")))
# sc <- scale_colour_gradientn(colours = myPalette(100), limits=c(1, 8))

# 1. pH perturbation
# plot Ammonia
df_a_pH <- df_a_bcf %>% filter(Titration_type %in% c("NaOH","HCl"))

dim(df_a_pH)
colnames(df_a_pH)

# average the no acid base one.
df_plot <- df_a_pH %>% select(H_mM, NH4_mM, Soil, Time_hours)
df_plot %>% filter(H_mM == 0) %>% dim()
df_plot %>% filter(H_mM == 0) %>% group_by(H_mM, Soil, Time_hours) %>% summarize(NH4_mM = mean(NH4_mM)) %>% ungroup()
df_sub <- df_plot %>% filter(H_mM == 0) %>% group_by(H_mM, Soil, Time_hours) %>% summarize(NH4_mM = mean(NH4_mM)) %>% ungroup()
df_main <- df_plot %>% filter(H_mM != 0)
dim(df_plot)
dim(df_main)
df_plot2 <- rbind(df_main, df_sub)

#export to plot with nitrate, nitrite
# write.xlsx(df_plot2, "220420-2_Ammonia_bcf.xlsx")

ggplot(df_plot2, aes(x=Time_hours, y=NH4_mM, color=H_mM, group=H_mM)) +
  geom_point(size=2.5, shape=16) +
  geom_line(size=1.2)+
  # geom_errorbar(aes(ymin=NH4_mM - Std_NH4_mM, ymax=NH4_mM + Std_NH4_mM), width=.05)+
  scale_colour_gradientn(colours = col_pH(100)) +
  # scale_color_manual(values=grad_pH) +
  ylab("NH4+ (mM) \n") +
  xlab("\n Time (hr)") +
  # scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  ggtitle("pH perturbation in 3 soils with different pH \n") +
  # label
  # geom_text(aes(label = round(NH4_mM,3)), size = 3, vjust = -1.5, face="bold", show.legend = FALSE)+
  mytheme_2d +
  facet_grid(. ~ Soil) +
  theme(strip.background = element_rect(colour="black", fill="white", size=0.1))+
  theme(strip.text.x = element_text(size = 17))


```

Ammonium and pH relationship
```{r}

df_web_T0 <- df_plot2 %>% filter(Soil == "Webster_pH3.3", Time_hours == 0)

ggplot(df_web_T0, aes(x=H_mM, y=NH4_mM, color=H_mM, group=H_mM)) +
  geom_point(size=2.5, shape=16) +
  geom_line(size=1.2)+
  # geom_errorbar(aes(ymin=NH4_mM - Std_NH4_mM, ymax=NH4_mM + Std_NH4_mM), width=.05)+
  scale_colour_gradientn(colours = col_pH(100)) +
  # scale_color_manual(values=grad_pH) +
  ylab("NH4+ (mM) \n") +
  xlab("\n H+ (mM)") +
  # scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  ggtitle("Ammonium concentration at T0 (Webster pH3.3) \n") +
  # label
  # geom_text(aes(label = round(NH4_mM,3)), size = 3, vjust = -1.5, face="bold", show.legend = FALSE)+
  mytheme_2d



```

Let's subtract T0 ammonium value in all time points.

```{r}
df_web <- df_plot2 %>% filter(Soil == "Webster_pH3.3")
df_web_T0 <- df_plot2 %>% filter(Soil == "Webster_pH3.3", Time_hours == 0)
df_web_T0 %<>% rename(T0_NH4_mM = NH4_mM) %<>% select(-Time_hours)

df_web_subtract_T0 <- df_web %>% left_join(df_web_T0, by = c("H_mM"="H_mM", "Soil"="Soil")) %>% mutate(NH4_mM = NH4_mM - T0_NH4_mM) %>% select(-T0_NH4_mM)

df_rest2 <- df_plot2 %>% filter(!(Soil == "Webster_pH3.3"))
df_merge2 <- rbind(df_rest2, df_web_subtract_T0)

ggplot(df_merge2, aes(x=Time_hours, y=NH4_mM, color=H_mM, group=H_mM)) +
  geom_point(size=2.5, shape=16) +
  geom_line(size=1.2)+
  # geom_errorbar(aes(ymin=NH4_mM - Std_NH4_mM, ymax=NH4_mM + Std_NH4_mM), width=.05)+
  scale_colour_gradientn(colours = col_pH(100)) +
  # scale_color_manual(values=grad_pH) +
  ylab("NH4+ (mM) \n") +
  xlab("\n Time (hr)") +
  # scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  ggtitle("pH perturbation in 3 soils with different pH \n") +
  # label
  # geom_text(aes(label = round(NH4_mM,3)), size = 3, vjust = -1.5, face="bold", show.legend = FALSE)+
  mytheme_2d +
  facet_grid(. ~ Soil) +
  theme(strip.background = element_rect(colour="black", fill="white", size=0.1))+
  theme(strip.text.x = element_text(size = 17))


```




## 5. Ammonia mu space

## 5.1. Ammonia area under curve
```{r}

## area under curve
df_plot2$Time_hours
require(pracma)
colnames(df_plot2)
am_corr <- df_plot2 %>% select(H_mM, Time_hours, NH4_mM) %>% group_by(H_mM) %>% summarize(auc = trapz(Time_hours, NH4_mM)) %>% ungroup()

plot(am_corr$H_mM, am_corr$auc)

am_corr$H_mM_2 <- (am_corr$H_mM)^2
fit.amm <- lm(auc ~ H_mM + H_mM_2, am_corr)
summary(fit.amm)

perturbH <- seq(-100, 100, 0.1)
am_aucPredict <- predict(fit.amm,list(H_mM=perturbH, H_mM_2=perturbH^2))
am_auc_quad <- data.frame(H_mM = perturbH, Time_hours = am_aucPredict)
plot(perturbH, am_aucPredict)

# (1) Plot fitted linear regression line
ggplot(am_corr, aes(x=H_mM, y=auc)) +
  geom_point(size=2.5, shape=16, color = "brown") +
  stat_smooth(method = "loess", size = 1) +
  # geom_errorbar(aes(ymin=NO3_mM - sd_NO3_mM, ymax=NO3_mM + sd_NO3_mM), width=.05)+
  # scale_color_brewer(palette='Set2') +
  # scale_color_manual(values = c("maroon2","deepskyblue4"))+
  xlab("Amount of pH perturbation (H+ mM) \n") +
  ylab("\n Area under curve (NH4+)") +
  # scale_x_continuous(breaks = seq(0,16,1), limits=c(0, 16))+
  #scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  # geom_text_repel(aes(label = round(NO3_mM,3)), size = 3,face="bold", show.legend = FALSE)+
  ggtitle("Correlation with perturbation and area under ammonia curve \n") +
  # geom_abline(slope = 1, intercept=0, show.legend = "y=x")+
  # regression line
  # geom_line(data = am_auc_quad, aes(x = H_mM, y = Time_hours), color = "maroon2", size = 1) +
  # show equation
  # annotate("text",x=0,y=100, label= paste0("y = ", round(coef(fit.amm)[[1]],3), "+", round(coef(fit.amm)[[2]],3),"x+",round(coef(fit.amm)[[3]],3), "x^2", ",  R^2: ", round(summary(fit.amm)$r.squared,3)), color = "maroon2") +
  mytheme_2d


```

## 5.2. Ammonia average slope

```{r}
mat_NH4 <- dcast(df_plot2, H_mM ~ Time_hours, value.var = "NH4_mM")
mat_NH4 <- tibble::column_to_rownames(mat_NH4, var = "H_mM")
mat_NH4 <- as.matrix(mat_NH4) 
class(mat_NH4)
dim(mat_NH4)

mat_NH4[is.na(mat_NH4)] 
for (i in 1:dim(mat_NH4)[1]){
  # print(i)
  for (j in 1:dim(mat_NH4)[2]){
    # print(j)
    if (is.na(mat_NH4[i,j])){
      mat_NH4[i,j] <- (mat_NH4[i,j-1] + mat_NH4[i,j+1] ) / 2
    }
  }
}
mat_NH4[is.na(mat_NH4)] # no more NA

## Max
vec_H_mM <- rownames(mat_NH4)
vec_max_NH4 <- rep(-1, dim(mat_NH4)[1])
vec_max_time <- rep(-1, dim(mat_NH4)[1])

for (i in 1:dim(mat_NH4)[1]){
  x = colnames(mat_NH4)
  y = mat_NH4[i,]
  max_j = y[dim(mat_NH4)[2]]
  # save
  vec_max_NH4[i] <- max_j
  vec_max_time[i] <- x[dim(mat_NH4)[2]]
  iter_j <- dim(mat_NH4)[2] -1
  # get the more early points if the difference with max is not big (10%)
  for (k in 1:iter_j){
    print(k)
    if ( (y[dim(mat_NH4)[2]-k] > max_j) || (abs(max_j - y[dim(mat_NH4)[2]-k])/max_j < 0.1) ){
      max_j = y[dim(mat_NH4)[2] - k]
      print(max_j)
      vec_max_NH4[i] <- max_j
      print(names(max_j))
      vec_max_time[i] <- names(max_j)
    } else{ break }
  }
}

am_ave_slope <- data.frame(H_mM = vec_H_mM, NH4_mM = vec_max_NH4, Time_hours = vec_max_time)

# check
i = 36
plot(colnames(mat_NH4), mat_NH4[i,])
points(vec_max_time[i], vec_max_NO_mM[i], col='red')

for (i in 1:dim(mat_NH4)[1]){
  plot(colnames(mat_NH4), mat_NH4[i,])
  points(vec_max_time[i], vec_max_NO_mM[i], col='red')
}

# get average slope
am_ave_slope$H_mM <- as.numeric(am_ave_slope$H_mM)
am_ave_slope$average_slope <- am_ave_slope$NH4_mM / as.numeric(am_ave_slope$Time_hours)

# plot
plot(vec_H_mM, am_ave_slope$average_slope)

# quadratic fit
am_ave_slope$H_mM_2 <- (am_ave_slope$H_mM)^2
fit.aveslope <- lm(average_slope ~ H_mM + H_mM_2, am_ave_slope)
summary(fit.aveslope)

perturbH <- seq(-100, 100, 0.1)
aveslopePredict <- predict(fit.aveslope, list(H_mM=perturbH, H_mM_2=perturbH^2))
df_avs_quad <- data.frame(H_mM = perturbH, average_slope = aveslopePredict)
plot(perturbH, aveslopePredict)

# (1) Plot fitted quadratic regression line
ggplot(am_ave_slope, aes(x=H_mM, y=average_slope)) +
  geom_point(size=2.5, shape=16, color = "brown") +
  stat_smooth(method = "loess", size = 1) +
  # geom_errorbar(aes(ymin=NO3_mM - sd_NO3_mM, ymax=NO3_mM + sd_NO3_mM), width=.05)+
  # scale_color_brewer(palette='Set2') +
  # scale_color_manual(values = c("maroon2","deepskyblue4"))+
  xlab("Amount of pH perturbation (H+ mM) \n") +
  ylab("\n Average slope of Ammonia curve (NH4_mM/Time_hours)") +
  # scale_x_continuous(breaks = seq(0,16,1), limits=c(0, 16))+
  #scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  # geom_text_repel(aes(label = round(NO3_mM,3)), size = 3,face="bold", show.legend = FALSE)+
  ggtitle("Correlation with perturbation and average slope of Ammonia curve \n") +
  # geom_abline(slope = 1, intercept=0, show.legend = "y=x")+
  # regression line
  # geom_line(data = df_avs_quad, aes(x = H_mM, y = average_slope), color = "maroon2", size = 1) +
  # show equation
  # annotate("text",x=0,y=0,label= paste0("y = ", round(coef(fit.aveslope)[[1]],3), "+", round(coef(fit.aveslope)[[2]],3),"x+",round(coef(fit.aveslope)[[3]],3), "x^2", ",  R^2: ", round(summary(fit.aveslope)$r.squared,3)), color = "maroon2") +
  mytheme_2d
```

## 5.3. Subtracting Ir = Amm_produce + N2O_produce
```{r}
# N2O_produce = Amm_produce - Ir

mat_denit <- mat_Ir - mat_NH4

df_denit <- melt(mat_denit) 
names(df_denit) <- c("H_mM","Time_hours","NH4_mM")

# plot I r = reduced Nitrite (accumulative)
ggplot(df_denit, aes(x=Time_hours, y=NH4_mM, color=H_mM, group=H_mM)) +
  geom_point(size=2.5, shape=16) +
  geom_line(size=1.5)+
  # geom_errorbar(aes(ymin=NH4_mM - Std_NH4_mM, ymax=NH4_mM + Std_NH4_mM), width=.05)+
  scale_colour_gradientn(colours = col_pH(100)) +
  # scale_color_manual(values=col_pH(4)) +
  ylab("NO2- used in denitrification (mM) \n") +
  xlab("\n Time (hr)") +
  # scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  ggtitle("I_denit (Nitrite reduced to NO) = I_r - Amm_produced \n") +
  # label
  # geom_text(aes(label = round(NH4_mM,3)), size = 3, vjust = -1.5, face="bold", show.legend = FALSE)+
  mytheme_2d +
  theme(strip.background = element_rect(colour="black", fill="white", size=0.1))





```



