---
title: "220521_pH_antibiotics_dose_effect"
author: "KiseokUchicago"
date: "2022-05-23"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

```{r global_options, include=FALSE}
library(knitr)
knitr::opts_chunk$set(fig.width=11, fig.height=9,
                      error=TRUE, echo=TRUE, eval=TRUE, warning=FALSE, message=FALSE,
                      tidy.opts=list(width.cutoff=40),tidy=TRUE)
```

## Time series analysis - pH analysis of antibiotic dosage effect 
Researcher: **Kiseok Lee** \
Experiment Date: 5/8/22 - 5/12/22 (5 days) \
Analysis Date: 5/23/21
Lab: **Seppe Kuehn**

```{r, include=FALSE}
# libraries
library(dplyr)
library(ggplot2)
library(RColorBrewer)
library(vegan)
library(tidyverse)
library(magrittr)
library(readxl)
library(reshape2)
library(gtools)
library(devtools)
library(openxlsx)
library(ape)
library(stringr)
library(tidyr)
library(ggrepel)
library(ggpubr)
require(gridExtra)
# grid.arrange(p_strain, p_ai, nrow=1)

# color collection
my_color_collection <- c(
  "#CBD588", "#5F7FC7", "orange", "#AD6F3B", "#673770", 
  "#D14285", "#652926", "#C84248", "#8569D5", "#5E738F",
  "#D1A33D", "#8A7C64", "#599861","#616163", "#FFCDB2",
  "#6D9F71", "#242F40",
  "#CCA43B", "#F92A82", "#ED7B84", "#7EB77F", 
  "#DEC4A1", "#E5D1D0", '#0E8482', '#C9DAEA', '#337357', 
  '#95C623', '#E55812', '#04471C', '#F2D7EE', '#D3BCC0', 
  '#A5668B', '#69306D', '#0E103D', '#1A535C', '#4ECDC4', 
  '#F7FFF7', '#FF6B6B', '#FFE66D', '#6699CC', '#FFF275', 
  '#FF8C42', '#FF3C38', '#A23E48', '#000000', '#CF5C36', 
  '#EEE5E9', '#7C7C7C', '#EFC88B', '#2E5266', '#6E8898', 
  '#9FB1BC', '#D3D0CB', '#E2C044', '#5BC0EB', '#FDE74C', 
  '#9BC53D', '#E55934', '#FA7921', "#CD9BCD", "#508578", "#DA5724")

# for git push, use this instead of using wflow_git_push()
# git push -u origin master (in the Git app / in the working directory)

# for making pdf file
library(rmarkdown)
# render("analysis/~~.Rmd", "pdf_document")
```


```{r, echo=F}
## theme for ggplot
mytheme <- theme_bw() + 
  theme(text = element_text(face="bold", colour = 'black')) +
  theme(plot.title = element_text(size = 19,hjust = 0.5,face="bold", colour = 'black')) + 
  theme(axis.title.x = element_text(size = 17,hjust = 0.5,face="bold", colour = 'black')) + 
  theme(axis.title.y = element_text(size = 17,hjust = 0.5,face="bold", colour = 'black')) + 
  theme(axis.text.x = element_text(hjust = 0.5, vjust=0.3,size=13,face="bold", colour = 'black'))+
  theme(axis.text.y = element_text(size=13,face="bold", colour = 'black'))+
  theme(panel.grid.major = element_blank()) +
  theme(panel.grid.minor = element_blank(),panel.background=element_blank(),panel.border=element_blank(),plot.background=element_blank()) +
  theme(axis.ticks = element_line(size = 1.1))+
  theme(legend.text=element_text(size=10,face="bold", colour = 'black'))


mytheme_2d <- theme_bw() + 
  theme(text = element_text(face="bold", colour = 'black')) +
  theme(plot.title = element_text(size = 19,hjust = 0.5,face="bold", colour = 'black')) + 
  theme(axis.title.x = element_text(size = 17,hjust = 0.5,face="bold", colour = 'black')) + 
  theme(axis.title.y = element_text(size = 17,hjust = 0.5,face="bold", colour = 'black')) + 
  theme(axis.text.x = element_text(hjust = 0.5, vjust=0.3,size=13,face="bold", colour = 'black'))+
  theme(axis.text.y = element_text(size=13,face="bold", colour = 'black'))+
  # theme(panel.grid.major = element_blank()) +
  # theme(panel.grid.minor = element_blank(),panel.background=element_blank(),plot.background=element_blank()) +
  theme(axis.ticks = element_line(size = 1.1))+
  theme(legend.text=element_text(size=10,face="bold", colour = 'black'))
```


## 1. 20ul of 0.5M HCl or 0.05M NaOH was incrementally added
```{r}
df_pH1 <- openxlsx::read.xlsx("data/220521_pH_colorimetric_Barneveld2_Sterile_T0_mu_opt_T0.xlsx")
df_pH2 <- openxlsx::read.xlsx("data/220521_pH_colorimetric_Barneveld2_Sterile_T7_mu_opt_T0.xlsx") 
df_pH3 <- openxlsx::read.xlsx("data/220521_pH_colorimetric_Barneveld2_Sterile_T10_mu_opt_T0.xlsx") 


# I incorporated pH meter into pH1 and pH3... so... I'll put pH_meter column for other df.
df_pH2$pH_meter <- NA
df_pH3$pH_meter <- NA
colnames(df_pH1)
colnames(df_pH2)
colnames(df_pH3)


# Filter defect
# I ruined T10....
df_pH1 %<>% filter(!(Well %in% c("C01", "C10", "C11", "D01", "D11", "E10","F01","F11" ))) # less than 120ul
df_pH2 %<>% filter(!(Well %in% c("A01", "A03", "B02", "B05", "C08", "D04", "D12", "E06", "E07", "E12", "G12", "H02", "H04", "H05", "H07", "H09", "H10", "H11"))) # little sample
df_pH3 %<>% filter(!(Well %in% c("A02", "A04", "A05", "B02", "B04", "C04", "D03", "D04", "E01", "E05", "E07", "E09", "E12", "F05",
                                 "G09", "G10", "G11", "G12", "H03", "H04", "H05", "H06", "H09" ))) # little sample
# df_pH4 %<>% filter(!(Well %in% c("H02","H05","F03"))) # Less than 90ul of sample
dim(df_pH1)
dim(df_pH2)
dim(df_pH3)

df_time <- openxlsx::read.xlsx("data/220519_time_table.xlsx")
df_time$Time_hours <- round(df_time$Time_hours, 1)
df_time$Time_days <- round(df_time$Time_days, 2)

df_pH_T <- rbind(df_pH1, df_pH2, df_pH3)
df_pH_T %<>% left_join(df_time, by=c("Time_point"="Time_point"))
dim(df_pH_T) # 575

# remove NA # don't remove NA this time
# dim(df_pH_T) # 575
# df_pH_T[is.na(df_pH_T)]
# df_na <- df_pH_T[rowSums(is.na(df_pH_T)) > 0,]
# # df_pH_T <- na.omit(df_pH_T)
# df_pH_T <- df_pH_T[rowSums(is.na(df_pH_T)) == 0,]
# dim(df_pH_T) # 373

# Change the soil names to include pH
# df_pH_T$Soil <- str_replace(df_pH_T$Soil,"NicholsC","NicholsC_pH7")
# df_pH_T$Soil <- str_replace(df_pH_T$Soil,"Allandale","Allandale_pH4")
# df_pH_T$Soil <-  factor(df_pH_T$Soil, levels = c("NicholsC_pH7", "Allandale_pH4"))

# mols and molarity unit conversion
# test
df_pH <- df_pH_T %>% filter(Titration_type %in% c("NaOH","HCl","No_Nitrate"))
dim(df_pH) # 304
df_pH$Titration_type %>% unique()

Added_Volume <- 1.7 # ml
Soil_mg <- 0.85
moisture_percent_1 = 20.15 # Barneveld2 for antibiotics
Added_Volume + Soil_mg*(moisture_percent_1/100)
# moisture_percent_2 = 8.12 # Sterile - LaBaghWoods that has been autoclaved 5 times.
# Added_Volume + Soil_mg*(moisture_percent_2/100)
# moisture_percent_3 = 9.0 # Crerar7
# Added_Volume + Soil_mg*(moisture_percent_3/100)

df_pH$Added_ul <- ifelse(df_pH$Titration_type == "NaOH", -1*df_pH$Added_ul, df_pH$Added_ul) # HCl is +, NaOH is -
df_pH %<>% mutate(H_mol = Concentration_M * Added_ul * 10^(-6)) # Calculate H mol 
df_pH$Volume <- ifelse(df_pH$Soil == "Barneveld2", Added_Volume + Soil_mg*(moisture_percent_1/100),
                      ifelse(df_pH$Soil == "LaBaghWoods_autoclaved_pH6.66", Added_Volume + Soil_mg*(moisture_percent_2/100),
                             0))
                             # ifelse(df_pH$Soil == "Crerar1_pH8.05", Added_Volume + Soil_mg*(moisture_percent_3/100),
                                    # 0))) # Calc total volume

df_pH %<>% mutate(H_Molarity = H_mol / (Volume * 10^(-3)))
df_pH %<>% mutate(H_mM = H_Molarity * 1000)
# openxlsx::write.xlsx(df_pH, "df_pH.xlsx")

# how many levels of H_mM?
df_pH %>% filter(Soil == "Barneveld2")%>% select(H_mM) %>% unique() %>% arrange(H_mM)
# df_pH %>% filter(Soil == "LaBaghWoods_autoclaved_pH6.66")%>% select(H_mM) %>% unique() %>% arrange(H_mM)
# df_pH %>% filter(Soil == "Crerar1_pH8.05")%>% select(H_mM) %>% unique() %>% arrange()
colnames(df_pH)
dim(df_pH)



# average the pH
# 220329 only used 1 replicate. So, no need to average.
# df_pH_ave <- df_pH %>% group_by(Nitrite_input, Nitrate_input, Soil, Titration_type, Concentration_M, Added_ul, Sample_type, H_mol, H_Molarity, H_mM, Time_point, Time_minutes, Time_hours, Time_days) %>% summarise(Ave_pH = mean(pH_colorimetric), Std_pH = sd(pH_colorimetric)) %>% ungroup()

# colnames(df_pH_ave)

```

Export pH for ammonium analysis
```{r}
# where is autoclaved?
# df_pH %>% filter(Soil == "LaBaghWoods_autoclaved_pH6.66")

# remove blanks
df_pH_export <- df_pH %>% filter(Titration_type %in% c("NaOH", "HCl"))

# use only T7
df_pH_export %<>% rename(pH = pH_colorimetric) %>% arrange(H_mM, Soil, Titration_type, Antibiotics_type, Dose_ppm)

# average the replicates
df_pH_export2 <- df_pH_export %>% group_by(Soil, Titration_type, Unit, H_mM, Antibiotics_type, Dose_ppm, Time_point) %>% summarise(pH = mean(pH)) %>% ungroup() %>% arrange(Antibiotics_type, Dose_ppm, H_mM)
df_pH_export2$pH <- as.numeric(df_pH_export2$pH)

ggplot(df_pH_export2, aes(x=H_mM, y=pH, color=Antibiotics_type, group=Antibiotics_type)) +
  geom_point(size=3, shape=16, alpha=1) +
  # geom_errorbar(aes(ymin=Ave_pH - Std_pH, ymax=Ave_pH + Std_pH), width=.05)+
  geom_line(size=1)+
  # scale_color_brewer(palette='Set1') +
  ylab("pH \n") +
  xlab("\n added [H+] mM") +
  scale_x_continuous(breaks = seq(-100,100,5))+
  scale_y_continuous(breaks = seq(0,14,1), limits=c(0, 14))+
  ggtitle("Soil pH perturbation & titration curves (LaBaghWoods1(pH6.66)) \n") +
  # label
  # geom_text(aes(label = pH_colorimetric), size = 3, vjust = -1.5, family="serif", show.legend  = FALSE)+
  mytheme_2d+
  facet_grid(Dose_ppm ~ Antibiotics_type) +
  theme(strip.background = element_rect(colour="black", fill="white", size=0.1))+
  theme(strip.text.x = element_text(size = 17))

write.xlsx(df_pH_export2, "220521_pH_Antibiotics_dose_effect_experiment.xlsx")

```



To Kyle

```{r, echo=FALSE}
# Let's export pH levels for Kyle (220426)
dim(df_pH)
# removing timepoint T8
df_pH_kyle <- df_pH %>% filter(Soil == "LaBaghWoods_pH6.66")
df_pH_kyle$Time_point %>% unique()
df_pH_kyle2 <- df_pH_kyle %>% filter(Titration_type %in% c("NaOH", "HCl")) 
# only look at T7
df_pH_kyle2 %<>% filter(Time_point == "LBA_T7") %>% rename(pH = pH_colorimetric) %>% arrange(H_mM, Antibiotics_type)
dim(df_pH_kyle2) # 33
df_pH_kyle2 %>% arrange(H_mM, Antibiotics_type)

# average the replicates
df_pH_kyle3 <- df_pH_kyle2 %>% group_by(Titration_type, Unit, Antibiotics_type) %>% summarise(pH = mean(pH)) %>% ungroup()
df_pH_kyle3$pH <- as.numeric(df_pH_kyle3$pH)

ggplot(df_pH_kyle3, aes(x=H_mM, y=pH, color=Antibiotics_type, group=Antibiotics_type)) +
  geom_point(size=3, shape=16, alpha=1) +
  # geom_errorbar(aes(ymin=Ave_pH - Std_pH, ymax=Ave_pH + Std_pH), width=.05)+
  geom_line(size=1)+
  # scale_color_brewer(palette='Set1') +
  ylab("pH \n") +
  xlab("\n added [H+] mM") +
  scale_x_continuous(breaks = seq(-100,100,5))+
  scale_y_continuous(breaks = seq(0,14,1), limits=c(0, 14))+
  ggtitle("Soil pH perturbation & titration curves (LaBaghWoods1(pH6.66)) \n") +
  # label
  # geom_text(aes(label = pH_colorimetric), size = 3, vjust = -1.5, family="serif", show.legend  = FALSE)+
  mytheme_2d

# add NaOH Unit 6 
df_pH_kyle3 %>% filter(Unit == 6, Titration_type == "NaOH")
pH_mean = mean(df_pH_kyle3 %>% filter(Unit == 6, Titration_type == "NaOH") %>% select(pH) %>% unlist())
df_pH_kyle3 <- rbind(df_pH_kyle3, c("NaOH", as.numeric(6), "CHL", as.numeric(pH_mean)))
df_pH_kyle3$pH <- as.numeric(df_pH_kyle3$pH)
df_pH_kyle3$pH <- round(df_pH_kyle3$pH, 3)
# df_kyle2 is from 
df_kyle2 <- read.xlsx("data/220421_Griess_antibiotics_experiment_to_kyle_remove_blanks.xlsx")

# incompatible?
df_pH_kyle3$Unit <- as.numeric(df_pH_kyle3$Unit)
df_kyle2$Unit

df_kyle3 <- df_kyle2 %>% left_join(df_pH_kyle3, by=c("Titration_type"="Titration_type", "Unit"="Unit","Antibiotics_type"="Antibiotics_type"))

write.xlsx(df_kyle3, "220421_Griess_antibiotics_experiment_to_kyle_remove_blanks_add_pH.xlsx")

```


## 2. Plot titration curves
Plot one time point at the time
```{r}
df_time
# df_T0 <- df_pH_ave %>% filter(Time_point == "T0")

# Plot it in one plot - time series
df_plot <- df_pH
dim(df_plot)
# df_plot$Time_days <- factor(df_plot$Time_days)
df_plot$Time_point <- factor(df_plot$Time_point, levels = paste0("T", 0:10))
# unique(df_pH$Time_point)
colnames(df_plot)
df_plot$Time_point

ggplot(df_plot, aes(x=H_mM, y=pH_colorimetric, color=Time_point, group=Time_point)) +
  geom_point(size=3, shape=16, alpha=1) +
  # geom_errorbar(aes(ymin=Ave_pH - Std_pH, ymax=Ave_pH + Std_pH), width=.05)+
  geom_line(size=1)+
  # scale_color_brewer(palette='Set1') +
  ylab("pH \n") +
  xlab("\n added [H+] mM") +
  scale_x_continuous(breaks = seq(-100,100,5))+
  scale_y_continuous(breaks = seq(0,14,1), limits=c(0, 14))+
  ggtitle("Soil pH perturbation & titration curves (LaBaghWoods1(pH6.66)) \n") +
  # label
  # geom_text(aes(label = pH_colorimetric), size = 3, vjust = -1.5, family="serif", show.legend  = FALSE)+
  mytheme_2d

# pH meter
ggplot(df_plot, aes(x=H_mM, y=pH_meter, color=Time_point, group=Time_point)) +
  geom_point(size=3, shape=16, alpha=1) +
  # geom_errorbar(aes(ymin=Ave_pH - Std_pH, ymax=Ave_pH + Std_pH), width=.05)+
  geom_line(size=1)+
  # scale_color_brewer(palette='Set1') +
  ylab("pH \n") +
  xlab("\n added [H+] mM") +
  scale_x_continuous(breaks = seq(-100,100,5))+
  scale_y_continuous(breaks = seq(0,14,1), limits=c(0, 14))+
  ggtitle("[pH micrometer] Soil pH perturbation & titration curves (LaBaghWoods1(pH6.66)) \n") +
  # label
  # geom_text(aes(label = pH_colorimetric), size = 3, vjust = -1.5, family="serif", show.legend  = FALSE)+
  mytheme_2d

# order factors
df_plot$Dose_ppm <- ifelse(df_plot$Dose_ppm == 2500, 5000, df_plot$Dose_ppm)
df_plot$Dose_ppm <- ifelse(df_plot$Dose_ppm == 5000, "2500 or 5000", df_plot$Dose_ppm)
df_plot$Dose_ppm <- factor(df_plot$Dose_ppm, levels = c(200, 1000, "2500 or 5000"))
df_plot$Antibiotics_type <- factor(df_plot$Antibiotics_type, levels = c("CHL", "KAN", "STM","NYT","CHX","STM_CHX"))
df_plot %<>% filter(Dose_ppm != 0)


# average
df_plot2 <- df_plot %>% group_by(Titration_type, Unit, Antibiotics_type, Dose_ppm, H_mM, Time_point, Time_hours, Time_days) %>% summarise(pH_colorimetric = mean(pH_colorimetric), pH_meter = mean(pH_meter)) %>% ungroup()
dim(df_plot2)

df_plot2$Time_hours <- factor(df_plot2$Time_hours)

# one plot
ggplot(df_plot2, aes(x=H_mM, y=pH_colorimetric, color=Time_hours)) +
  geom_line(size=1)+
  geom_point(size=3, alpha=1) +
  # geom_errorbar(aes(ymin=Ave_pH - Std_pH, ymax=Ave_pH + Std_pH), width=.05)+
  
  # scale_color_brewer(palette='Set1') +
  ylab("pH") +
  xlab("added [H+] mM") +
  scale_x_continuous(breaks = seq(-100,100,10))+
  scale_y_continuous(breaks = seq(0,14,2), limits=c(0, 14))+
  ggtitle("[Barneveld2 (pH 6.9)] Antibiotic dose effect (ppm)") +
  # label
  # geom_text(aes(label = pH_colorimetric), size = 3, vjust = -1.5, family="serif", show.legend  = FALSE)+
  mytheme_2d +
  facet_grid(Dose_ppm ~ Antibiotics_type) +
  theme(strip.background = element_rect(colour="black", fill="white", size=0.1))+
  theme(strip.text.x = element_text(size = 13)) +
  theme(strip.text.y = element_text(size = 13, face="bold"))



# comparing by timepoint
ggplot(df_plot2, aes(x=H_mM, y=pH_colorimetric, color=Antibiotics_type)) +
  geom_line(size=1)+
  geom_point(aes(shape = Antibiotics_type),size=3, alpha=1) +
  # geom_errorbar(aes(ymin=Ave_pH - Std_pH, ymax=Ave_pH + Std_pH), width=.05)+
  
  # scale_color_brewer(palette='Set1') +
  ylab("pH") +
  xlab("added [H+] mM") +
  scale_x_continuous(breaks = seq(-100,100,10))+
  scale_y_continuous(breaks = seq(2,12,2), limits=c(2, 12))+
  ggtitle("Dose (ppm)") +
  # label
  # geom_text(aes(label = pH_colorimetric), size = 3, vjust = -1.5, family="serif", show.legend  = FALSE)+
  mytheme_2d+
  facet_grid(Time_hours ~ Dose_ppm) +
  theme(strip.background = element_rect(colour="black", fill="white", size=0.1))




```


Now it's time to compare colorimeteric vs. pH micrometer measurements
```{r}
# melt pH_colorimetric and pH_meter
df_plot3 <- df_plot2 %>% filter(Time_point == "T0")
df_T0 <- melt(df_plot3, measure.vars = c("pH_colorimetric", "pH_meter"), variable.name = "pH_method", value.name = "pH")

# comparing LBA samples
ggplot(df_T0, aes(x=H_mM, y=pH, color=pH_method)) +
  geom_line(size=1)+
  geom_point(aes(shape = Antibiotics_type),size=3, alpha=1) +
  # geom_errorbar(aes(ymin=Ave_pH - Std_pH, ymax=Ave_pH + Std_pH), width=.05)+
  
  # scale_color_brewer(palette='Set1') +
  ylab("pH") +
  xlab("added [H+] mM") +
  scale_x_continuous(breaks = seq(-100,100,10))+
  scale_y_continuous(breaks = seq(2,10,2), limits=c(2, 10))+
  ggtitle("[Barneveld2 pH 6.9] Comparing pH measuring methods \n") +
  # label
  # geom_text(aes(label = pH_colorimetric), size = 3, vjust = -1.5, family="serif", show.legend  = FALSE)+
  mytheme_2d+
  facet_grid(Dose_ppm ~ Antibiotics_type) +
  theme(strip.background = element_rect(colour="black", fill="white", size=0.1))+
  theme(strip.text.x = element_text(size = 13)) +
  theme(strip.text.y = element_text(size = 13, face="bold"))

# plot scatter plot
ggplot(df_plot3, aes(x=pH_colorimetric, y=pH_meter)) +
  # geom_line(size=1)+
  geom_point(size=3, alpha=1, color="royalblue") +
  # geom_errorbar(aes(ymin=Ave_pH - Std_pH, ymax=Ave_pH + Std_pH), width=.05)+
  geom_abline(intercept=0, slope=1)+
  scale_color_brewer(palette='Set1') +
  ylab("pH by micro electrode \n") +
  xlab("\n pH by colorimetric assay") +
  scale_x_continuous(breaks = seq(2,10,1), limits=c(2, 10))+
  scale_y_continuous(breaks = seq(2,10,1), limits=c(2, 10))+
  ggtitle("Comparing pH measuring methods \n") +
  # label
  # geom_text(aes(label = pH_colorimetric), size = 3, vjust = -1.5, family="serif", show.legend  = FALSE)+
  mytheme_2d


```

## Is pH change due to biotic activity?
```{r}
# compare only with varying dose level
df_plot <- df_pH
df_plot %<>% group_by(Titration_type, Unit, Antibiotics_type, Dose_ppm, H_mM, Time_point, Time_hours, Time_days) %>% summarise(pH_colorimetric = mean(pH_colorimetric), pH_meter = mean(pH_meter)) %>% ungroup()
df_plot$Dose_ppm <- ifelse(df_plot$Dose_ppm == 2500, 5000, df_plot$Dose_ppm)
df_plot$Dose_ppm <- ifelse(df_plot$Dose_ppm == 5000, "2500 or 5000", df_plot$Dose_ppm)
df_plot$Dose_ppm <- factor(df_plot$Dose_ppm, levels = c(0, 200, 1000, "2500 or 5000"))
df_plot$Antibiotics_type <- factor(df_plot$Antibiotics_type, levels = c("CHL", "KAN", "STM","NYT","CHX","STM_CHX"))

df_dose <- df_plot %>% filter(H_mM == 0, Dose_ppm != 0)
df_nodose <- df_plot %>% filter(Dose_ppm == 0)
df_nodose_CHL <- df_nodose %>% mutate(Antibiotics_type = "CHL")
df_nodose_KAN <- df_nodose %>% mutate(Antibiotics_type = "KAN")
df_nodose_STM <- df_nodose %>% mutate(Antibiotics_type = "STM")
df_nodose_NYT <- df_nodose %>% mutate(Antibiotics_type = "NYT")
df_nodose_CHX <- df_nodose %>% mutate(Antibiotics_type = "CHX")
df_nodose_STM_CHX <- df_nodose %>% mutate(Antibiotics_type = "STM_CHX")

df_dose <- rbind(df_dose, df_nodose_CHL, df_nodose_KAN, df_nodose_STM, df_nodose_NYT, df_nodose_CHX, df_nodose_STM_CHX)
df_dose$Dose_ppm

df_dose$Dose_ppm <- factor(df_dose$Dose_ppm)
df_dose$Antibiotics_type <- factor(df_dose$Antibiotics_type, levels = c("CHL", "KAN", "STM","NYT","CHX","STM_CHX"))

ggplot(df_dose, aes(x=Time_hours, y=pH_colorimetric, color=Dose_ppm, group=Dose_ppm)) +
  geom_point(size=2.5, shape=16) +
  geom_line(size=1.2)+
  # geom_errorbar(aes(ymin=NO3_mM - Std_NO3_mM, ymax=NO3_mM + Std_NO3_mM), width=.05)+
  # scale_colour_gradientn(colours = rev(col_pH(100))) +
  # scale_color_manual(values=grad_pH) +
  ylab("pH") +
  xlab("Time (hr)") +
  # scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  # label
  # geom_text(aes(label = round(NO3_mM,3)), size = 3, vjust = -1.5, family="serif", show.legend = FALSE)+
  mytheme_2d +
  ggtitle("pH change and biotic activity") +
  facet_wrap(. ~ Antibiotics_type, nrow=2) +
  theme(strip.background = element_rect(colour="black", fill="white", size=0.1))+
  theme(strip.text.x = element_text(size = 13))
  # theme(strip.text.y = element_text(size = 13, face="bold"))






```













## 2.1. plot OD434 and OD585
```{r}
df_OD <- read.xlsx("data/OD434_OD585_WW_C_T0_220329.xlsx")
colnames(df_OD)[1] <- "Well"

df_OD_merged <- df_OD %>% left_join(df_plot %>% filter(Time_point %in% c("WW_T0", "C_T0")), by=c("Well"="Well"))

df_OD_C <- df_OD_merged %>% filter(Soil == "Crerar7_pH8.05")

# plot OD434 and its change
ggplot(df_OD_C, aes(x=H_mM, y=OD434, color=Time_days, group=Time_days)) +
  geom_point(size=3, shape=16, alpha=1) +
  # geom_errorbar(aes(ymin=Ave_pH - Std_pH, ymax=Ave_pH + Std_pH), width=.05)+
  geom_line(size=1)+
  geom_vline(xintercept=0, linetype="dashed", color = "black")+
  # scale_color_brewer(palette='Set1') +
  ylab("pH \n") +
  xlab("\n added [H+] mM") +
  # scale_x_continuous(breaks = seq(-100,100,5), limits=c(-100, 100))+
  # scale_y_continuous(breaks = seq(0,14,1), limits=c(0, 14))+
  ggtitle("Soil pH perturbation & titration curves (Crerar7_pH8.05) \n") +
  # label
  # geom_text(aes(label = pH_colorimetric), size = 3, vjust = -1.5, family="serif", show.legend  = FALSE)+
  mytheme_2d

# use this instead: OD434
plot(df_OD_C$H_mM, df_OD_C$OD434_background, col = "orange", lty = 1, pch = 17, lwd = 1, main = "OD434 (Crerar7_T0 soil)",
     ylab = "OD434", xlab = "added [H+] mM", ylim = c(-1, 3), cex=2)

points(df_OD_C$H_mM, df_OD_C$OD434, col = "blue", pch = 17, cex=2)
points(df_OD_C$H_mM, df_OD_C$OD434_subtraction, col = 'red', pch = 17, lwd = 1)

legend("topright",legend = c("Background", "After dye", "(After dye - Background)"),
    col = c("orange", "blue", 'red'), bty = "n", pch = 17, cex = 1, box.lty = 0)


# use this instead
plot(df_OD_C$H_mM, df_OD_C$OD585_background, col = "orange", lty = 1, pch = 16, lwd = 1, main = "OD585 (Crerar7_T0 soil)",
     ylab = "OD585", xlab = "added [H+] mM", ylim = c(0, 3), cex=2)

points(df_OD_C$H_mM, df_OD_C$OD585, col = "blue", pch = 16, cex=2)
points(df_OD_C$H_mM, df_OD_C$OD585_subtraction, col = 'red', pch = 16, lwd = 1)
legend("topright",legend = c("Background", "After dye", "(After dye - Background)"),
    col = c("orange", "blue", 'red'), bty = "n", pch = 16, cex = 1, box.lty = 0)

# R_multi?
plot(df_OD_C$H_mM, df_OD_C$R_multi, col = "red", lty = 1, pch = 15, lwd = 1, main = "R_multi (Crerar7_T0 soil)",
     ylab = "R_multi", xlab = "added [H+] mM",cex=2)


# show R_multi and a_434, a_585
plot(df_OD_C$H_mM, df_OD_C$R_multi, col = "red", lty = 1, pch = 15, lwd = 1, main = "R_multi (Crerar7_T0 soil)",
     ylab = "R_multi", xlab = "added [H+] mM",ylim = c(-20, 100), cex=2)
abline(a=0, b=0)
points(df_OD_C$H_mM, df_OD_C$OD434_subtraction, col = "red", pch = 17)
points(df_OD_C$H_mM, df_OD_C$OD585_subtraction, col = 'red', pch = 16, lwd = 1)

legend("topright",legend = c("OD434_corrected", "OC585_corrected", "R_multi = OD585/OD434"),
    pch = c(17, 16, 15), bty = "n", col = 'red', cex = 1.2, box.lty = 0)

# R_multi and pH

plot(df_OD_C$pH_colorimetric, df_OD_C$R_multi, col = "royalblue", lty = 1, pch = 18, lwd = 1, main = "R_multi (Crerar7_T0 soil)",
     ylab = "R_multi", xlab = "pH_colorimetric", cex=1.5)


```



Plot by time point
```{r}
# df_T0 <- df_pH_ave %>% filter(Time_point == "T0")
df_T0 <- df_pH %>% filter(Time_point == "T0")

ggplot(df_T0, aes(x=H_mM, y=pH_colorimetric, color=Soil, group=Soil)) +
  geom_point(size=3, shape=16, alpha=1) +
  # geom_errorbar(aes(ymin=Ave_pH - Std_pH, ymax=Ave_pH + Std_pH), width=.05)+
  geom_line(size=1)+
  # scale_color_brewer(palette='Set1') +
  ylab("pH \n") +
  xlab("\n added [H+] mM") +
  scale_y_continuous(breaks = seq(0,12,1), limits=c(0, 12))+
  ggtitle("[T0] Soil pH perturbation (Anaerobic incubation) \n") +
  # label
  # geom_text(aes(label = pH_colorimetric), size = 3, vjust = -1.5, family="serif", show.legend  = FALSE)+
  mytheme_2d

# df_T2 <- df_pH_ave %>% filter(Time_point == "T2")
df_T4 <- df_pH %>% filter(Time_point == "T4")

ggplot(df_T4, aes(x=H_mM, y=pH_colorimetric, color=Soil, group=Soil)) +
  geom_point(size=3, shape=16, alpha=1) +
  # geom_errorbar(aes(ymin=Ave_pH - Std_pH, ymax=Ave_pH + Std_pH), width=.05)+
  geom_line(size=1)+
  # scale_color_brewer(palette='Set1') +
  ylab("pH \n") +
  xlab("\n added [H+] mM") +
  scale_y_continuous(breaks = seq(0,12,1), limits=c(0, 12))+
  ggtitle("[T4] Soil pH perturbation (Anaerobic incubation) \n") +
  # label
  # geom_text(aes(label = pH_colorimetric), size = 3, vjust = -1.5, family="serif", show.legend  = FALSE)+
  mytheme_2d

# df_T7 <- df_pH_ave %>% filter(Time_point == "T7")
df_T7 <- df_pH %>% filter(Time_point == "T7")
df_T7 %>% filter(H_mM == 0)

ggplot(df_T7, aes(x=H_mM, y=pH_colorimetric, color=Soil, group=Soil)) +
  geom_point(size=3, shape=16, alpha=1) +
  # geom_errorbar(aes(ymin=Ave_pH - Std_pH, ymax=Ave_pH + Std_pH), width=.05)+
  geom_line(size=1)+
  # scale_color_brewer(palette='Set1') +
  ylab("pH \n") +
  xlab("\n added [H+] mM") +
  scale_y_continuous(breaks = seq(0,12,1), limits=c(0, 12))+
  ggtitle("[T7] Soil pH perturbation (Anaerobic incubation) \n") +
  # label
  # geom_text(aes(label = pH_colorimetric), size = 3, vjust = -1.5, family="serif", show.legend  = FALSE)+
  mytheme_2d

# df_T9 <- df_pH_ave %>% filter(Time_point == "T9")
df_T9 <- df_pH %>% filter(Time_point == "T9")

ggplot(df_T9, aes(x=H_mM, y=pH_colorimetric, color=Soil, group=Soil)) +
  geom_point(size=3, shape=16, alpha=1) +
  # geom_errorbar(aes(ymin=Ave_pH - Std_pH, ymax=Ave_pH + Std_pH), width=.05)+
  geom_line(size=1)+
  # scale_color_brewer(palette='Set1') +
  ylab("pH \n") +
  xlab("\n added [H+] mM") +
  scale_y_continuous(breaks = seq(0,12,1), limits=c(0, 12))+
  ggtitle("[T9] Soil pH perturbation (Anaerobic incubation) \n") +
  # label
  # geom_text(aes(label = pH_colorimetric), size = 3, vjust = -1.5, family="serif", show.legend  = FALSE)+
  mytheme_2d
```


## 2.1. Let's fit a line to the pH titration curves to infer the pH - H_mM
```{r}

df_plot_no1 <- df_plot %>% filter(!(pH_colorimetric==1))

ggplot(df_plot_no1, aes(x=H_mM, y=pH_colorimetric, color=Time_days, group=Time_days)) +
  geom_point(size=3, shape=16, alpha=1) +
  # geom_errorbar(aes(ymin=Ave_pH - Std_pH, ymax=Ave_pH + Std_pH), width=.05)+
  geom_line(size=1)+
  geom_vline(xintercept=0, linetype="dashed", color = "black")+
  # scale_color_brewer(palette='Set1') +
  ylab("pH \n") +
  xlab("\n added [H+] mM") +
  scale_x_continuous(breaks = seq(-100,100,5), limits=c(-100, 100))+
  scale_y_continuous(breaks = seq(0,14,1), limits=c(0, 14))+
  ggtitle("Soil pH perturbation & titration curves (LaBaghWoods1: pH 6.66) \n") +
  # label
  # geom_text(aes(label = pH_colorimetric), size = 3, vjust = -1.5, family="serif", show.legend  = FALSE)+
  mytheme_2d

df_2.09 <- df_plot_no1 %>% filter(Time_days == 2.09 & H_mM > -30) %>% select(pH_colorimetric, H_mM, Time_days) # fit the line to the second day
dim(df_2.09)

df_2.09$H_mM_2 <- (df_2.09$H_mM)^2
df_2.09$H_mM_3 <- (df_2.09$H_mM)^3

fit.pH <- lm(pH_colorimetric ~ H_mM + H_mM_2 + H_mM_3, df_2.09)
summary(fit.pH)

perturbH <- seq(-100, 100, 0.1)
pHPredict <- predict(fit.pH,list(H_mM=perturbH, H_mM_2=perturbH^2, H_mM_3=perturbH^3))
df_auc_poly <- data.frame(H_mM = perturbH, pH = pHPredict)
plot(perturbH, pHPredict)

# how about plotting a sigmoidal function?

plot(df_2.09$pH_colorimetric ~ df_2.09$H_mM)

fit.sig <- nls(pH_colorimetric ~ SSlogis(H_mM, Asym, xmid, scal), data =df_2.09)
summary(fit.sig)

perturbH <- seq(-100, 100, 0.1)
pHPredict <- predict(fit.sig, list(H_mM=perturbH))
df_sig <- data.frame(H_mM = perturbH, pH = pHPredict)
plot(perturbH, predict(fit.sig, list(H_mM=perturbH)))



# (1) Plot fitted sigmoid line
ggplot(df_2.09, aes(x=H_mM, y=pH_colorimetric)) +
  geom_point(size=2.5, shape=16, color = "brown") +
  # stat_smooth(method = "lm", formula = y ~ x + I(x^2), size = 1) +
  # geom_errorbar(aes(ymin=NO3_mM - sd_NO3_mM, ymax=NO3_mM + sd_NO3_mM), width=.05)+
  # scale_color_brewer(palette='Set2') +
  # scale_color_manual(values = c("maroon2","deepskyblue4"))+
  xlab("Amount of pH perturbation (H+ mM) \n") +
  ylab("\n pH_colorimetric") +
  # scale_x_continuous(breaks = seq(0,16,1), limits=c(0, 16))+
  #scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  # geom_text_repel(aes(label = round(NO3_mM,3)), size = 3,family="serif", show.legend = FALSE)+
  # ggtitle("Correlation with perturbation and area under nitrate curve \n") +
  # geom_abline(slope = 1, intercept=0, show.legend = "y=x")+
  # regression line
  geom_line(data = df_sig, aes(x = H_mM, y = pH), color = "maroon2", size = 1) +
  # show equation
  # annotate("text",x=0,y=10, label= paste0("y = ", round(coef(fit.sig)[[1]],3), "+", round(coef(fit.sig)[[2]],3),"x+",round(coef(fit.sig)[[3]],3), "x^2", ",  R^2: ", round(summary(fit.sig)$r.squared,3)), color = "maroon2") +
  mytheme_2d

## use artificial dataset to fit the sigmoid function

## how about we add some points? (This is a dangerous step)
added_points = 10
df_artificial_left <- data.frame(pH_colorimetric = rep(9, added_points), H_mM = seq(-30, -100, length = added_points), Time_days= rep(2.09, added_points))
df_artificial_right <- data.frame(pH_colorimetric = rep(2.5, added_points), H_mM = seq(100, 170, length = added_points), Time_days= rep(2.09, added_points))
df_2.09 <- df_plot_no1 %>% filter(Time_days == 2.09 & H_mM > -30) %>% select(pH_colorimetric, H_mM, Time_days) # fit the line to the second day
dim(df_2.09)
df_2.09_artificial <- rbind(df_2.09, df_artificial_left, df_artificial_right)


plot(df_2.09_artificial$pH_colorimetric ~ df_2.09_artificial$H_mM)

fit.sig <- nls(pH_colorimetric ~ SSlogis(H_mM, Asym, xmid, scal), data =df_2.09_artificial)
summary(fit.sig)

perturbH <- seq(-100, 100, 0.1)
pHPredict <- predict(fit.sig, list(H_mM=perturbH))
df_sig <- data.frame(H_mM = perturbH, pH = pHPredict)
lines(perturbH, predict(fit.sig, list(H_mM=perturbH)), col = 'red')

# (1) Plot fitted linear regression line
ggplot(df_2.09, aes(x=H_mM, y=pH_colorimetric)) +
  geom_point(size=2.5, shape=16, color = "brown") +
  # stat_smooth(method = "lm", formula = y ~ x + I(x^2), size = 1) +
  # geom_errorbar(aes(ymin=NO3_mM - sd_NO3_mM, ymax=NO3_mM + sd_NO3_mM), width=.05)+
  # scale_color_brewer(palette='Set2') +
  # scale_color_manual(values = c("maroon2","deepskyblue4"))+
  xlab("Amount of pH perturbation (H+ mM) \n") +
  ylab("\n pH_colorimetric") +
  # scale_x_continuous(breaks = seq(0,16,1), limits=c(0, 16))+
  #scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  # geom_text_repel(aes(label = round(NO3_mM,3)), size = 3,family="serif", show.legend = FALSE)+
  # ggtitle("Correlation with perturbation and area under nitrate curve \n") +
  # geom_abline(slope = 1, intercept=0, show.legend = "y=x")+
  # regression line
  geom_line(data = df_sig, aes(x = H_mM, y = pH), color = "maroon2", size = 1) +
  # show equation
  # annotate("text",x=0,y=10, label= paste0("y = ", round(coef(fit.sig)[[1]],3), "+", round(coef(fit.sig)[[2]],3),"x+",round(coef(fit.sig)[[3]],3), "x^2", ",  R^2: ", round(summary(fit.sig)$r.squared,3)), color = "maroon2") +
  mytheme_2d


## just draw our own sigmoid plot
plot(df_2.09$pH_colorimetric ~ df_2.09$H_mM, xlim=c(-100, 100), ylim = c(2, 10))

x <- seq(-100, 100, 0.1)
y <- (6.5 / (1+ exp(1*(0.07*(x+125))-10))) + 2.5
lines(x, y, col = 'red')
df_draw <- data.frame(H_mM = x, pH = y)

ggplot(df_2.09, aes(x=H_mM, y=pH_colorimetric)) +
  geom_point(size=2.5, shape=16, color = "brown") +
  # stat_smooth(method = "lm", formula = y ~ x + I(x^2), size = 1) +
  # geom_errorbar(aes(ymin=NO3_mM - sd_NO3_mM, ymax=NO3_mM + sd_NO3_mM), width=.05)+
  # scale_color_brewer(palette='Set2') +
  # scale_color_manual(values = c("maroon2","deepskyblue4"))+
  xlab("Amount of pH perturbation (H+ mM) \n") +
  ylab("\n pH_colorimetric") +
  # scale_x_continuous(breaks = seq(0,16,1), limits=c(0, 16))+
  #scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  # geom_text_repel(aes(label = round(NO3_mM,3)), size = 3,family="serif", show.legend = FALSE)+
  ggtitle("Artificial sigmoidal tritration curve (pink) drawn for inferring pH \n") +
  # geom_abline(slope = 1, intercept=0, show.legend = "y=x")+
  # regression line
  geom_line(data = df_draw, aes(x = H_mM, y = pH), color = "maroon2", size = 1) +
  # show equation
  # annotate("text",x=0,y=10, label= paste0("y = ", round(coef(fit.sig)[[1]],3), "+", round(coef(fit.sig)[[2]],3),"x+",round(coef(fit.sig)[[3]],3), "x^2", ",  R^2: ", round(summary(fit.sig)$r.squared,3)), color = "maroon2") +
  mytheme_2d


```

```{r}

library(titrationCurves)
wb_sa(eqpt = TRUE, main = "Titration of WB w/ SA")
wb_sa(pka = 7, col = "blue", overlay = TRUE)


```



## 3. Time dynamics of pH

```{r}
# Get No_Nitrate sample
df_pH <- df_pH_T %>% filter(Titration_type %in% c("NaOH","HCl","No_Nitrate"))
dim(df_pH) # 160
Added_Volume <- 1.7 # ml
Soil_mg <- 0.85
moisture_percent_1 = 23.6 # LaBaghWoods1
Added_Volume + Soil_mg*(moisture_percent_1/100)
# moisture_percent_2 = 33.2 # Allandale
df_pH$Added_ul <- ifelse(df_pH$Titration_type == "NaOH", -1*df_pH$Added_ul, df_pH$Added_ul) # HCl is +, NaOH is -
df_pH %<>% mutate(H_mol = Concentration_M * Added_ul * 10^(-6)) # Calculate H mol 
df_pH$Volume <- ifelse(df_pH$Soil == "LaBaghWoods_pH6.66", Added_Volume + Soil_mg*(moisture_percent_1/100), 0) # Calc total volume
# df_pH$Volume <- ifelse(df_pH$Soil == "Allandale_pH4", Added_Volume + Soil_mg*(moisture_percent_2/100), df_pH$Volume) # Calc total volume
# df_pH$Volume %>% unique()
df_pH %<>% mutate(H_Molarity = H_mol / (Volume * 10^(-3)))
df_pH %<>% mutate(H_mM = H_Molarity * 1000)
# openxlsx::write.xlsx(df_pH, "df_pH.xlsx")

# how many levels of H_mM?
pH_pert <- df_pH %>% select(H_mM) %>% unique() %>% arrange()
df_pH %>% filter(Soil == "LaBaghWoods_pH6.66")%>% select(H_mM) %>% unique() %>% arrange(H_mM)
# df_pH %>% filter(Soil == "Allandale_pH4")%>% select(H_mM) %>% unique() %>% arrange()
colnames(df_pH)

df_pH %>% filter()

# plot time dynamics

# pH color
col_pH <- colorRampPalette(c("gold","red","purple"))

library(colorRamps)
colorRamps::green2red
plot(rep(1,13),col=col_pH(13),pch=19,cex=3)
grad_pH <- scale_colour_gradientn(colours = col_pH(100))

# Confer this page (https://stackoverflow.com/questions/21537782/how-to-set-fixed-continuous-colour-values-in-ggplot2)
# myPalette <- colorRampPalette(rev(brewer.pal(11, "Spectral")))
# sc <- scale_colour_gradientn(colours = myPalette(100), limits=c(1, 8))

# 1. pH perturbation
# first only plot No_Nitrate samples
df_no_no3 <- df_pH %>% filter(Titration_type == "No_Nitrate") %>% select(H_mM, pH_colorimetric, Soil, Time_hours)
df_no_ab <- df_pH %>% filter(Titration_type == "HCl" & H_mM == 0) %>% select(H_mM, pH_colorimetric, Soil, Time_hours)
plot(df_no_no3$Time_hours, df_no_no3$pH_colorimetric, )
points(df_no_ab$Time_hours, df_no_ab$pH_colorimetric, col='red')

# plot ave and std
df_no_no3_ave <- df_no_no3 %>% group_by(H_mM, Soil, Time_hours) %>% summarize(pH = mean(pH_colorimetric), std_pH = sd(pH_colorimetric)) %>% ungroup() %>% mutate(Sample_type = "No_Nitrate_added")
df_no_ab_ave <- df_no_ab %>% group_by(H_mM, Soil, Time_hours) %>% summarize(pH = mean(pH_colorimetric), std_pH = sd(pH_colorimetric)) %>% ungroup() %>% mutate(Sample_type = "2mM_Nitrate_added")

df_no <- rbind(df_no_no3_ave, df_no_ab_ave)

ggplot(df_no, aes(x=Time_hours, y=pH, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=16) +
  geom_line(size=1.2)+
  geom_errorbar(aes(ymin=pH - std_pH, ymax=pH + std_pH), width=.05)+
  # scale_colour_gradientn(colours = col_pH(100)) +
  # scale_color_manual(values=grad_pH) +
  ylab("pH \n") +
  xlab("\n Time (hr)") +
  scale_y_continuous(breaks = seq(6.5,8,0.25), limits=c(6.5, 8))+
  ggtitle("Effect of nitrate addition (no acid/base added) \n") +
  # label
  # geom_text(aes(label = round(NO3_mM,3)), size = 3, vjust = -1.5, family="serif", show.legend = FALSE)+
  mytheme_2d +
  facet_grid(. ~ Soil) +
  theme(strip.background = element_rect(colour="black", fill="white", size=0.1))

# let's include some pH perturbed samples
df_pH %>% filter(!(H_mM == 0)) %>% dim()
df_10 <- df_pH %>% filter(!(H_mM == 0)) %>% filter(H_mM < 15 & H_mM > -15) %>% filter(H_mM > 5)
df_10 %<>% select(H_mM, Soil, Time_hours, pH_colorimetric) %>% rename(pH = pH_colorimetric) %>% mutate(std_pH = 0) %>% mutate(Sample_type = paste0("H+ ", round(H_mM,2), " mM"))

df_no_10 <- rbind(df_no, df_10)
colnames(df_no_10)

df_no_10$Sample_type <- factor(df_no_10$Sample_type, levels = c("2mM_Nitrate_added", "H+ 5.26 mM", "No_Nitrate_added","H+ 10.52 mM"))

ggplot(df_no_10, aes(x=Time_hours, y=pH, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5) +
  geom_line(size=1.2)+
  geom_errorbar(aes(ymin=pH - std_pH, ymax=pH + std_pH), width=.05)+
  # scale_colour_gradientn(colours = col_pH(100)) +
  # scale_color_manual(values=grad_pH) +
  ylab("pH \n") +
  xlab("\n Time (hr)") +
  # scale_y_continuous(breaks = seq(6.5,8,0.25), limits=c(6.5, 8))+
  ggtitle("Effect of nitrate addition in comparison with acid added samples \n") +
  # label
  # geom_text(aes(label = round(NO3_mM,3)), size = 3, vjust = -1.5, family="serif", show.legend = FALSE)+
  mytheme_2d +
  facet_grid(. ~ Soil) +
  theme(strip.background = element_rect(colour="black", fill="white", size=0.1))

ggplot(df_pH, aes(x=Time_hours, y=pH_colorimetric, color=H_mM, group=H_mM)) +
  geom_point(size=2.5, shape=16) +
  geom_line(size=1.2)+
  # geom_errorbar(aes(ymin=NO3_mM - Std_NO3_mM, ymax=NO3_mM + Std_NO3_mM), width=.05)+
  scale_colour_gradientn(colours = col_pH(100)) +
  # scale_color_manual(values=grad_pH) +
  ylab("pH \n") +
  xlab("\n Time (hr)") +
  # scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  ggtitle("pH perturbation \n") +
  # label
  # geom_text(aes(label = round(NO3_mM,3)), size = 3, vjust = -1.5, family="serif", show.legend = FALSE)+
  mytheme_2d +
  facet_grid(. ~ Soil) +
  theme(strip.background = element_rect(colour="black", fill="white", size=0.1))



```


