---
title: "220519_Griess_crerar7_extreme_pH"
author: "KiseokUchicago"
date: "2022-05-25"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---


```{r global_options, include=FALSE}
library(knitr)
knitr::opts_chunk$set(fig.width=11, fig.height=9,
                      error=TRUE, echo=TRUE, eval=TRUE, warning=FALSE, message=FALSE,
                      tidy.opts=list(width.cutoff=40),tidy=TRUE)
```

## Time series analysis - crerar7 pH extreme experiment
Researcher: **Kiseok Lee** \
Experiment Date: 5/12/22 - 5/17/22 (5 days) \
Analysis Date: 5/25/21
Lab: **Seppe Kuehn**

```{r}
# libraries
library(dplyr)
library(ggplot2)
library(RColorBrewer)
library(vegan)
library(tidyverse)
library(magrittr)
library(readxl)
library(reshape2)
library(gtools)
library(devtools)
library(openxlsx)
library(ape)
library(stringr)
library(tidyr)
library(ggrepel)
library(ggpubr)
require(gridExtra)
# grid.arrange(p_strain, p_ai, nrow=1)

## theme for ggplot
mytheme <- theme_bw() + 
  theme(text = element_text(face="bold", colour = 'black')) +
  theme(plot.title = element_text(size = 19,hjust = 0.5,face="bold", colour = 'black')) + 
  theme(axis.title.x = element_text(size = 17,hjust = 0.5,face="bold", colour = 'black')) + 
  theme(axis.title.y = element_text(size = 17,hjust = 0.5,face="bold", colour = 'black')) + 
  theme(axis.text.x = element_text(hjust = 0.5, vjust=0.3,size=13,face="bold", colour = 'black'))+
  theme(axis.text.y = element_text(size=13,face="bold", colour = 'black'))+
  theme(panel.grid.major = element_blank()) +
  theme(panel.grid.minor = element_blank(),panel.background=element_blank(),panel.border=element_blank(),plot.background=element_blank()) +
  theme(axis.ticks = element_line(size = 1.1))+
  theme(legend.text=element_text(size=10,face="bold", colour = 'black'))


mytheme_2d <- theme_bw() + 
  theme(text = element_text(face="bold", colour = 'black')) +
  theme(plot.title = element_text(size = 19,hjust = 0.5,face="bold", colour = 'black')) + 
  theme(axis.title.x = element_text(size = 17,hjust = 0.5,face="bold", colour = 'black')) + 
  theme(axis.title.y = element_text(size = 17,hjust = 0.5,face="bold", colour = 'black')) + 
  theme(axis.text.x = element_text(hjust = 0.5, vjust=0.3,size=13,face="bold", colour = 'black'))+
  theme(axis.text.y = element_text(size=13,face="bold", colour = 'black'))+
  # theme(panel.grid.major = element_blank()) +
  # theme(panel.grid.minor = element_blank(),panel.background=element_blank(),plot.background=element_blank()) +
  theme(axis.ticks = element_line(size = 1.1))+
  theme(legend.text=element_text(size=10,face="bold", colour = 'black'))


# color collection
my_color_collection <- c(
  "#CBD588", "#5F7FC7", "orange", "#AD6F3B", "#673770", 
  "#D14285", "#652926", "#C84248", "#8569D5", "#5E738F",
  "#D1A33D", "#8A7C64", "#599861","#616163", "#FFCDB2",
  "#6D9F71", "#242F40",
  "#CCA43B", "#F92A82", "#ED7B84", "#7EB77F", 
  "#DEC4A1", "#E5D1D0", '#0E8482', '#C9DAEA', '#337357', 
  '#95C623', '#E55812', '#04471C', '#F2D7EE', '#D3BCC0', 
  '#A5668B', '#69306D', '#0E103D', '#1A535C', '#4ECDC4', 
  '#F7FFF7', '#FF6B6B', '#FFE66D', '#6699CC', '#FFF275', 
  '#FF8C42', '#FF3C38', '#A23E48', '#000000', '#CF5C36', 
  '#EEE5E9', '#7C7C7C', '#EFC88B', '#2E5266', '#6E8898', 
  '#9FB1BC', '#D3D0CB', '#E2C044', '#5BC0EB', '#FDE74C', 
  '#9BC53D', '#E55934', '#FA7921', "#CD9BCD", "#508578", "#DA5724")

# for git push, use this instead of using wflow_git_push()
# git push -u origin master (in the Git app / in the working directory)

# for making pdf file
library(rmarkdown)
# render("analysis/~~.Rmd", "pdf_document")

```


## 1. Import data table from python code
We are going to use the vcl3 treated standard curve that is fitted with pure nitrate standards
```{r error=TRUE}
# import file
df_plate1 <- openxlsx::read.xlsx("data/220519_Griess_crerar7_extreme.xlsx")
# df_plate2 <- openxlsx::read.xlsx("data/220519_Griess_plate2.xlsx")
# df_plate3 <- openxlsx::read.xlsx("data/220519_Griess_plate3.xlsx")
# df_plate4 <- openxlsx::read.xlsx("data/220519_Griess_plate4.xlsx")
# df_plate5 <- openxlsx::read.xlsx("data/220519_Griess_plate5.xlsx")
# df_plate6 <- openxlsx::read.xlsx("data/220519_Griess_plate6.xlsx")
# df_plate7 <- openxlsx::read.xlsx("data/220519_Griess_plate7.xlsx")
# df_plate8 <- openxlsx::read.xlsx("data/220519_Griess_plate8.xlsx")
# df_plate9 <- openxlsx::read.xlsx("data/220519_Griess_plate9.xlsx")
# df_plate10 <- openxlsx::read.xlsx("data/220519_Griess_plate10.xlsx")
# df_plate11 <- openxlsx::read.xlsx("data/220519_Griess_plate11.xlsx")
# df_plate12 <- openxlsx::read.xlsx("data/220519_Griess_plate12.xlsx")
# df_plate13 <- openxlsx::read.xlsx("data/220519_Griess_plate13.xlsx")
# df_plate14 <- openxlsx::read.xlsx("data/220519_Griess_plate14.xlsx")
# df_plate15 <- openxlsx::read.xlsx("data/220519_Griess_plate15.xlsx")
# df_plate16 <- openxlsx::read.xlsx("data/220519_Griess_plate16.xlsx")

head(df_plate1)
colnames(df_plate1)
dim(df_plate1)

head(df_plate2)
colnames(df_plate2)
dim(df_plate2)

head(df_plate3)
colnames(df_plate3)
dim(df_plate3)

head(df_plate4)
colnames(df_plate4)
dim(df_plate4)

head(df_plate5)
colnames(df_plate5)
dim(df_plate5)

head(df_plate6)
colnames(df_plate6)
dim(df_plate6)

head(df_plate7)
colnames(df_plate7)
dim(df_plate7)

head(df_plate8)
colnames(df_plate8)
dim(df_plate8)

head(df_plate9)
colnames(df_plate9)
dim(df_plate9)

head(df_plate10)
colnames(df_plate10)
dim(df_plate10)

head(df_plate11)
colnames(df_plate11)
dim(df_plate11)

# head(df_plate16)
# colnames(df_plate16)
# dim(df_plate16)


# X1 to Well
# df_plate1 %<>% rename(Well = X1)
# df_plate2 %<>% rename(Well = X1)
# df_plate3 %<>% rename(Well = X1)
# df_plate4 %<>% rename(Well = X1)
# df_plate5 %<>% rename(Well = X1)
# df_plate6 %<>% rename(Well = X1)
# df_plate7 %<>% rename(Well = X1)
# df_plate8 %<>% rename(Well = X1)
# df_plate9 %<>% rename(Well = X1)
# df_plate10 %<>% rename(Well = X1)
# df_plate11 %<>% rename(Well = X1)
# df_plate12 %<>% rename(Well = X1)
# df_plate13 %<>% rename(Well = X1)
# df_plate14 %<>% rename(Well = X1)
# df_plate15 %<>% rename(Well = X1)
# df_plate16 %<>% rename(Well = X1)


# remove wells that were contaminated during the experiment
# df_plate1 %<>% filter(!(Well %in% c("A04"))) # NA detected below... don't know the reason
# df_plate4 %<>% filter(!(Well %in% c("H05"))) # filter defect
# df_plate6 %<>% filter(!(Well %in% c("G05"))) # Too low.... why???
# df_plate8 %<>% filter(!(Well %in% c("A01", "A09"))) # filter defect
# df_plate9 %<>% filter(!(Well %in% c("D11"))) # NA detected below...
# df_plate11 %<>% filter(!(Well %in% c("A12"))) # filter defect

# bind two dataframe
df_p <- rbind(df_plate1)
              # , df_plate2, df_plate3, df_plate4, df_plate5, df_plate6, df_plate7, df_plate8, df_plate9, df_plate10, df_plate11)
              # df_plate12, df_plate13, df_plate14, df_plate15, df_plate16)
dim(df_p)

# remove NA
dim(df_p) # 1056
df_p[is.na(df_p)]
# df_na <- df_p[rowSums(is.na(df_p)) > 0,]  # A04 in plate1 has NA. Let's remove from the wells above.
# df_p <- na.omit(df_p)
# df_p <- df_p[rowSums(is.na(df_p)) == 0,]
dim(df_p) # 1055

# multiply dilution factor which is 5/2
# df_p %<>% select(-NO2_OD540, -NO2NO3_OD540)
df_p %<>% mutate(NO2_mM = NO2_mM * (5/2), NO2NO3_mM = NO2NO3_mM * (5/2), NO3_mM = NO3_mM * (5/2))

# Get the metadata for time point and left join
Time_table <- openxlsx::read.xlsx("data/220517_time_table.xlsx")
# Time_table_BN <- openxlsx::read.xlsx("data/220519_time_table_BN.xlsx")
# Time_table <- rbind(Time_table_AU, Time_table_BN)

Time_table %<>% select(-Date) 
Time_table$Time_hours <- round(Time_table$Time_hours, 1)
Time_table$Time_days <- round(Time_table$Time_days, 1)
df_time <- Time_table
dim(df_p)
df_p <- df_p %>% left_join(Time_table, by=("Time_point"="Time_point"))
dim(df_p)
colnames(df_p)
# time_point order
# df_p$Time_point <-  factor(df_p$Time_point, levels = c(paste0("LBA_T",0:10), paste0("Sterile_T",0:10)))
df_p$Time_point <-  factor(df_p$Time_point, levels = c(paste0("T",0:10)))

```

## 2. Get average and standard deviation & Moisture correction & Blank correction
```{r}
# plot to see
ggplot(df_p, aes(x=Time_point, y=NO3_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  scale_fill_brewer(palette='Set2') +
  ylab("NO3- (mM) \n") +
  xlab("\n Time_point") +
  # scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  ggtitle("Without averaging \n") +
  mytheme_2d +
  theme(axis.text.x = element_text(hjust = 0.8, vjust=0.8, size=13, family="serif", angle = 40))

# plot to see
ggplot(df_p, aes(x=Time_point, y=NO2_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  scale_fill_brewer(palette='Set2') +
  ylab("NO2- (mM) \n") +
  xlab("\n Time_point") +
  # scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  ggtitle("Without averaging \n") +
  mytheme_2d+
  theme(axis.text.x = element_text(hjust = 0.8, vjust=0.8, size=13, family="serif", angle = 40))

# let's plot the no nitrate sample's nitrate, nitrite levels
df_no_nitrite <- df_p %>% filter(Sample_type == "No_Nitrate")

ggplot(df_no_nitrite, aes(x=Time_point, y=NO3_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  scale_fill_brewer(palette='Set2') +
  ylab("NO3- (mM) \n") +
  xlab("\n Time_point") +
  # scale_y_continuous(breaks = seq(0,0.5,0.05), limits=c(0, 0.5))+
  ggtitle("Samples without nitrate addition \n") +
  mytheme_2d +
  theme(axis.text.x = element_text(hjust = 0.8, vjust=0.8, size=13, family="serif", angle = 40))

ggplot(df_no_nitrite, aes(x=Time_point, y=NO2_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  scale_fill_brewer(palette='Set2') +
  ylab("NO2- (mM) \n") +
  xlab("\n Time_point") +
  scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  ggtitle("Samples without nitrate addition \n") +
  mytheme_2d+
  theme(axis.text.x = element_text(hjust = 0.8, vjust=0.8, size=13, family="serif", angle = 40))

# T8 is weird
# how about blanks?

# let's plot the blank sample's nitrate, nitrite levels
df_A_blank <- df_p %>% filter(Sample_type == "Nitrate_Blank")
ggplot(df_A_blank, aes(x=Time_point, y=NO3_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  scale_fill_brewer(palette='Set2') +
  ylab("NO3- (mM) \n") +
  xlab("\n Time_point") +
  scale_y_continuous(breaks = seq(0,2.5,0.1), limits=c(0, 2.5))+
  ggtitle("Nitrate blanks \n") +
  mytheme_2d +
  theme(axis.text.x = element_text(hjust = 0.8, vjust=0.8, size=13, family="serif", angle = 40))

ggplot(df_A_blank, aes(x=Time_point, y=NO2_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  scale_fill_brewer(palette='Set2') +
  ylab("NO2- (mM) \n") +
  xlab("\n Time_point") +
  scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  ggtitle("Nitrate blanks \n") +
  mytheme_2d+
  theme(axis.text.x = element_text(hjust = 0.8, vjust=0.8, size=13, family="serif", angle = 40))

# let's plot the Nitrite blank sample's nitrate, nitrite levels
df_I_blank <- df_p %>% filter(Sample_type == "Nitrite_Blank")
ggplot(df_I_blank, aes(x=Time_point, y=NO3_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  scale_fill_brewer(palette='Set2') +
  ylab("NO3- (mM) \n") +
  xlab("\n Time_point") +
  scale_y_continuous(breaks = seq(0,2.5,0.1), limits=c(0, 2.5))+
  ggtitle("Nitrite blanks \n") +
  mytheme_2d +
  theme(axis.text.x = element_text(hjust = 0.8, vjust=0.8, size=13, family="serif", angle = 40))

ggplot(df_I_blank, aes(x=Time_point, y=NO2_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  scale_fill_brewer(palette='Set2') +
  ylab("NO2- (mM) \n") +
  xlab("\n Time_point") +
  # scale_y_continuous(breaks = seq(0,2.5,0.1), limits=c(0, 2.5))+
  ggtitle("Nitrite blanks \n") +
  mytheme_2d+
  theme(axis.text.x = element_text(hjust = 0.8, vjust=0.8, size=13, family="serif", angle = 40))

### Important ###
# Due to the nitrate decrease in time, something is wrong. Therefore, I would omit the evaporation correction????


# average technical replicate (here only 1 replicate per pH perturbation)
colnames(df_p)
dim(df_p)

# df_p <- df_p %>% group_by(Nitrite_input, Nitrate_input, Soil, Titration_type, Concentration_M, Added_ul, Sample_type, Time_point, Time_minutes, Time_hours, Time_days) %>% summarise(NO2_mM = mean(NO2_mM), Std_NO2_mM = sd(NO2_mM), NO3_mM = mean(NO3_mM), Std_NO3_mM = sd(NO3_mM)) %>% ungroup()


# mols and molarity unit conversion
# test
df_p$Titration_type %>% length()

# Setting H_mM column
# df_soil <- df_p %>% filter(Titration_type %in% c("NaOH","HCl"))

Added_Volume <- 1.7 # ml
Soil_mg <- 0.85
moisture_percent_1 = 16 # Crerar7
Added_Volume + Soil_mg*(moisture_percent_1/100)
# moisture_percent_2 = 8.12 # Sterile - LaBaghWoods that has been autoclaved 5 times.
# Added_Volume + Soil_mg*(moisture_percent_2/100)
# moisture_percent_3 = 9.0 # Crerar7
# Added_Volume + Soil_mg*(moisture_percent_3/100)

df_p$Added_ul <- ifelse(df_p$Titration_type == "NaOH", -1*df_p$Added_ul, df_p$Added_ul) # HCl is +, NaOH is -
df_p %<>% mutate(H_mol = Concentration_M * Added_ul * 10^(-6)) # Calculate H mol 
df_p$Volume <- ifelse(df_p$Soil == "Crerar7_pH8.08", Added_Volume + Soil_mg*(moisture_percent_1/100),
                      ifelse(df_p$Soil == "LaBaghWoods_autoclaved_pH6.66", Added_Volume + Soil_mg*(moisture_percent_2/100),
                             0))
                             # ifelse(df_p$Soil == "Crerar1_pH8.05", Added_Volume + Soil_mg*(moisture_percent_3/100),
                                    # 0))) # Calc total volume

# df_p$Volume <- ifelse(df_p$Soil == "Allandale_pH4", Added_Volume + Soil_mg*(moisture_percent_2/100), df_p$Volume) # Calc total volume
# df_p$Volume %>% unique()
df_p %<>% mutate(H_Molarity = H_mol / (Volume * 10^(-3)))
df_p %<>% mutate(H_mM = H_Molarity * 1000)
# openxlsx::write.xlsx(df_p, "df_p.xlsx")

# how many levels of H_mM?
df_p %>% filter(Soil == "Crerar7_pH8.08")%>% select(H_mM) %>% unique() %>% arrange(H_mM)
# df_p %>% filter(Soil == "LaBaghWoods_autoclaved_pH6.66")%>% select(H_mM) %>% unique() %>% arrange(H_mM)
# df_p %>% filter(Soil == "Crerar1_pH8.05")%>% select(H_mM) %>% unique() %>% arrange()
colnames(df_p)

## Moisture correction
dim(df_p)

# Testing negative samples
df_no3_blank <- df_p %>% filter(Sample_type == "Nitrate_Blank")  # Use Nitrate_Blank instead in the future
df_no3_blank # 33

df_no2_blank <- df_p %>% filter(Sample_type == "Nitrite_Blank")
df_no2_blank # 33
# close to zero

# 1. Apply moisture correction factor (correcting for moisture in soil)
soil_spike_ratio = 0.5 # soil weight(0.85g) / spike in volume (1.7ml) 

mcf_1 = (soil_spike_ratio*(moisture_percent_1/100) + 1)
mcf_1
# mcf_2 = (soil_spike_ratio*(moisture_percent_2/100) + 1)
# mcf_2
# mcf_3 = (soil_spike_ratio*(moisture_percent_3/100) + 1)
# mcf_3

# apply moisture factor to each soil
dim(df_p)
df_p %>% select(Soil) %>% unique()

# this is a special case with no replicates
df_p_mcf_1 <- df_p %>% filter(Soil == "Crerar7_pH8.08") %>% filter(Titration_type %in% c("NaOH","HCl","No_Nitrate")) %>% mutate(NO3_mM = NO3_mM * mcf_1, NO2_mM = NO2_mM * mcf_1)
dim(df_p_mcf_1) #923
# df_p_mcf_2 <- df_p %>% filter(Soil == "LaBaghWoods_autoclaved_pH6.66") %>%  filter(Titration_type %in% c("NaOH","HCl","No_Nitrate")) %>% mutate(NO3_mM = NO3_mM * mcf_2, NO2_mM = NO2_mM * mcf_2)
# dim(df_p_mcf_2) #426
# df_p_mcf_3 <- df_p %>% filter(Soil == "Crerar1_pH8.05") %>% filter(Titration_type %in% c("NaOH","HCl","No_Nitrate")) %>% mutate(NO3_mM = NO3_mM * mcf_3, NO2_mM = NO2_mM * mcf_3)
# dim(df_p_mcf_3) #426

df_p_others_mcf <- df_p %>% filter(Sample_type %in% c("Nitrite_Blank", "Nitrate_Blank", "Ammonium_Blank")) # Use Nitrate_Blank instead in the future
dim(df_p_others_mcf) #24
df_p_mcf <- rbind(df_p_mcf_1, df_p_others_mcf)
dim(df_p_mcf) # 48

# plot to see
ggplot(df_p_mcf, aes(x=Time_hours, y=NO3_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  # geom_errorbar(aes(ymin=NO3_mM - Std_NO3_mM, ymax=NO3_mM + Std_NO3_mM), width=.05)+
  scale_fill_brewer(palette='Set2') +
  ylab("NO3- (mM) \n") +
  xlab("\n Time (hours)") +
  # scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  ggtitle("After averaging with biological replicates \n") +
  mytheme_2d

# 2. Apply blank correction factor (drying effect during incubation)
# Blank reads
df_no3_blank <- df_p %>% filter(Sample_type == "Nitrate_Blank")
df_no3_blank
df_no2_blank <- df_p %>% filter(Sample_type == "Nitrite_Blank")
df_no2_blank

# df_aero_blank$Nitrate_input <- as.numeric(as.character(df_aero_blank$Nitrate_input))
df_no2_blank %<>% mutate(Correction_factor_NO2 = (Nitrite_input / NO2_mM)) 
df_no3_blank %<>% mutate(Correction_factor_NO3 = (Nitrate_input / NO3_mM)) 

# average the blanks by time point
cf_no2 <- df_no2_blank %>% select(Soil, Time_point, Correction_factor_NO2) %>% group_by(Soil, Time_point) %>% summarize(Correction_factor_NO2 = mean(Correction_factor_NO2)) %>% ungroup()
cf_no3 <- df_no3_blank %>% select(Soil, Time_point, Correction_factor_NO3) %>% group_by(Soil, Time_point) %>% summarize(Correction_factor_NO3 = mean(Correction_factor_NO3)) %>% ungroup()
# why is nitrate decreasing????


# left join and multiply the correction factor
# left join to samples
df_sample_mcf <- df_p_mcf %>% filter(!(Sample_type %in% c("Nitrite_Blank","Nitrate_Blank","Ammonium_Blank")))
dim(df_sample_mcf) #1065
df_sample_mcf$Sample_type %>% unique()

df_sample_bcf <- df_sample_mcf %>% left_join(cf_no2, by = c("Soil"="Soil", "Time_point"="Time_point")) %>% left_join(cf_no3, by = c("Soil"="Soil", "Time_point"="Time_point"))
dim(df_sample_bcf)

df_sample_bcf <- df_sample_bcf %>% mutate(NO3_mM = NO3_mM * Correction_factor_NO3, NO2_mM = NO2_mM * Correction_factor_NO2)
dim(df_sample_bcf) #849

# merge dataframe with blank just for convenience
df_p_blanks_bcf <- df_p_mcf %>% filter(Sample_type %in% c("Nitrite_Blank","Nitrate_Blank","Ammonium_Blank")) %>% left_join(cf_no2, by = c("Soil"="Soil", "Time_point"="Time_point")) %>% left_join(cf_no3, by = c("Soil"="Soil", "Time_point"="Time_point"))
dim(df_p_blanks_bcf) #197 26
dim(df_sample_bcf) # 849 26
df_p_bcf <- rbind(df_sample_bcf, df_p_blanks_bcf)
dim(df_p_bcf) # 1055

## innate nitrate
df_p_bcf %>% filter(Titration_type == "No_Nitrate" & Time_point == "LBA_T0") %>% select(NO3_mM) %>% unlist() %>% mean()
df_p_bcf %>% filter(Titration_type == "No_Nitrate" & Time_point == "Sterile_T0") %>% select(NO3_mM) %>% unlist() %>% mean()

# export
df_p_bcf$Time_point
# removing timepoint T8
df_kyle <- df_p_bcf
df_kyle$Time_point %>% unique()
dim(df_kyle)
# write.xlsx(df_kyle, "220519_Griess_antibiotics_experiment_to_kyle.xlsx")

df_kyle2 <- df_kyle %>% filter(Titration_type %in% c("NaOH", "HCl"))
dim(df_kyle2)
# write.xlsx(df_kyle2, "220519_Griess_antibiotics_dose_experiment_remove_blanks.xlsx")

                               
```


## 3. Sanity check: moisture correction & blank correction factor 

Blank correction \
Use the nitrate concentration of the blank and use the ratio. \
For example, multiply to nitrate concentration x (2mM / changed [NO3]) \

```{r}
# without any correction
# nitrate blanks
dim(df_no3_blank)
ggplot(df_no3_blank, aes(x=Time_hours, y=NO3_mM, color=Soil, group=Soil)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  # geom_errorbar(aes(ymin=NO3_mM - Std_NO3_mM, ymax=NO3_mM + Std_NO3_mM), width=.05)+
  # scale_color_brewer(palette='Set2') +
  # scale_color_manual(values = c("deepskyblue4","maroon2"))+
  ylab("Measured NO3- (mM) \n") +
  xlab("\n Time (hr)") +
  scale_y_continuous(breaks = seq(0,2.5,0.5), limits=c(0, 2.5))+
  # scale_x_continuous(breaks = seq(0,2.1,0.25), limits=c(0, 2.1))+
  ggtitle("Nitrate blank \n") +
  mytheme_2d

# nitrite blanks
dim(df_no2_blank)
ggplot(df_no2_blank, aes(x=Time_hours, y=NO2_mM, color=Soil, group=Soil)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  # geom_errorbar(aes(ymin=NO2_mM - Std_NO2_mM, ymax=NO2_mM + Std_NO2_mM), width=.05)+
  # scale_color_brewer(palette='Set2') +
  # scale_color_manual(values = c("deepskyblue4","maroon2"))+
  ylab("Measured NO2- (mM) \n") +
  xlab("\n Time (hr)") +
  scale_y_continuous(breaks = seq(0,2.7,0.5), limits=c(0, 2.7))+
  # scale_x_continuous(breaks = seq(0,2.1,0.25), limits=c(0, 2.1))+
  ggtitle("Nitrite blank \n") +
  mytheme_2d

# without any correction
ggplot(df_p, aes(x=Time_hours, y=NO3_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  # geom_errorbar(aes(ymin=NO3_mM - Std_NO3_mM, ymax=NO3_mM + Std_NO3_mM), width=.05)+
  # scale_color_brewer(palette='Set2') +
  # scale_color_manual(values = c("deepskyblue4","maroon2"))+
  ylab("Measured NO3- (mM) \n") +
  xlab("\n Time (hr)") +
  # scale_y_continuous(breaks = seq(0,5.1,1), limits=c(0, 5.1))+
  # scale_x_continuous(breaks = seq(0,5.1,1), limits=c(0, 5.1))+
  ggtitle("(Without any correction) All samples \n") +
  mytheme_2d +
  facet_grid(. ~ Soil) +
  theme(strip.background = element_rect(colour="black", fill="white", size=0.1))


### What are those points with very high std?
colnames(df_p)
# df_p %>% arrange(desc(Std_NO3_mM)) %>% select(Soil, Titration_type, Concentration_M, Sample_type, Time_point, Std_NO3_mM) 
## based on this I corrected the wrongly removed E02 -< removed E01 (filter burst). Eliminated point P11 G11.

# After moisture correction
ggplot(df_p_mcf, aes(x=Time_hours, y=NO3_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  # geom_errorbar(aes(ymin=NO3_mM - Std_NO3_mM, ymax=NO3_mM + Std_NO3_mM), width=.05)+
  # scale_color_brewer(palette='Set2') +
  # scale_color_manual(values = c("deepskyblue4","maroon2"))+
  ylab("Measured NO3- (mM) \n") +
  xlab("\n Time (hr)") +
  # scale_y_continuous(breaks = seq(0,5.1,1), limits=c(0, 5.1))+
  # scale_x_continuous(breaks = seq(0,5.1,1), limits=c(0, 5.1))+
  ggtitle("(After moisture correction) All samples \n") +
  mytheme_2d +
  facet_grid(. ~ Soil) +
  theme(strip.background = element_rect(colour="black", fill="white", size=0.1))

# After blank correction (evaporation) 
ggplot(df_p_bcf, aes(x=Time_hours, y=NO3_mM, color=Sample_type, group=Sample_type)) +
  geom_point(size=2.5, shape=21) +
  # geom_line(size=1)+
  # geom_errorbar(aes(ymin=NO3_mM - Std_NO3_mM, ymax=NO3_mM + Std_NO3_mM), width=.05)+
  # scale_color_brewer(palette='Set2') +
  # scale_color_manual(values = c("deepskyblue4","maroon2"))+
  ylab("Measured NO3- (mM) \n") +
  xlab("\n Time (hr)") +
  # scale_y_continuous(breaks = seq(0,5.1,1), limits=c(0, 5.1))+
  # scale_x_continuous(breaks = seq(0,5.1,1), limits=c(0, 5.1))+
  ggtitle("(After moisture + blank correction) All samples \n") +
  mytheme_2d +
  facet_grid(. ~ Soil) +
  theme(strip.background = element_rect(colour="black", fill="white", size=0.1))


```

## 4. Nitrogen dynamics

## 4.1. pH perturbation experiment.
- Is there a difference in pH perturbation levels?
```{r}
# pH color
col_pH <- colorRampPalette(c("gold","red","purple"))

library(colorRamps)
colorRamps::green2red
plot(rep(1,13),col=col_pH(13),pch=19,cex=3)
grad_pH <- scale_colour_gradientn(colours = col_pH(100))

# Confer this page (https://stackoverflow.com/questions/21537782/how-to-set-fixed-continuous-colour-values-in-ggplot2)
# myPalette <- colorRampPalette(rev(brewer.pal(11, "Spectral")))
# sc <- scale_colour_gradientn(colours = myPalette(100), limits=c(1, 8))

# 1. pH perturbation
# plot Nitrate

# only autoclaved soil is relevant for this analysis
# df_p_bcf$Soil <-  factor(df_p_bcf$Soil, levels = c("Barneveld2"))
df_plot <- df_p_bcf %>% filter(Titration_type %in% c("NaOH","HCl")) 
df_plot2 <- df_p_bcf %>% filter(Titration_type %in% c("NaOH","HCl")) 

# include pH data of the endpoint
# df_pH_T7_10 <- df_220521_pH %>% filter(Time_point %in% c("T7","T10"))
# 
# df_plot2 <- df_plot2 %>% left_join(df_pH_T7_10, by=c("Soil"="Soil", "Titration_type"="Titration_type","Unit"="Unit", "Antibiotics_type"="Antibiotics_type", "Dose_ppm"="Dose_ppm"))
df_plot2$H_mM <- round(df_plot2$H_mM, 0)
df_plot2$H_mM <- factor(df_plot2$H_mM)

# plot with H_mM
ggplot(df_plot2, aes(x=Time_hours, y=NO3_mM, color=H_mM, group=H_mM)) +
  geom_point(size=2.5, shape=16) +
  geom_line(size=1.2)+
  # geom_errorbar(aes(ymin=NO3_mM - Std_NO3_mM, ymax=NO3_mM + Std_NO3_mM), width=.05)+
  # scale_colour_gradientn(colours = (col_pH(100))) +
  # scale_color_manual(values=grad_pH) +
  ylab("NO3- (mM) \n") +
  xlab("\n Time (hr)") +
  # scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  # label
  # geom_text(aes(label = round(NO3_mM,3)), size = 3, vjust = -1.5, family="serif", show.legend = FALSE)+
  mytheme_2d +
  facet_grid(. ~ Soil) +
  theme(strip.background = element_rect(colour="black", fill="white", size=0.1))+
  theme(strip.text.x = element_text(size = 17))

# plot Nitrite
ggplot(df_plot2, aes(x=Time_hours, y=NO2_mM, color=H_mM, group=H_mM)) +
  geom_point(size=2.5, shape=16) +
  geom_line(size=1.5)+
  # geom_errorbar(aes(ymin=NO2_mM - Std_NO2_mM, ymax=NO2_mM + Std_NO2_mM), width=.05)+
  # scale_colour_gradientn(colours = (col_pH(100))) +
  # scale_color_manual(values=col_pH(4)) +
  ylab("NO2- (mM) \n") +
  xlab("\n Time (hr)") +
  # scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  # label
  # geom_text(aes(label = round(NO2_mM,3)), size = 3, vjust = -1.5, family="serif", show.legend = FALSE)+
  mytheme_2d +
  facet_grid(. ~ Soil) +
  theme(strip.background = element_rect(colour="black", fill="white", size=0.1))+
  theme(strip.text.x = element_text(size = 17))

p_A <- ggplot(df_plot2, aes(x=Time_hours, y=NO3_mM, color=H_mM, group=H_mM)) +
  geom_point(size=2.5, shape=16) +
  geom_line(size=1.2)+
  # geom_errorbar(aes(ymin=NO3_mM - Std_NO3_mM, ymax=NO3_mM + Std_NO3_mM), width=.05)+
  # scale_colour_gradientn(colours = (col_pH(100))) +
  # scale_color_manual(values=grad_pH) +
  ylab("NO3- (mM) \n") +
  xlab("\n Time (hr)") +
  # scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  # label
  # geom_text(aes(label = round(NO3_mM,3)), size = 3, vjust = -1.5, family="serif", show.legend = FALSE)+
  mytheme_2d +
  facet_grid(. ~ Soil) +
  theme(strip.background = element_rect(colour="black", fill="white", size=0.1))+
  theme(strip.text.x = element_text(size = 17))

p_A

# plot Nitrite
p_I <- ggplot(df_plot2, aes(x=Time_hours, y=NO2_mM, color=H_mM, group=H_mM)) +
  geom_point(size=2.5, shape=16) +
  geom_line(size=1.5)+
  # geom_errorbar(aes(ymin=NO2_mM - Std_NO2_mM, ymax=NO2_mM + Std_NO2_mM), width=.05)+
  # scale_colour_gradientn(colours = (col_pH(100))) +
  # scale_color_manual(values=col_pH(4)) +
  ylab("NO2- (mM) \n") +
  xlab("\n Time (hr)") +
  # scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  # label
  # geom_text(aes(label = round(NO2_mM,3)), size = 3, vjust = -1.5, family="serif", show.legend = FALSE)+
  mytheme_2d +
  facet_grid(. ~ Soil) +
  theme(strip.background = element_rect(colour="black", fill="white", size=0.1))+
  theme(strip.text.x = element_text(size = 17))

p_I

require(gridExtra)
library(grid)
library(gtable)

legend = gtable_filter(ggplotGrob(p_A), "guide-box")

grid.arrange(arrangeGrob(p_A+xlab(NULL)+theme(legend.position="none"), 
                         p_I+xlab(NULL)+theme(legend.position="none")+theme(strip.background = element_blank(), strip.text = element_blank(), strip.text.x = element_blank()), nrow=2,
             top = textGrob("Adding strong acid to the extreme", vjust = 0.5, gp = gpar(fontface = "bold", cex = 1.5)),
             # left = textGrob("Relative abundance of strains with opt_pH", vjust = 0.5, rot=90, gp = gpar(fontface = "bold", cex = 1.5)),
             bottom = textGrob("Time (hr)", vjust = 0, gp = gpar(fontface="bold", cex = 1.5)),
             
             right = legend
             ))

```

# plot pH
```{r}
# plot with H_mM
df_plot3 <- df_plot2
df_pH_endpoint <- df_plot2 %>% filter(Time_point == "T2") %>%  group_by(Unit, Added_ul) %>% summarize(pH = mean(pH_meter)) 
df_plot3 %<>% left_join(df_pH_endpoint, by = c("Unit"="Unit", "Added_ul"="Added_ul"))
df_pH_endpoint$pH
df_plot3$pH <- factor(df_plot3$pH, levels=df_pH_endpoint$pH)

ggplot(df_plot3, aes(x=Time_hours, y=NO3_mM, color=pH, group=pH)) +
  geom_point(size=2.5, shape=16) +
  geom_line(size=1.2)+
  # geom_errorbar(aes(ymin=NO3_mM - Std_NO3_mM, ymax=NO3_mM + Std_NO3_mM), width=.05)+
  # scale_colour_gradientn(colours = rev(col_pH(100))) +
  # scale_color_manual(values=grad_pH) +
  ylab("NO3- (mM) \n") +
  xlab("\n Time (hr)") +
  # scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  # label
  # geom_text(aes(label = round(NO3_mM,3)), size = 3, vjust = -1.5, family="serif", show.legend = FALSE)+
  mytheme_2d +
  facet_grid(. ~ Soil) +
  theme(strip.background = element_rect(colour="black", fill="white", size=0.1))+
  theme(strip.text.x = element_text(size = 17))

# plot Nitrite
ggplot(df_plot3, aes(x=Time_hours, y=NO2_mM, color=pH, group=pH)) +
  geom_point(size=2.5, shape=16) +
  geom_line(size=1.5)+
  # geom_errorbar(aes(ymin=NO2_mM - Std_NO2_mM, ymax=NO2_mM + Std_NO2_mM), width=.05)+
  # scale_colour_gradientn(colours = (col_pH(100))) +
  # scale_color_manual(values=col_pH(4)) +
  ylab("NO2- (mM) \n") +
  xlab("\n Time (hr)") +
  # scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  # label
  # geom_text(aes(label = round(NO2_mM,3)), size = 3, vjust = -1.5, family="serif", show.legend = FALSE)+
  mytheme_2d +
  facet_grid(. ~ Soil) +
  theme(strip.background = element_rect(colour="black", fill="white", size=0.1))+
  theme(strip.text.x = element_text(size = 17))

p_A <- ggplot(df_plot3, aes(x=Time_hours, y=NO3_mM, color=pH, group=pH)) +
  geom_point(size=2.5, shape=16) +
  geom_line(size=1.2)+
  # geom_errorbar(aes(ymin=NO3_mM - Std_NO3_mM, ymax=NO3_mM + Std_NO3_mM), width=.05)+
  # scale_colour_gradientn(colours = rev(col_pH(100))) +
  # scale_color_manual(values=grad_pH) +
  ylab("NO3- (mM) \n") +
  xlab("\n Time (hr)") +
  # scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  # label
  # geom_text(aes(label = round(NO3_mM,3)), size = 3, vjust = -1.5, family="serif", show.legend = FALSE)+
  mytheme_2d +
  facet_grid(. ~ Soil) +
  theme(strip.background = element_rect(colour="black", fill="white", size=0.1))+
  theme(strip.text.x = element_text(size = 17))

p_A

# plot Nitrite
p_I <- ggplot(df_plot3, aes(x=Time_hours, y=NO2_mM, color=pH, group=pH)) +
  geom_point(size=2.5, shape=16) +
  geom_line(size=1.5)+
  # geom_errorbar(aes(ymin=NO2_mM - Std_NO2_mM, ymax=NO2_mM + Std_NO2_mM), width=.05)+
  # scale_colour_gradientn(colours = (col_pH(100))) +
  # scale_color_manual(values=col_pH(4)) +
  ylab("NO2- (mM) \n") +
  xlab("\n Time (hr)") +
  # scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  # label
  # geom_text(aes(label = round(NO2_mM,3)), size = 3, vjust = -1.5, family="serif", show.legend = FALSE)+
  mytheme_2d +
  facet_grid(. ~ Soil) +
  theme(strip.background = element_rect(colour="black", fill="white", size=0.1))+
  theme(strip.text.x = element_text(size = 17))

p_I

require(gridExtra)
library(grid)
library(gtable)

legend = gtable_filter(ggplotGrob(p_A), "guide-box")

grid.arrange(arrangeGrob(p_A+xlab(NULL)+theme(legend.position="none"), 
                         p_I+xlab(NULL)+theme(legend.position="none")+theme(strip.background = element_blank(), strip.text = element_blank(), strip.text.x = element_blank()), nrow=2,
             top = textGrob("Adding strong acid to the extreme", vjust = 0.5, gp = gpar(fontface = "bold", cex = 1.5)),
             # left = textGrob("Relative abundance of strains with opt_pH", vjust = 0.5, rot=90, gp = gpar(fontface = "bold", cex = 1.5)),
             bottom = textGrob("Time (hr)", vjust = 0, gp = gpar(fontface="bold", cex = 1.5)),
             
             right = legend
             ))

```

# pH titration curve

```{r}
df_plot$Time_days <- factor(df_plot$Time_days)
ggplot(df_plot, aes(x=H_mM, y=pH_meter, color=Time_days, group=Time_days)) +
  geom_point(size=3, shape=16, alpha=1) +
  # geom_errorbar(aes(ymin=Ave_pH - Std_pH, ymax=Ave_pH + Std_pH), width=.05)+
  geom_line(size=1)+
  # scale_color_brewer(palette='Set1') +
  ylab("pH \n") +
  xlab("\n added [H+] mM") +
  # scale_x_continuous(breaks = seq(-100,100,5))+
  scale_y_continuous(breaks = seq(0,14,1), limits=c(0, 14))+
  ggtitle("Soil pH perturbation & titration curves (Crerar7 pH 8.05) \n") +
  # label
  # geom_text(aes(label = pH_colorimetric), size = 3, vjust = -1.5, family="serif", show.legend  = FALSE)+
  mytheme_2d



```

