---
title: "Soil_extraction_method_Griess"
author: "KiseokUchicago"
date: "2021-09-24"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=11, fig.height=9,
                      error=TRUE, echo=TRUE, eval=TRUE, warning=FALSE, message=FALSE)
```

## Soil extraction method testing (Griess assay)
Researcher: **Kiseok Lee** \
Lab: **Seppe Kuehn**

```{r}
# libraries
library(dplyr)
library(ggplot2)
library(RColorBrewer)
library(vegan)
library(tidyverse)
library(magrittr)
library(readxl)
library(reshape2)
library(gtools)
library(devtools)
library(openxlsx)
library(ape)
library(stringr)

## theme for ggplot
mytheme <- theme_bw() + 
  theme(text = element_text(family="serif")) +
  theme(plot.title = element_text(size = 19,hjust = 0.5, family="serif")) + 
  theme(axis.title.x = element_text(size = 17,hjust = 0.5, family="serif")) + 
  theme(axis.title.y = element_text(size = 17,hjust = 0.5, family="serif")) + 
  theme(axis.text.x = element_text(hjust = 0.5, vjust=0.3,size=13, family="serif"))+
  theme(axis.text.y = element_text(size=10, family="serif"))+
  theme(panel.grid.major = element_blank()) +
  theme(panel.grid.minor = element_blank(),panel.background=element_blank(),panel.border=element_blank(),plot.background=element_blank()) +
  theme(axis.ticks = element_line(size = 1.1))

mytheme_2d <- theme_bw() + 
  theme(text = element_text(family="serif")) +
  theme(plot.title = element_text(size = 19,hjust = 0.5, family="serif")) + 
  theme(axis.title.x = element_text(size = 17,hjust = 0.5, family="serif")) + 
  theme(axis.title.y = element_text(size = 17,hjust = 0.5, family="serif")) + 
  theme(axis.text.x = element_text(hjust = 0.5, vjust=0.3,size=13, family="serif"))+
  theme(axis.text.y = element_text(size=13, family="serif"))+
  # theme(panel.grid.major = element_blank()) +
  # theme(panel.grid.minor = element_blank(),panel.background=element_blank(),plot.background=element_blank()) +
  theme(axis.ticks = element_line(size = 1.1))


# color collection
my_color_collection <- c(
  "#CBD588", "#5F7FC7", "orange", "#AD6F3B", "#673770", 
  "#D14285", "#652926", "#C84248", "#8569D5", "#5E738F",
  "#D1A33D", "#8A7C64", "#599861","#616163", "#FFCDB2",
  "#6D9F71", "#242F40",
  "#CCA43B", "#F92A82", "#ED7B84", "#7EB77F", 
  "#DEC4A1", "#E5D1D0", '#0E8482', '#C9DAEA', '#337357', 
  '#95C623', '#E55812', '#04471C', '#F2D7EE', '#D3BCC0', 
  '#A5668B', '#69306D', '#0E103D', '#1A535C', '#4ECDC4', 
  '#F7FFF7', '#FF6B6B', '#FFE66D', '#6699CC', '#FFF275', 
  '#FF8C42', '#FF3C38', '#A23E48', '#000000', '#CF5C36', 
  '#EEE5E9', '#7C7C7C', '#EFC88B', '#2E5266', '#6E8898', 
  '#9FB1BC', '#D3D0CB', '#E2C044', '#5BC0EB', '#FDE74C', 
  '#9BC53D', '#E55934', '#FA7921', "#CD9BCD", "#508578", "#DA5724")

# for git push, use this instead of using wflow_git_push()
# git push -u origin master (in the Git app / in the working directory)

```

## 1. Import data table from python code
When I did the experiment, B05 and B06 was switched. D05, D06 also switched. F05, F06 switched.
```{r}
# import file
df_extract <- openxlsx::read.xlsx("data/210922_Griess_sample_plate1.xlsx")
class(df_extract)
head(df_extract)
colnames(df_extract)

# remove NA
dim(df_extract)
df_extract <- na.omit(df_extract)
dim(df_extract)

# Check
df_extract %>% filter(Well =="B06")
df_extract %>% filter(Well =="D05")
df_extract %>% filter(Well =="F05")

```

## 2. Get average and standard deviation
```{r}
# average and standard deviation
df_NO2NO3 <- df_extract %>% group_by(Sample, Buffer, Soil_weight, Method, Spike_in) %>% summarise(Ave_NO2_mM = mean(NO2_mM), Std_NO2_mM = sd(NO2_mM), Ave_NO2NO3_mM = mean(NO2NO3_mM), Std_NO2NO3_mM = sd(NO2NO3_mM), Ave_NO3_mM = mean(NO2NO3_mM - NO2_mM), Std_NO3_mM = sd(NO2NO3_mM - NO2_mM)) %>% ungroup()
# NO3_mM = NO2NO3_mM - NO2_mM

# Factor in orders
df_NO2NO3$Buffer <-  factor(df_NO2NO3$Buffer, levels = c("KCl","K2SO4","H2O"))

# Put is values for known spike_ins
df_spike_in <- df_NO2NO3 %>% filter(Spike_in == "Original_sample")
df_spike_in

# increase the concentration as the spike in & make standard deviation to 0
df_spike_in2 <- df_spike_in %>%  mutate(Ave_NO2_mM = Ave_NO2_mM + 0.2, Ave_NO2NO3_mM = Ave_NO2NO3_mM + 0.4, Ave_NO3_mM = Ave_NO3_mM + 0.2, Std_NO2_mM = 0, Std_NO2NO3_mM = 0, Std_NO3_mM = 0) 

# change Sample name
df_spike_in2$Sample <- str_replace(df_spike_in2$Sample,"$","_spike_in")

# label in Spike_in column
df_spike_in2$Spike_in <- "Assuming_full_extraction"
df_spike_in2$Spike_in
dim(df_spike_in2)

# Bind this df to the original dataframe df_NO2NO3
dim(df_NO2NO3)
df_NO2NO3 <- rbind(df_NO2NO3, df_spike_in2)
dim(df_NO2NO3)
tail(df_NO2NO3)

df_NO2NO3$Spike_in
# Factor in orders
df_NO2NO3$Spike_in <-  factor(df_NO2NO3$Spike_in, levels = c("Spiked_sample","Original_sample", "Assuming_full_extraction"))

df_NO2NO3$Spike_in

write.xlsx(df_NO2NO3,"df_NO2NO3.xlsx")

```

## 3. Plot data
4 graphs:
(1) Soil 1g & Spindown method
(2) Soil 0.1g & Spindown method
(3) Soil 1g & filtered(0.22um) method
(4) Soil 0.1g & filtered(0.22um) method
(5) Soil 1g & Whatman no.42 paper filtered
```{r}
# First, let's see extraction efficiency soil NO2

# (1) 1g & Spindown method
colnames(df_NO2NO3)
df_spin1 <- df_NO2NO3 %>% filter(Method == "Spindown", Soil_weight ==1)
dim(df_spin1)

df_spin1$Spike_in
df_spin1 %>% filter(Spike_in == "Assuming_full_extraction")
df_spin1 %>% filter(Spike_in == "Spiked_sample")

ggplot(df_spin1, aes(x=Buffer, y=Ave_NO2_mM, color=Spike_in, group=Spike_in)) +
  geom_point(size=2.5, shape=21) +
  geom_line(size=1)+
  geom_errorbar(aes(ymin=Ave_NO2_mM - Std_NO2_mM, ymax=Ave_NO2_mM + Std_NO2_mM), width=.05)+
  scale_fill_brewer(palette='Set2') +
  ylab("NO2- (mM) \n") +
  xlab("\n Extraction buffer") +
  scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  ggtitle("(1) Soil 1g & Spindown method \n") +
  # label
  geom_text(aes(label = round(Ave_NO2_mM,3)), size = 3, vjust = -1.5, family="serif", show.legend = FALSE)+
  mytheme_2d

# (2) Soil 0.1g & Spindown method
colnames(df_NO2NO3)
df_spin0.1 <- df_NO2NO3 %>% filter(Method == "Spindown", Soil_weight ==0.1)
dim(df_spin0.1)
head(df_spin0.1)

df_spin0.1$Spike_in
df_spin0.1 %>% filter(Spike_in == "Assuming_full_extraction")
df_spin0.1 %>% filter(Spike_in == "Spiked_sample")

ggplot(df_spin0.1, aes(x=Buffer, y=Ave_NO2_mM, color=Spike_in, group=Spike_in)) +
  geom_point(size=2.5, shape=21) +
  geom_line(size=1)+
  geom_errorbar(aes(ymin=Ave_NO2_mM - Std_NO2_mM, ymax=Ave_NO2_mM + Std_NO2_mM), width=.05)+
  scale_fill_brewer(palette='Set2') +
  ylab("NO2- (mM) \n") +
  xlab("\n Extraction buffer") +
  scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  ggtitle("(2) Soil 0.1g & Spindown method \n") +
  # label
  geom_text(aes(label = round(Ave_NO2_mM,3)), size = 3, vjust = -1.5, family="serif", show.legend = FALSE)+
  mytheme_2d

# (3) Soil 1g & filtered(0.22um) method
colnames(df_NO2NO3)
df_NO2NO3$Method %>% unique()
df_filt1 <- df_NO2NO3 %>% filter(Method == "Filter", Soil_weight ==1)
dim(df_filt1)
head(df_filt1)

df_filt1$Spike_in
df_filt1 %>% filter(Spike_in == "Assuming_full_extraction")
df_filt1 %>% filter(Spike_in == "Spiked_sample")

ggplot(df_filt1, aes(x=Buffer, y=Ave_NO2_mM, color=Spike_in, group=Spike_in)) +
  geom_point(size=2.5, shape=21) +
  geom_line(size=1)+
  geom_errorbar(aes(ymin=Ave_NO2_mM - Std_NO2_mM, ymax=Ave_NO2_mM + Std_NO2_mM), width=.05)+
  scale_fill_brewer(palette='Set2') +
  ylab("NO2- (mM) \n") +
  xlab("\n Extraction buffer") +
  scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  ggtitle("(3) Soil 1g & filtered (0.22um) method \n") +
  # label
  geom_text(aes(label = round(Ave_NO2_mM,3)), size = 3, vjust = -1.5, family="serif", show.legend = FALSE)+
  mytheme_2d

# (4) Soil 0.1g & filtered(0.22um) method
colnames(df_NO2NO3)
df_NO2NO3$Method %>% unique()
df_filt0.1 <- df_NO2NO3 %>% filter(Method == "Filter", Soil_weight ==0.1)
dim(df_filt0.1)
head(df_filt0.1)

df_filt0.1$Spike_in
df_filt0.1 %>% filter(Spike_in == "Assuming_full_extraction")
df_filt0.1 %>% filter(Spike_in == "Spiked_sample")

ggplot(df_filt0.1, aes(x=Buffer, y=Ave_NO2_mM, color=Spike_in, group=Spike_in)) +
  geom_point(size=2.5, shape=21) +
  geom_line(size=1)+
  geom_errorbar(aes(ymin=Ave_NO2_mM - Std_NO2_mM, ymax=Ave_NO2_mM + Std_NO2_mM), width=.05)+
  scale_fill_brewer(palette='Set2') +
  ylab("NO2- (mM) \n") +
  xlab("\n Extraction buffer") +
  scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  ggtitle("(4) Soil 0.1g & filtered (0.22um) method \n") +
  # label
  geom_text(aes(label = round(Ave_NO2_mM,3)), size = 3, vjust = -1.5, family="serif", show.legend = FALSE)+
  mytheme_2d

# (5) Soil 1g & Whatman no.42 paper filtered
colnames(df_NO2NO3)
df_NO2NO3$Method %>% unique()
df_what1 <- df_NO2NO3 %>% filter(Method == "Whatman", Soil_weight ==1)
dim(df_what1)
head(df_what1)

df_what1$Spike_in
df_what1 %>% filter(Spike_in == "Assuming_full_extraction")
df_what1 %>% filter(Spike_in == "Spiked_sample")

ggplot(df_what1, aes(x=Buffer, y=Ave_NO2_mM, color=Spike_in, group=Spike_in)) +
  geom_point(size=2.5, shape=21) +
  geom_line(size=1)+
  geom_errorbar(aes(ymin=Ave_NO2_mM - Std_NO2_mM, ymax=Ave_NO2_mM + Std_NO2_mM), width=.05)+
  scale_fill_brewer(palette='Set2') +
  ylab("NO2- (mM) \n") +
  xlab("\n Extraction buffer") +
  scale_y_continuous(breaks = seq(0,0.3,0.05), limits=c(0, 0.3))+
  ggtitle("(5) Soil 1g & Whatman no.42 paper filtered \n") +
  # label
  geom_text(aes(label = round(Ave_NO2_mM,3)), size = 3, vjust = -1.5, family="serif", show.legend = FALSE)+
  mytheme_2d



```

